### 2019-02-21 fantasy_baseball/draftResearch_pt1.Rmd
Init commit

---
title: "Draft Research pt1"
author: "Tom Kain"
date: "February 20, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Info for getting depth chart projections:
[Batters](https://www.fangraphs.com/projections.aspx?pos=all&stats=bat&type=fangraphsdc&team=0&lg=all&players=0)

[Pitchers](https://www.fangraphs.com/projections.aspx?pos=all&stats=pit&type=fangraphsdc&team=0&lg=all&players=0)

Download to CSV via:
`javascript:__doPostBack('ProjectionBoard1$cmdCSV','')`

Downloading manually for now...

```{r}
pitchers <- read_csv("data/depthChartProjections_pitchers_20190220.csv")

batters <- read_csv("data/depthChartProjections_batters_20190220.csv")

pitchers
batters
```

### 2019-02-24 R/yahoo_api.R
Yahoo API interface

@@ -1,0 +1,28 @@
+# TODO refactor into single function call
+library(httr)
+
+keys <- app_keys()
+
+myapp <- oauth_app("yahoo",
+                   key = keys[1],
+                   secret = keys[2]
+)
+
+yahoo_token <- oauth2.0_token(oauth_endpoints("yahoo"), 
+                              myapp,
+                              use_oob = TRUE, 
+                              oob_value = "oob"
+)
+
+
+app_keys <- function() {
+  key <- Sys.getenv('YAHOO_KEY')
+  secret <- Sys.getenv('YAHOO_SECRET')
+  
+  if (identical(key, "") || identical(secret, "")) {
+    stop("Please set env var YAHOO_KEY to your Yahoo app key, and YAHOO_SECRET to your Yahoo app secret",
+         call. = F)
+  }
+  
+  c(key,secret)
+}

### 2019-02-25 R/yahoo_api.R
Rolled up Yahoo API interface to single method call by URL path

@@ -1,19 +1,6 @@
-# TODO refactor into single function call
 library(httr)
-
-keys <- app_keys()
-
-myapp <- oauth_app("yahoo",
-                   key = keys[1],
-                   secret = keys[2]
-)
-
-yahoo_token <- oauth2.0_token(oauth_endpoints("yahoo"), 
-                              myapp,
-                              use_oob = TRUE, 
-                              oob_value = "oob"
-)
-
+library(httpuv)
+library(jsonlite)
 
 app_keys <- function() {
   key <- Sys.getenv('YAHOO_KEY')
@@ -26,3 +13,70 @@ app_keys <- function() {
   
   c(key,secret)
 }
+
+authenticate <- function() {
+  keys <- app_keys()
+  
+  myapp <- oauth_app("yahoo",
+                     key = keys[1],
+                     secret = keys[2]
+  )
+  
+  token <- oauth2.0_token(oauth_endpoints("yahoo"), 
+                                myapp,
+                                use_oob = TRUE, 
+                                oob_value = "oob"
+  )
+  
+  config(token = token)
+}
+
+yahoo_api <- function(path) {
+  
+  config <- authenticate()
+  ua <- user_agent("http://github.com/TK2575/ff_data")
+  
+  base <- "https://fantasysports.yahooapis.com/fantasy/v2/"
+  req_json <- "/?response=json"
+  
+  url <- paste0(base, path, req_json)
+  
+  resp <- GET(url = url, config = config, ua)
+  if (http_type(resp) != "application/json") {
+    stop("API did not return json", call. = F)
+  }
+  
+  parsed <- fromJSON(content(resp, "text"),
+                     simplifyVector = F)
+  
+  if (status_code(resp) != 200) {
+    stop(
+      sprintf(
+        "Yahoo API request failed [%s]\n%s\n<%s>",
+        status_code(resp),
+        parsed$message,
+        parsed$documentation_url
+      ),
+      call. = F
+    )
+  }
+  
+  structure(
+    list(
+      content = parsed,
+      path = path,
+      response = resp
+    ),
+    class = "yahoo_api"
+  )
+  
+}
+
+print.yahoo_api <- function(x, ...) {
+  cat("<Yahoo ", x$path, ">\n", sep = "")
+  str(x$content)
+  invisible(x)
+}
+
+
+

### 2019-03-01 draftResearch_pt1.Rmd
Yahoo API interface
Rolled up Yahoo API interface to single method call by URL path
Trying some approaches for parsing yahoo api data

--- 2019-02-21 fantasy_baseball/draftResearch_pt1.Rmd
@@
 knitr::opts_chunk$set(echo = TRUE)
+source("R/yahoo_api.R")
 library(tidyverse)
+library(rlist)
 ```
+
+# Position Eligibility
+
+```{r}
+get_json("users;use_login=1/games;game_keys=mlb/players") -> players
+
+players %>%
+  content() -> players_content
+
+players_content$fantasy_content$users$`0`$user[[2]]$games$`0`$game[[2]]$players[c(1:25)] -> players_list
+
+players_list %>% rlist::list.stack()
+
+players %>% list.load()
+
+```
+
+# Projection Data
 

### 2019-03-01 R/yahoo_api.R

@@ -1,6 +1,7 @@
 library(httr)
 library(httpuv)
 library(jsonlite)
+library(magrittr)
 
 app_keys <- function() {
   key <- Sys.getenv('YAHOO_KEY')
@@ -31,7 +32,7 @@ authenticate <- function() {
   config(token = token)
 }
 
-yahoo_api <- function(path) {
+get_json <- function(path) {
   
   config <- authenticate()
   ua <- user_agent("http://github.com/TK2575/ff_data")
@@ -61,6 +62,19 @@ yahoo_api <- function(path) {
     )
   }
   
+  resp
+}
+
+print.yahoo_api <- function(x, ...) {
+  cat("<Yahoo ", x$path, ">\n", sep = "")
+  str(x$content)
+  invisible(x)
+}
+
+parse_resp <- function(resp) {
+  parsed <- fromJSON(content(resp, "text"),
+                     simplifyVector = F)
+  
   structure(
     list(
       content = parsed,
@@ -72,10 +86,9 @@ yahoo_api <- function(path) {
   
 }
 
-print.yahoo_api <- function(x, ...) {
-  cat("<Yahoo ", x$path, ">\n", sep = "")
-  str(x$content)
-  invisible(x)
+yahoo_api <- function(path) {
+  get_json() %>%
+    parse_resp()    
 }
 
 

### 2019-03-02 draftResearch_pt1.Rmd
Encapsulated a single JSON example

@@
 
-players_list %>% rlist::list.stack()
+# trying different approach from https://cran.r-project.org/web/packages/jsonlite/vignettes/json-aaquickstart.html
+players %>%
+  content("text") %>%
+  fromJSON() -> players_fromJSON
 
-players %>% list.load()
+players_fromJSON$fantasy_content$users$`0`$user$games$`0`$game[[2]]$players[1:25] -> players_fromJSON_dataframe
 
+players_fromJSON_dataframe$`0`$player[[2]][[1]]
+
+# data camp approach
+players_content$fantasy_content$users$`0`$user[[2]]$games$`0`$game[[2]][[1]] -> players_content_list
+
+players_content_list %>% str(max.level=3)
+players_content_list %>% saveRDS("data/players_content_list.Rds")
 ```
+So this is a list of 26 elements, 25 lists, and "count" int = 25. One player is represented in each of the 25 nested lists, but their data is actually three levels of nesting beneath!
+
+Need to figure out how to extract that great-grandchild list from each of the 25 child lists, then I should be able to stack them via rlist.
 

### 2019-03-04 draftResearch_pt1.Rmd
mini eureka moment extracting player data from JSON response
Updated API interaction for coercing data to df, iterating for multiple pages

--- 2019-02-21 fantasy_baseball/draftResearch_pt1.Rmd
@@
 knitr::opts_chunk$set(echo = TRUE)
+source("R/yahoo_api.R")
 library(tidyverse)
 ```
+
+# Position Eligibility
+
+```{r}
+get_json("users;use_login=1/games;game_keys=mlb/players;start=0") %>% 
+  content() -> players_resp
+
+players_resp$fantasy_content$users$`0`$user[[2]]$games$`0`$game[[2]][[1]] -> players_list
+
+players_list %>% saveRDS("data/players_list.Rds")
+
+players_list$count -> row_count
+
+players_list$`0`[[1]][[1]] %>% flatten() %>% as.data.frame() -> ex_data
+
+suppressWarnings(
+  lapply(players_list[1:25], function(x) x[[1]][[1]] %>% 
+           flatten() %>% 
+           as.data.frame()) %>% 
+    bind_rows() %>% 
+    as_tibble() %>%
+    select(-(14:16))-> raw_df
+)
+```
+So this is a list of 26 elements, 25 lists, and "count" int = 25. One player is represented in each of the 25 nested lists, but their data is actually three levels of nesting beneath!
+
+Wrote a function to get iteratively get 25 players, get their data into a df and bind together:
+
+```{r}
+(get_players(50) -> tst_results)
+
+```
+
+Next, test and cleanup the data, specifically getting the position eligibility.
+Add a sleep time between calls so we don't hit the API over and over.
+See if we can join it with the Fangraphs data.
+Bonus points for applying other pipe operators.
+
+# Projection Data
 

### 2019-03-04 R/yahoo_api.R

@@ -71,25 +71,44 @@ print.yahoo_api <- function(x, ...) {
   invisible(x)
 }
 
-parse_resp <- function(resp) {
-  parsed <- fromJSON(content(resp, "text"),
-                     simplifyVector = F)
+get_players <- function(rownum=400) {
   
-  structure(
-    list(
-      content = parsed,
-      path = path,
-      response = resp
-    ),
-    class = "yahoo_api"
-  )
+  start <- 0
+  results <- data.frame()
+  times <- (rownum / 25) %>% floor()
   
+  for (i in 0:times) {
+    print(paste("i = ", i, " start = ", start))
+    suppressWarnings(
+      df <- get_players_page(start)
+    )
+    
+    print("binding data")
+    results <- results %>%
+      bind_rows(df)
+    
+    start <- start + 25
+    if (df %>% nrow() < 25) {
+      break
+    }
+  }
+
+  results
 }
 
-yahoo_api <- function(path) {
-  get_json() %>%
-    parse_resp()    
+get_players_page <- function(start) {
+  path <- paste0("users;use_login=1/games;game_keys=mlb/players;start=",start,";count=25")
+  
+  get_json(path) %>% 
+    content() -> players_resp
+  
+  players_resp$fantasy_content$users$`0`$user[[2]]$games$`0`$game[[2]][[1]] -> players_filtered
+  
+  lapply(players_filtered[1:25], function(x) x[[1]][[1]] %>% 
+           flatten() %>% 
+           as.data.frame()) %>% 
+    bind_rows() %>% 
+    as_tibble() %>%
+    select(-(14:16))
 }
-
-
 

### 2019-03-05 draftResearch_pt1.Rmd
Working on compiling up eligible positions into a comma separated string or vector

--- 2019-03-01 draftResearch_pt1.Rmd
@@
 library(tidyverse)
-library(rlist)
 ```
@@
 # Position Eligibility
+```{r}
+(get_players(50) -> tst_results)
 
-```{r}
-get_json("users;use_login=1/games;game_keys=mlb/players") -> players
+tst_results %>%
+  select(starts_with("eligible_positions")) %>%
+  transpose() %>%
+  lapply(as.character) %>%
+  lapply(function(x) x[!is.na(x)]) -> pos_complete
 
-players %>%
-  content() -> players_content
-
-players_content$fantasy_content$users$`0`$user[[2]]$games$`0`$game[[2]]$players[c(1:25)] -> players_list
-
-players_list %>% rlist::list.stack()
-
-players %>% list.load()
+# add list rows representing new column as new column on prior df?
+tst_results %>%
+  add_column(pos_complete) %>%
+  select(1, pos_complete)
 
 ```
-
-# Projection Data
-
-Info for getting depth chart projections:
-[Batters](https://www.fangraphs.com/projections.aspx?pos=all&stats=bat&type=fangraphsdc&team=0&lg=all&players=0)
-
-[Pitchers](https://www.fangraphs.com/projections.aspx?pos=all&stats=pit&type=fangraphsdc&team=0&lg=all&players=0)
-
-Download to CSV via:
-`javascript:__doPostBack('ProjectionBoard1$cmdCSV','')`
-
-Downloading manually for now...
-
-```{r}
-pitchers <- read_csv("data/depthChartProjections_pitchers_20190220.csv")
-
-batters <- read_csv("data/depthChartProjections_batters_20190220.csv")
-
-pitchers
-batters
-```

### 2019-03-05 R/yahoo_api.R

@@ -74,16 +74,12 @@ print.yahoo_api <- function(x, ...) {
 get_players <- function(rownum=400) {
   
   start <- 0
-  results <- data.frame()
+  results <- tibble()
   times <- (rownum / 25) %>% floor()
   
   for (i in 0:times) {
-    print(paste("i = ", i, " start = ", start))
-    suppressWarnings(
       df <- get_players_page(start)
-    )
     
-    print("binding data")
     results <- results %>%
       bind_rows(df)
     
@@ -106,7 +102,7 @@ get_players_page <- function(start) {
   
   lapply(players_filtered[1:25], function(x) x[[1]][[1]] %>% 
            flatten() %>% 
-           as.data.frame()) %>% 
+           as.data.frame(stringsAsFactors = F)) %>% 
     bind_rows() %>% 
     as_tibble() %>%
     select(-(14:16))

### 2019-03-06 draftResearch_pt1.Rmd
Trying to find a way to get my concatenated rowwise list of eligible positions

@@
 
+tst_results %>% saveRDS("data/tst_results")
+
+```
+Two ways avenues with which I'm hoping to find a solution with at least one. 
+```{r}
+# get all positions per row as list, add to data set
 tst_results %>%
@@
 
-# add list rows representing new column as new column on prior df?
 tst_results %>%
-  add_column(pos_complete) %>%
-  select(1, pos_complete)
+  add_column(all_pos = pos_complete) %>%
+  # Challenge - results stord as a list type column, need to convert to a character vector with ", " separator.
+  select(1, all_pos)
 
 ```
+
+```{r}
+# rather than store as list, complete the paste of the various columns directly
+collapse_cols <- function(d,...) {
+  vars  <- quos(...)
+  d %>% mutate(f = paste(!!!vars, sep=", "))
+}
+
+# this works, but isn't dynamic based on the potentially varying number of eligible position columns
+tst_results %>%
+  select(starts_with("eligible_positions")) %>%
+  mutate(all_pos = paste(eligible_positions.position,
+                         eligible_positions.position.1, sep = ", ")) %>%
+  select(1,2, all_pos) %>%
+  head()
+
+col_nms <- tst_results %>%
+  select(starts_with("eligible_positions")) %>%
+  colnames()
+
+# challenge - pass the dynamic list of column names to the paste function
+tst_results %>%
+  collapse_cols(col_nms) %>%
+  select(f) %>%
+  head()
+
+tst_results %>%
+  mutate(all_pos = paste(quos(eligible_positions.position, eligible_positions.position.1), sep=", ")) %>%
+  select(all_pos)
+```

### 2019-03-08 draftResearch_pt1.Rmd
Concatenated eligible positions to single comma delimited character vector

--- 2019-03-05 draftResearch_pt1.Rmd
@@
 ```{r}
-(get_players(50) -> tst_results)
+suppressWarnings(
+  get_players(312) -> tst_results
+)
+
+col_nms <- tst_results %>%
+  select(starts_with("eligible_positions")) %>%
+  colnames()
 
 tst_results %>%
-  select(starts_with("eligible_positions")) %>%
-  transpose() %>%
-  lapply(as.character) %>%
-  lapply(function(x) x[!is.na(x)]) -> pos_complete
+  mutate(positions = paste(!!! syms(col_nms), sep = "," )) %>%
+  mutate(positions = gsub('NA', '', positions)) %>%
+  mutate(positions = gsub(',,', '', positions)) %>%
+  select(-(starts_with("eligible_positions"))) %>%
+  select(name.full, display_position, positions) -> tst_results
 
-# add list rows representing new column as new column on prior df?
-tst_results %>%
-  add_column(pos_complete) %>%
-  select(1, pos_complete)
+tst_results %>% saveRDS("data/tst_results")
+
+View(tst_results)
 
 ```
+
+##### To Do
+
+1. Prevent the need to supressWarnings 
+2. Some merge of display position and positions
+3. Rename df to something useful for joining to other data sets
+4. Figure out what columns to include that will be needed for joining to other data sets
+5. Kill trailing comma in positions column

### 2019-03-09 draftResearch_pt1.Rmd
Finished position eligibility

--- 2019-03-05 draftResearch_pt1.Rmd
@@
 ```{r}
-(get_players(50) -> tst_results)
+get_players(450) -> players
 
-tst_results %>%
+position_columns <- players %>%
   select(starts_with("eligible_positions")) %>%
-  transpose() %>%
-  lapply(as.character) %>%
-  lapply(function(x) x[!is.na(x)]) -> pos_complete
+  colnames()
 
-# add list rows representing new column as new column on prior df?
-tst_results %>%
-  add_column(pos_complete) %>%
-  select(1, pos_complete)
+players %>%
+  mutate(positions = paste(!!! syms(position_columns), sep = "," )) %>%
+  mutate(positions = gsub('NA', '', positions)) %>%
+  mutate(positions = gsub("^,*|(?<=,),|,*$", "", positions, perl=T)) %>%
+  select(-(starts_with("eligible_positions"))) %>%
+  select(
+    player_id:name.last, 
+    editorial_team_abbr, 
+    position_type, 
+    display_position,
+    positions
+  ) -> players
+
+players %>% saveRDS("data/players_position_eligibility.Rds")
 

### 2019-03-09 R/yahoo_api.R

@@ -2,6 +2,7 @@ library(httr)
 library(httpuv)
 library(jsonlite)
 library(magrittr)
+library(glue)
 
 app_keys <- function() {
   key <- Sys.getenv('YAHOO_KEY')
@@ -73,20 +74,22 @@ print.yahoo_api <- function(x, ...) {
 
 get_players <- function(rownum=400) {
   
-  start <- 0
+  cursor <- 0
   results <- tibble()
-  times <- (rownum / 25) %>% floor()
+  pages <- (rownum / 25) %>% ceiling()
   
-  for (i in 0:times) {
-      df <- get_players_page(start)
+  for (i in 1:(pages)) {
+    print(glue("Retrieving page {i} of {pages}"))  
+    df <- get_players_page(cursor)
     
     results <- results %>%
       bind_rows(df)
     
-    start <- start + 25
+    cursor <- cursor + 25
     if (df %>% nrow() < 25) {
       break
     }
+    Sys.sleep(5)
   }
 
   results

### 2019-03-09 draftResearch_pt2.Rmd
Import fangraphs depth chart projection data

---
title: "Draft Research pt2"
author: "Tom Kain"
date: "March 8, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Custom player rankings

Goals:
1. Import projection data, as automated as possible
2. Generate ranks based on league stat categories using projection data via z-scores controlling for PA/IP
3. Determine a replacement-level performance and scale rankings accordingly

# Import
Info for getting depth chart projections:
[Batters](https://www.fangraphs.com/projections.aspx?pos=all&stats=bat&type=fangraphsdc&team=0&lg=all&players=0)

[Pitchers](https://www.fangraphs.com/projections.aspx?pos=all&stats=pit&type=fangraphsdc&team=0&lg=all&players=0)

Download to CSV via:
`javascript:__doPostBack('ProjectionBoard1$cmdCSV','')`

Downloading manually for now. The scoring categories for our league:
Batters: R, H, HR, RBI, SB, BB, K, OBP, OPS - Not included in data set: E
Pitchers: SV, K, HLD, ERA, WHIP - Not included in data set: NH, QS, BSV, CG, SHO

```{r}
pitchers_file <- "data/depthChartProjections_pitchers_20190308.csv"
batters_file <- "data/depthChartProjections_batters_20190308.csv"

pitchers <- read_csv(pitchers_file) %>%
  select(playerid, 
         Name, 
         Team,
         ADP,
         IP,
         SV:ERA,
         SO,
         WHIP)

batters <- read_csv(batters_file) %>%
  select(playerid,
         Name,
         Team,
         ADP,
         PA,
         H,
         HR:SO,
         SB,
         OBP,
         OPS)
```

### 2019-03-09 draftResearch_pt2.Rmd
Z-scores computation

@@
 ```
+
+# Generate rankings
+```{r}
+z_score_count <- function(df, stat, invert=FALSE) {
+  stat <- enquo(stat)
+  col_nm <- paste0("z_", quo_name(stat))
+
+  df <- df %>% 
+    mutate(s_z = (!! stat - mean(!! stat)) / sd(!! stat))
+
+  if (invert) {
+    df %>%
+      mutate(s_z = -s_z) -> df
+  }
+
+  df %>%
+   rename(!! col_nm := s_z)
+}
+
+z_score_rate <- function(df, stat, quantity, invert=FALSE) {
+  stat <- enquo(stat)
+  quantity <- enquo(quantity)
+  col_nm <- paste0("z_",quo_name(stat))
+
+  df %>%
+    mutate(s_q = (!! stat - mean(!! stat)) * !! quantity) %>%
+    mutate(s_z = (s_q - mean(s_q)) / sd(s_q)) -> df
+
+  if (invert) {
+    df %>%
+      mutate(s_z = -s_z) -> df
+  }
+
+  df %>%
+    rename(!! col_nm := s_z) %>%
+    select(-s_q)
+}
+
+(z_pitchers <- pitchers %>%
+  z_score_count(SV) %>%
+  z_score_count(HLD) %>%
+  z_score_rate(ERA, IP, TRUE) %>%
+  z_score_count(SO) %>%
+  z_score_rate(WHIP, IP, TRUE) %>%
+  mutate(
+    z_sum = pmap_dbl(
+      select(., starts_with("z_")), 
+      sum
+    )
+  ) %>%
+  arrange(desc(z_sum))
+)
+
+(z_batters <- batters %>%
+  z_score_count(H) %>%
+  z_score_count(HR) %>%
+  z_score_count(R) %>%
+  z_score_count(RBI) %>%
+  z_score_count(BB) %>%
+  z_score_count(SO, TRUE) %>%
+  z_score_count(SB) %>%
+  z_score_rate(OBP, PA) %>%
+  z_score_rate(OPS, PA) %>%
+  mutate(
+    z_sum = pmap_dbl(
+      select(., starts_with("z_")), 
+      sum
+    )
+  ) %>%
+  arrange(desc(z_sum))
+)
+
+z_batters %>% saveRDS("data/z_batters.Rds")
+z_pitchers %>% saveRDS("data/z_pitchers.Rds")
+
+z_batters %>% 
+  mutate(type = "Batter") %>%
+  bind_rows(z_pitchers) %>%
+  select(playerid, Name, type, ADP, z_sum) %>%
+  filter(ADP < 999) %>%
+  mutate(type = if_else(is.na(type), "Pitcher", type)) %>%
+  arrange(z_sum %>% desc()) %>%
+  ggplot(aes(x=ADP,y=z_sum,color=type)) +
+  geom_point() -> p
+
+plotly::ggplotly(p)
+
+```
+
+### To Do
+1. Strategy for projecting scoring stats not in this data set (i.e. CG/SHO, etc)
+2. Validate findings, control z-scores between batters and players to make them comparable
+3. Develop tiers of players (linear model? nearest neighbor?), visualize - adjust plotly hover over detail to include player name (or maybe just playerid?)
+4. Replacement level stuff (new section)

### 2019-03-10 draftResearch_pt2.Rmd
Some fruitless research into projecting some missing metrics

--- 2019-03-09 draftResearch_pt2.Rmd
@@
 ```{r}
-pitchers_file <- "data/depthChartProjections_pitchers_20190308.csv"
-batters_file <- "data/depthChartProjections_batters_20190308.csv"
+pitchers_raw <- "data/depthChartProjections_pitchers_20190308.csv" %>%
+  read_csv()
+batters_raw <- "data/depthChartProjections_batters_20190308.csv" %>%
+  read_csv()
 
-pitchers <- read_csv(pitchers_file) %>%
+pitchers <- pitchers_raw %>%
   select(playerid, 
@@
 
-batters <- read_csv(batters_file) %>%
+batters <- batters_raw %>%
   select(playerid,
@@
 ```
+
+# Generate rankings
+```{r}
+z_score_count <- function(df, stat, invert=FALSE) {
+  stat <- enquo(stat)
+  col_nm <- paste0("z_", quo_name(stat))
+
+  df <- df %>% 
+    mutate(s_z = (!! stat - mean(!! stat)) / sd(!! stat))
+
+  if (invert) {
+    df %>%
+      mutate(s_z = -s_z) -> df
+  }
+
+  df %>%
+   rename(!! col_nm := s_z)
+}
+
+z_score_rate <- function(df, stat, quantity, invert=FALSE) {
+  stat <- enquo(stat)
+  quantity <- enquo(quantity)
+  col_nm <- paste0("z_",quo_name(stat))
+
+  df %>%
+    mutate(s_q = (!! stat - mean(!! stat)) * !! quantity) %>%
+    mutate(s_z = (s_q - mean(s_q)) / sd(s_q)) -> df
+
+  if (invert) {
+    df %>%
+      mutate(s_z = -s_z) -> df
+  }
+
+  df %>%
+    rename(!! col_nm := s_z) %>%
+    select(-s_q)
+}
+
+(z_pitchers <- pitchers %>%
+  filter(ADP < 999) %>%
+  z_score_count(SV) %>%
+  z_score_count(HLD) %>%
+  z_score_rate(ERA, IP, TRUE) %>%
+  z_score_count(SO) %>%
+  z_score_rate(WHIP, IP, TRUE) %>%
+  mutate(
+    z_sum = pmap_dbl(
+      select(., starts_with("z_")), 
+      sum
+    )
+  ) %>%
+  arrange(desc(z_sum))
+)
+
+(z_batters <- batters %>%
+  filter(ADP < 999) %>%
+  z_score_count(H) %>%
+  z_score_count(HR) %>%
+  z_score_count(R) %>%
+  z_score_count(RBI) %>%
+  z_score_count(BB) %>%
+  z_score_count(SO, TRUE) %>%
+  z_score_count(SB) %>%
+  z_score_rate(OBP, PA) %>%
+  z_score_rate(OPS, PA) %>%
+  mutate(
+    z_sum = pmap_dbl(
+      select(., starts_with("z_")), 
+      sum
+    )
+  ) %>%
+  arrange(desc(z_sum))
+)
+
+z_batters %>% saveRDS("data/z_batters.Rds")
+z_pitchers %>% saveRDS("data/z_pitchers.Rds")
+
+z_batters %>% 
+  mutate(type = "Batter") %>%
+  bind_rows(z_pitchers) %>%
+  select(playerid, Name, type, ADP, z_sum) %>%
+  mutate(type = if_else(is.na(type), "Pitcher", type)) %>%
+  arrange(z_sum %>% desc()) %>%
+  ggplot(aes(x=ADP,y=z_sum,color=type)) +
+  geom_point(aes(text=Name)) -> p
+
+plotly::ggplotly(p)
+
+```
+
+### Missing Projection Data
+Looking for some proxies for the following: NH, QS, BSV, CG, SHO, E. NH and SHO scarcity probably isn't worth diving in, probably just weight CG higher if I can project that. As for the remainders:
+
+- Errors : research the correlation with Depth Chart's "FLD" metric to see if that's useful enough to weigh lightly. 
+- BSV : Look at prior years' data to see the blown save rate and see if there's a predictable relationship to anything
+- QS : once we've got a tally (find a source or summarize game logs), same idea as above
+- CG : same
+
+##### Errors
+```{r}
+fielding_standard <- "data/2018_Fielding-Standard.csv" %>%
+  read_csv() %>%
+  mutate(playerid = playerid %>% as.character())
+
+fielding_advanced <- "data/2018_Fielding-Advanced.csv" %>%
+  read_csv() %>%
+  mutate(playerid = playerid %>% as.character()) %>%
+  select(-(Name:Inn))
+
+fielding <- fielding_standard %>%
+  full_join(fielding_advanced, "playerid")
+
+fielding %>%
+  select(playerid, Pos, E, Def) %>%
+  full_join(batters_raw, "playerid") %>%
+  filter(ADP < 999) %>%
+  select(Name, Team, Pos, E, Def, Fld) %>%
+  filter(is.na(E))
+  ggplot(aes(x=E,y=Fld)) +
+  geom_point()
+
+```
+Incomplete listing, probably due to minimum qualified innings, but even with this sample (~ a third of the batters in the depth chart projections), not seeing a pattern.
+Since there is going to be at least one pitching category I won't be able to project, not having Errors should be ok.
+
+##### CG
+```{r}
+hist_pitching <- "data/2016-2018_Pitching.csv" %>%
+  read_csv()
+
+hist_pitching %>%
+  ggplot(aes(x=CG/3)) + 
+  geom_histogram(binwidth=1)
+
+hist_pitching %>%
+  ggplot(aes(x=CG/3,y=IP/3)) +
+  geom_point()
+```
+Looks like there were only two pitchers in the past three years that averaged 1 CG/year with less than 150 IP/year. Takeaway is to weigh IP a bit more.
+
+##### BSV
+```{r}
+hist_pitching %>%
+  select(Name, Team, G, IP, ERA, SV, BS) %>%
+  filter(SV > 0 | BS > 0) -> sv_pitching
+
+sv_pitching %>%
+  ggplot(aes(x=SV/3)) +
+  geom_histogram(binwidth=1)
+
+sv_pitching %>%
+  ggplot(aes(x=SV/3,y=BS/3)) +
+  geom_point()
+
+sv_pitching %>%
+  ggplot(aes(x=SV/3,y=IP/3)) +
+  geom_point()
+
+sv_pitching %>%
+  ggplot(aes(x=BS/3,y=IP/3)) +
+  geom_point()
+```
+As expected, not much with the existing data to correlate Blown Saves, so I the takeaway will probably be to more highly weigh ERA and WHIP.
+
+##### QS
+```{r}
+
+```
+
+### To Do
+1. Strategy for projecting scoring stats not in this data set (i.e. CG/SHO, etc)
+2. Validate findings, control z-scores between batters and players to make them comparable
+3. visualize - adjust plotly hover over detail to include player name (or maybe just playerid?)
+4. Develop tiers of players (linear model? nearest neighbor?)
+5. Replacement level stuff (new section)

### 2019-03-10 draftResearch_pt2.Rmd
Trying some adjustments to pitching z-scores for comparison to batters

@@
 ```{r}
-z_score_count <- function(df, stat, invert=FALSE) {
+z_score_count <- function(df, stat, invert=FALSE, multiplier=1) {
   stat <- enquo(stat)
@@
 
+  if (multiplier != 1) {
+    df %>%
+      mutate(s_z = multiplier * s_z) -> df
+  }
+
   df %>%
@@
 
-z_score_rate <- function(df, stat, quantity, invert=FALSE) {
+z_score_rate <- function(df, stat, quantity, invert=FALSE, multiplier = 1) {
   stat <- enquo(stat)
@@
       mutate(s_z = -s_z) -> df
+  }
+
+  if (multiplier != 1) {
+    df %>%
+      mutate(s_z = multiplier * s_z) -> df
   }
@@
 ##### QS
+Struggling to find meaningful QS data to work with, but again, I'm thinking the takeaway will be more weighting on ERA & WHIP.
+
+##### Z-Score Adjustments
+I originally added a multiplier of 3 to two of the pitching categories, so that it would mean there were "nine" categories for both pitching and batting that make up the z_sum. 
+The result was that pitching z_sums had a much wider range, to the point where three pitchers had a higher z_sum than Mike Trout, who was coming out roughly as valuable as Justin Verlander. 
+Weighting the categories so that there would be an "equal" number of categories felt right, but I wonder if that's giving too much credit to scarce categories like CG/SHO. 
+For now, I've set the multiplier to 2. The results are still a bit "scandalous" (Mookie Betts going after Sale/deGrom/Scherzer) but this is a better starting point for a conversation.
+Need to take a deeper look into how I'm comparing the relative value between pitcher and catcher rather than setting the multiplier to get results I'm expecting. 
 ```{r}
+(z_pitchers_adj <- pitchers %>%
+  filter(ADP < 999) %>%
+  z_score_count(SV) %>%
+  z_score_count(HLD) %>%
+  z_score_rate(ERA, IP, TRUE, multiplier=2) %>%
+  z_score_count(SO) %>%
+  z_score_rate(WHIP, IP, TRUE, multiplier=2) %>%
+  mutate(
+    z_sum = pmap_dbl(
+      select(., starts_with("z_")), 
+      sum
+    )
+  ) %>%
+  arrange(desc(z_sum))
+)
 
+(z_compare_adj <- z_batters %>% 
+  mutate(type = "Batter") %>%
+  bind_rows(z_pitchers_adj) %>%
+  mutate(type = if_else(is.na(type), "Pitcher", type)) %>%
+  arrange(z_sum %>% desc()) %>%
+  mutate(ovrl_rank = row_number()))
+
+z_compare_adj %>% saveRDS("data/z_compare_adj.Rds")
+
+z_compare_adj %>%  
+  filter(Name == "Miguel Cabrera" | Name == "Kyle Freeland") %>% 
+  View()
+
+z_compare_adj %>%
+  ggplot(aes(x=ADP,y=z_sum,color=type)) +
+  geom_point(aes(text=Name)) -> p_adj
+
+plotly::ggplotly(p_adj)
 ```
@@
 ### To Do
-1. Strategy for projecting scoring stats not in this data set (i.e. CG/SHO, etc)
-2. Validate findings, control z-scores between batters and players to make them comparable
-3. visualize - adjust plotly hover over detail to include player name (or maybe just playerid?)
-4. Develop tiers of players (linear model? nearest neighbor?)
-5. Replacement level stuff (new section)
+1. Validate findings, control z-scores between batters and players to make them comparable
+2. visualize - adjust plotly hover over detail to include player name (or maybe just playerid?)
+3. Develop tiers of players (linear model? nearest neighbor?)
+4. Replacement level stuff (new section)

### 2019-03-10 draftResearch_pt2.Rmd
Clean up of z_score vs z_score_adj comparison

@@
 
-z_batters %>% 
+z_compare <- z_batters %>% 
   mutate(type = "Batter") %>%
@@
   mutate(type = if_else(is.na(type), "Pitcher", type)) %>%
-  arrange(z_sum %>% desc()) %>%
-  ggplot(aes(x=ADP,y=z_sum,color=type)) +
-  geom_point(aes(text=Name)) -> p
+  arrange(z_sum %>% desc())
+
+z_compare %>%
+  mutate(ovrl_rank = row_number()) %>%
+  ggplot(aes(x=ADP,y=ovrl_rank,color=type)) +
+  geom_point(aes(text=Name)) +
+  geom_abline(slope=1) -> p
 
@@
   select(Name, Team, Pos, E, Def, Fld) %>%
-  filter(is.na(E))
+  filter(!is.na(E)) %>%
   ggplot(aes(x=E,y=Fld)) +
@@
 ```
-Looks like there were only two pitchers in the past three years that averaged 1 CG/year with less than 150 IP/year. Takeaway is to weigh IP a bit more.
+Looks like there were only three pitchers in the past three years that averaged 1 CG/year with less than 150 IP/year. Takeaway is to weigh IP a bit more.
 
@@
 z_compare_adj %>%
-  ggplot(aes(x=ADP,y=z_sum,color=type)) +
-  geom_point(aes(text=Name)) -> p_adj
+  ggplot(aes(x=ADP,y=ovrl_rank,color=type)) +
+  geom_point(aes(text=Name)) +
+  geom_abline(slope=1)-> p_adj
 

### 2019-03-12 draftResearch_pt2.Rmd
Completed adjusted validation

@@
 
+# Validation
+```{r}
+z_compare_adj %>%
+  filter(type != "Batter") %>% 
+  select(playerid, Name, Team, ADP, ovrl_rank, z_sum, z_ERA, z_WHIP, z_SO, z_SV, z_HLD, IP, ERA, WHIP, SO, SV, HLD) %>%
+  arrange(ADP) %>%
+  View()
+
+z_compare_adj %>%
+  ggplot(aes(z_sum, color = type)) +
+  geom_freqpoly(binwidth=1)
+
+z_compare_adj %>%
+  filter(Name %in% c("Blake Snell", "Andrew Benintendi")) %>%
+  View()
+
+z_compare_adj %>%
+  filter(Name %in% c("James Paxton", "Eugenio Suarez")) %>% 
+  View()
+```
+
+I don't have any objective measure to compare the value between similarly ranked batters and pitchers.
+I compared a few pairs of players against other expert's rankings and these largely seem to be in line.
+I'm at a disadvantage without being able to project Quality Starts.
+However, since I'm walking in with the likely goal of spending early draft capital on hitting and planning to play the waiver wire for two-start/matchup starters, these results should be sufficient.
 ### To Do
-1. Validate findings, control z-scores between batters and players to make them comparable
-2. visualize - adjust plotly hover over detail to include player name (or maybe just playerid?)
-3. Develop tiers of players (linear model? nearest neighbor?)
-4. Replacement level stuff (new section)
+1. Develop tiers of players (linear model? nearest neighbor?)
+2. Replacement level stuff (new section)
+3. Take averages of multiple projection sources? 
+4. Build team stats based on selections, available players per round?

### 2019-03-12 draftResearch_pt3.Rmd
Starting join

---
title: "Draft Research pt3"
author: "Tom Kain"
date: "March 11, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Join Data
Let's see if we can join the eligible position data (Yahoo) with the projection data (Fangraphs).

```{r}
yahoo <- readRDS('data/players_position_eligibility.Rds') %>%
  select(name.full, display_position, positions)

fangraphs <- readRDS('data/z_compare_adj.Rds')

df_raw <- fangraphs %>%
  full_join(yahoo, by = c("Name" = "name.full"))

```

```{r}
df_raw %>%
  filter(is.na(display_position)) %>%
  select(Name, positions, ADP, ovrl_rank, z_sum) %>%
  head(25)

df_raw %>%
  filter(Name == "Jose Ramirez") %>%
  select(Name, positions, ADP, ovrl_rank, z_sum) %>%
  head()

fangraphs %>%
  count()
```

### To Do
1. Missing joins in yahoo data (i.e. Jose Ramirez) due to inconsistent accent marks on letters (and maybe other causes too?)
2. Develop tiers of players (linear model? nearest neighbor?)
3. Replacement level stuff (new section)
4. Take averages of multiple projection sources? 
5. Build team stats based on selections, available players per round?

### 2019-03-15 draftResearch_pt2.Rmd
Starting join
Some data refresh and join fixes

@@
 knitr::opts_chunk$set(echo = TRUE)
+options(tidyverse.quiet=TRUE)
 library(tidyverse)
@@
 pitchers_raw <- "data/depthChartProjections_pitchers_20190308.csv" %>%
-  read_csv()
+  read_csv() %>%
+  unique()
 batters_raw <- "data/depthChartProjections_batters_20190308.csv" %>%
-  read_csv()
+  read_csv() %>%
+  unique()
 
@@
 However, since I'm walking in with the likely goal of spending early draft capital on hitting and planning to play the waiver wire for two-start/matchup starters, these results should be sufficient.
-### To Do
-1. Develop tiers of players (linear model? nearest neighbor?)
-2. Replacement level stuff (new section)
-3. Take averages of multiple projection sources? 
-4. Build team stats based on selections, available players per round?

### 2019-03-15 draftResearch_pt3.Rmd
Some data refresh and join fixes

@@
 knitr::opts_chunk$set(echo = TRUE)
+options(tidyverse.quiet=TRUE)
 library(tidyverse)
+library(fuzzyjoin)
 ```
@@
 yahoo <- readRDS('data/players_position_eligibility.Rds') %>%
-  select(name.full, display_position, positions)
+  select(name.full, display_position, positions) %>%
+  mutate(name.full = chartr("áéóíñú", "aeoinu", name.full))
+
+yahoo$name.full[yahoo$name.full == 'Daniel Vogelbach'] <- "Dan Vogelbach"
+yahoo$name.full[yahoo$name.full == 'Shohei Ohtani (Batter)'] <- "Shohei Ohtani"
 
 fangraphs <- readRDS('data/z_compare_adj.Rds')
+
+fangraphs$Name[fangraphs$Name == 'Enrique Hernandez'] <- "Kike Hernandez"
+fangraphs$Name[fangraphs$Name == 'Cedric Mullins II'] <- "Cedric Mullins"
+fangraphs$Name[fangraphs$Name == 'Michael Soroka'] <- "Mike Soroka"
+fangraphs$Name[fangraphs$Name == 'Nathaniel Lowe'] <- "Nate Lowe"
+fangraphs$Name[fangraphs$Name == 'Nathan Karns'] <- "Nate Karns"
 
@@
 
+df_fuzzy <- fangraphs %>%
+  stringdist_full_join(yahoo, by = c("Name" = "name.full"))
+
+df_raw %>% 
+  count(is.na(display_position) & is.na(positions))
+df_fuzzy %>% 
+  count(is.na(display_position) & is.na(positions))
 ```
 
+#### Orphaned Records after join fixes
+1. Replaced accented characters to characters without accents
+2. Fuzzy join
+3. Yahoo API query for *2500* players (rather than 850)
+4. Duplicate Shohei Ohtani records, lack of pitching projections
+5. Multiple player minor name mismatches
+
 ```{r}
-df_raw %>%
-  filter(is.na(display_position)) %>%
-  select(Name, positions, ADP, ovrl_rank, z_sum) %>%
-  head(25)
+df_fuzzy %>% 
+  filter(is.na(display_position) & is.na(positions)) %>%
+  View()
 
-df_raw %>%
-  filter(Name == "Jose Ramirez") %>%
-  select(Name, positions, ADP, ovrl_rank, z_sum) %>%
-  head()
-
-fangraphs %>%
-  count()
+yahoo %>% filter("Riley" %>% grepl(name.full))
+fangraphs %>% filter("Riley" %>% grepl(Name)) %>% select(Name)
 ```

### 2019-03-15 R/yahoo_api.R

@@ -72,9 +72,9 @@ print.yahoo_api <- function(x, ...) {
   invisible(x)
 }
 
-get_players <- function(rownum=400) {
+get_players <- function(rownum=25, start=0) {
   
-  cursor <- 0
+  cursor <- start
   results <- tibble()
   pages <- (rownum / 25) %>% ceiling()
   
@@ -87,6 +87,7 @@ get_players <- function(rownum=400) {
     
     cursor <- cursor + 25
     if (df %>% nrow() < 25) {
+      print(glue("No more players to retrieve, exiting"))
       break
     }
     Sys.sleep(5)
@@ -103,7 +104,9 @@ get_players_page <- function(start) {
   
   players_resp$fantasy_content$users$`0`$user[[2]]$games$`0`$game[[2]][[1]] -> players_filtered
   
-  lapply(players_filtered[1:25], function(x) x[[1]][[1]] %>% 
+  count <- players_filtered$count
+  
+  lapply(players_filtered[1:count], function(x) x[[1]][[1]] %>% 
            flatten() %>% 
            as.data.frame(stringsAsFactors = F)) %>% 
     bind_rows() %>% 

### 2019-03-16 draftResearch_pt3.Rmd
Completed join fixes

--- 2019-03-12 draftResearch_pt3.Rmd
@@
 knitr::opts_chunk$set(echo = TRUE)
-library(tidyverse)
+options(tidyverse.quiet=TRUE)
+require(tidyverse)
+require(fuzzyjoin)
 ```
@@
 yahoo <- readRDS('data/players_position_eligibility.Rds') %>%
-  select(name.full, display_position, positions)
+  select(name.full, display_position, positions) %>%
+  mutate(name.full = chartr("áéóíñú", "aeoinu", name.full))
+
+yahoo$name.full[yahoo$name.full == 'Daniel Vogelbach'] <- "Dan Vogelbach"
+yahoo$name.full[yahoo$name.full == 'Shohei Ohtani (Batter)'] <- "Shohei Ohtani"
+yahoo$name.full[yahoo$name.full == 'Shin-soo Choo'] <- "Shin-Soo Choo"
+yahoo$name.full[yahoo$name.full == 'Seunghwan Oh'] <- "Seung Hwan Oh"
+yahoo$name.full[yahoo$name.full == 'JT Riddle'] <- "J.T. Riddle"
+yahoo$name.full[yahoo$name.full == 'AJ Reed'] <- "A.J. Reed"
 
@@
 
-df_raw <- fangraphs %>%
+fangraphs$Name[fangraphs$Name == 'Enrique Hernandez'] <- "Kike Hernandez"
+fangraphs$Name[fangraphs$Name == 'Cedric Mullins II'] <- "Cedric Mullins"
+fangraphs$Name[fangraphs$Name == 'Michael Soroka'] <- "Mike Soroka"
+fangraphs$Name[fangraphs$Name == 'Nathaniel Lowe'] <- "Nate Lowe"
+fangraphs$Name[fangraphs$Name == 'Nathan Karns'] <- "Nate Karns"
+fangraphs$Name[fangraphs$Name == 'Zach Britton'] <- "Zack Britton"
+fangraphs$Name[fangraphs$Name == 'Joshua James'] <- "Josh James"
+fangraphs$Name[fangraphs$Name == 'D.J. Stewart'] <- "DJ Stewart"
+
+df_join <- fangraphs %>%
   full_join(yahoo, by = c("Name" = "name.full"))
 
+df_join %>% 
+  count(is.na(display_position) & is.na(positions))
 ```
 
-```{r}
-df_raw %>%
-  filter(is.na(display_position)) %>%
-  select(Name, positions, ADP, ovrl_rank, z_sum) %>%
-  head(25)
-
-df_raw %>%
-  filter(Name == "Jose Ramirez") %>%
-  select(Name, positions, ADP, ovrl_rank, z_sum) %>%
-  head()
-
-fangraphs %>%
-  count()
-```
+#### Orphaned Records after join fixes
+1. Replaced accented characters to characters without accents
+2. Fuzzy join
+3. Yahoo API query for *2500* players (rather than 850)
+4. Duplicate Shohei Ohtani records, lack of pitching projections
+5. Multiple player minor name mismatches
 
 ### To Do
-1. Missing joins in yahoo data (i.e. Jose Ramirez) due to inconsistent accent marks on letters (and maybe other causes too?)
-2. Develop tiers of players (linear model? nearest neighbor?)
-3. Replacement level stuff (new section)
-4. Take averages of multiple projection sources? 
-5. Build team stats based on selections, available players per round?
+1. Develop tiers of players (linear model? nearest neighbor?)
+2. Replacement level stuff (new section)
+3. Take averages of multiple projection sources? 
+4. Build team stats based on selections, available players per round?

### 2019-03-16 draftResearch_pt3.Rmd
Added positions for subplotting

@@
 options(tidyverse.quiet=TRUE)
-require(tidyverse)
-require(fuzzyjoin)
+library(plotly)
+library(tidyverse)
 ```
@@
 df_join <- fangraphs %>%
-  full_join(yahoo, by = c("Name" = "name.full"))
+  full_join(yahoo, by = c("Name" = "name.full")) %>%
+  filter(!is.na(ADP))
 
@@
 
+```{r}
+df_join_positions <-
+  df_join %>%
+  filter(ovrl_rank <= 400) %>%
+  mutate(SP = grepl("SP", display_position)) %>%
+  mutate(RP = grepl("RP", display_position)) %>%
+  mutate(C = grepl("C", display_position)) %>%
+  mutate(`1B` = grepl("1B", display_position)) %>%
+  mutate(`2B` = grepl("2B", display_position)) %>%
+  mutate(SS = grepl("SS", display_position)) %>%
+  mutate(`3B` = grepl("3B", display_position)) %>%
+  mutate(OF = grepl("OF", display_position))
+
+df_join_positions %>% saveRDS("data/projections_with_positions.Rds")
+
+position_plot <- function(df, pos) {
+  pos_var <- enquo(pos)
+  title <- paste0(quo_name(pos_var))
+
+  df %>%
+    filter(!! pos_var) %>%
+    ggplot(aes(x=ADP, y=ovrl_rank, alpha = z_sum)) + 
+    geom_point(aes(text=Name)) +
+    scale_y_reverse() +
+    geom_abline(slope = -1)
+}
+
+sp_plot <- position_plot(df_join_positions, SP)
+rp_plot <- position_plot(df_join_positions, RP)
+c_plot <- position_plot(df_join_positions, C)
+`1b_plot` <- position_plot(df_join_positions, `1B`)
+`2b_plot` <- position_plot(df_join_positions, `2B`)
+ss_plot <- position_plot(df_join_positions, SS)
+`3b_plot` <- position_plot(df_join_positions, `3B`)
+of_plot <- position_plot(df_join_positions, OF)
+
+subplot(sp_plot , rp_plot , c_plot , `1b_plot`, `2b_plot`, ss_plot , `3b_plot`, of_plot, nrows = 3, shareX = TRUE, shareY = TRUE)
+```
+
+```{r}
+df_join_positions %>%
+  filter(SS) %>%
+  select(Name, ADP, ovrl_rank, z_sum, PA:z_OPS) %>%
+  View()
+```
+
 ### To Do

### 2019-03-17 draftResearch_pt3.Rmd
Starting tiering approach

@@
 
+# Compare positions
+
 ```{r}
@@
 
+Confirming keeper pick of Trevor Story...
 ```{r}
 df_join_positions %>%
-  filter(SS) %>%
+  filter(grepl("Story|Rendon",Name)) %>%
   select(Name, ADP, ovrl_rank, z_sum, PA:z_OPS) %>%
   View()
+```
+
+# Tiers
+
+```{r}
+SP <- df_join_positions %>%
+  filter(SP) %>%
+  mutate(position = "SP")
+
+RP <- df_join_positions %>%
+  filter(RP) %>%
+  mutate(position = "RP")
+
+C <- df_join_positions %>%
+  filter(C) %>%
+  mutate(position = "C")
+
+`1B` <- df_join_positions %>%
+  filter(`1B`) %>%
+  mutate(position = "1B")
+
+`2B` <- df_join_positions %>%
+  filter(`2B`) %>%
+  mutate(position = "2B")
+
+`3B` <- df_join_positions %>%
+  filter(`3B`) %>%
+  mutate(position = "3B")
+
+SS <- df_join_positions %>%
+  filter(SS) %>%
+  mutate(position = "SS")
+
+OF <- df_join_positions %>%
+  filter(OF) %>%
+  mutate(position = "OF")
+
+positions_tiers <- SP %>%
+	bind_rows(RP) %>%
+	bind_rows(C) %>%
+	bind_rows(`1B`) %>%
+	bind_rows(`2B`) %>%
+	bind_rows(`3B`) %>%
+	bind_rows(SS) %>%
+	bind_rows(OF ) %>%
+  select(Name, ADP, z_sum, ovrl_rank, position) %>%
+  mutate(round = ceiling(ADP/12))
+
+positions_tiers %>%
+  select(ADP, round) %>% head(25)
+
+positions_tiers %>%
+  filter(z_sum > 0) %>%
+  ggplot(aes(x=position, y=z_sum, alpha = desc(round))) +
+  geom_jitter(aes(text=Name), width = .3) -> pt
+
+ggplotly(pt)
+```
+
+### Players available in even numbered rounds
+I'm picking 11 of 12, which means I'll be getting the tail end of odd number rounds and getting the jump on even numbered rounds.
+So, let's just see what kind of team I can make up assuming two picks per even round.
+
+```{r}
+positions_tiers %>%
+  filter(round > 17) %>%
+  ggplot(aes(x=position, y=z_sum, alpha = desc(round))) +
+  geom_jitter(aes(text=Name), width = .3) -> pt_even
+
+ggplotly(pt_even)
+```
+```{r}
+
 ```
@@
 4. Build team stats based on selections, available players per round? 
+5. Exclude known keepers

### 2019-03-17 draftResearch_pt3.Rmd
Trying some draft results summary research

@@
 positions_tiers %>%
-  filter(round > 17) %>%
+  filter(round > 23) %>%
   ggplot(aes(x=position, y=z_sum, alpha = desc(round))) +
@@
 ```{r}
+
+drafted_players_190316 <- c(
+  "Chris Sale",
+  "Bryce Harper",
+  "Joey Votto",
+  "Carlos Carrasco",
+  "Justin Turner",
+  "Daniel Murphy",
+  "Joey Gallo",
+  "Josh Hader",
+  "Aaron Hicks",
+  "Carlos Santana",
+  "Trevor Story",
+  "Dellin Betances",
+  "David Robertson",
+  "Will Smith",
+  "Andrew Miller",
+  "Kyle Schwarber",
+  "Josh Bell",
+  "Soo Choo",
+  "Brandon Belt",
+  "Chad Green",
+  "Wilmer Flores",
+  "Keone Kela",
+  "Ryan Pressly"
+  )
+
+drafted_team_190316 <- df_join_positions %>%
+  filter(Name %in% drafted_players)
+
+drafted_batters_190316 <- drafted_team_190316 %>%
+  filter(type == "Batter") %>%
+  mutate(OB = PA * OBP,
+         SLG = OPS - OBP,
+         AB = PA - H,
+         TB = SLG * AB) %>%
+  summarize(PA = sum(PA),
+            H = sum(H),
+            HR = sum(HR),
+            R = sum(R),
+            RBI = sum(RBI),
+            BB = sum(BB),
+            SO = sum(SO),
+            SB = sum(SB),
+            OBP = sum(OB) / PA,
+            SLG = sum(TB) / sum(AB),
+            OPS = OBP + SLG
+            )
+
+drafted_pitchers_190316 <- drafted_team_190316 %>% 
+  filter(type == "Pitcher") %>%
+  mutate(ER = IP/9 * ERA,
+         runners = WHIP * IP) %>%
+  summarize(IP = sum(IP),
+            SV = sum(SV),
+            HLD = sum(HLD),
+            ERA = sum(ER) / (IP/9),
+            WHIP = sum(runners) / IP)
+
+drafted_team_stats_190316 <- drafted_batters_190316 %>%
+  bind_cols(drafted_pitchers_190316)
 

### 2019-03-20 draftPrep.Rmd
Bringing research into Draft Prep document

---
title: "2019 Draft Prep"
author: "Tom Kain"
date: "March 19, 2019"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intro
Rather than loosely apply fantasy baseball expert rankings for traditionally-scored roto leagues, I wanted to take a stab at developing my own rankings based on several factors:

1. league-custom categories used for H2H scoring
2. quality projection data with realistic expectations for variance
3. my preferences for draft strategy and team management throughout the year

To that end, the below document is a walk-through of the various research completed in other R Markdown files found in this repo.

### Scoring Categories
Here are the statistical categories which are used in our H2H categories, 12 team fantasy baseball league. Both team and category record are tracked throughout the year.

##### Batters
(@) Runs (R)
(@) Hits (H)
(@) Home runs (HR)
(@) Runs Batted In (RBI)
(@) Stolen Bases (SB)
(@) Walks (BB)
(@) Strikeouts (SO/K)
(@) On-Base Percentage (OBP)
(@) On-Base Plus Slugging (OPS)
(@) \*Errors (E)

##### Pitchers
(@) Saves (SV)
(@) Strikeouts (SO/K)
(@) Holds (HLD)
(@) Earned Run Average (ERA)
(@) Walks+Hits per Inning (WHIP)
(@) \*No Hitters (NH)
(@) \*Quality Starts (QS)
(@) \*Blown Saves (BS)
(@) \*Complete Games (CG)
(@) \*Shut outs (SHO)

Categories marked with an asterisk (\*) are not inluded in projection data.

### Projection Data
Based on prior personal success and their construction is the average of two separate projections, I've downloaded the latest Fangraphs Depth Chart preseason projections. This data is joined with Yahoo position eligibility data, since this is our league's host.

### Personal Strategy
After playing fantasy baseball for a few seasons and reading up from various experts (CBS Sports, The Athletic, etc), here are a few takeaways and preferences I prefer to take to heart at draft time as well as during the season.

(@) Batter projections tend to be more accurate than pitchers
(@) I tend to ride the waiver wire for starting pitching to take advantage of two-start weeks in an effort to find quality starts
(@) Since more batting categories are projected than pitching categories, I tend to put more emphasis on getting hitters early in drafts

### 2019-03-20 draftPrep.Rmd
Combined imports in progress

@@
 knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_knit$set(stop_on_error = 2L)
+source("R/yahoo_api.R")
+options(tidyverse.quiet=TRUE)
+library(tidyverse)
 ```
@@
 (@) Since more batting categories are projected than pitching categories, I tend to put more emphasis on getting hitters early in drafts
+
+# Data Set
+```{r importFangraphs, include=FALSE}
+fangraphs_pitchers <- "data/fangraphs_pitchers.Rds"
+fangraphs_batters <- "data/fangraphs_batters.Rds"
+pitchers_file <- "data/depthChartProjections_pitchers_20190308.csv"
+batters_file <- "data/depthChartProjections_batters_20190308.csv"
+
+if (file.exists(fangraphs_pitchers) && file.exists(fangraphs_batters)) {
+  pitchers <- readRDS(fangraphs_pitchers)
+  batters <- readRDS(fangraphs_batters)
+} else {
+  if (!file.exists(pitchers_file) || !file.exists(batters_file)) {
+  stop("Couldn't find fangraphs export data in the data folder")
+}
+
+  pitchers <- pitchers_file %>%
+    read_csv() %>%
+    unique() %>%
+    select(playerid, 
+           Name, 
+           Team,
+           ADP,
+           IP,
+           SV:ERA,
+           SO,
+           WHIP) %>%
+    mutate(type = "pitcher")
+
+  batters <- batters_file %>%
+    read_csv() %>%
+    unique() %>%
+    select(playerid,
+           Name,
+           Team,
+           ADP,
+           PA,
+           H,
+           HR:SO,
+           SB,
+           OBP,
+           OPS) %>%
+    mutate(type = "batter")
+
+  fangraphs <- pitchers %>% 
+    bind_rows(batters)
+
+  fangraphs$Name[fangraphs$Name == 'Enrique Hernandez'] <- "Kike Hernandez"
+  fangraphs$Name[fangraphs$Name == 'Cedric Mullins II'] <- "Cedric Mullins"
+  fangraphs$Name[fangraphs$Name == 'Michael Soroka'] <- "Mike Soroka"
+  fangraphs$Name[fangraphs$Name == 'Nathaniel Lowe'] <- "Nate Lowe"
+  fangraphs$Name[fangraphs$Name == 'Nathan Karns'] <- "Nate Karns"
+  fangraphs$Name[fangraphs$Name == 'Zach Britton'] <- "Zack Britton"
+  fangraphs$Name[fangraphs$Name == 'Joshua James'] <- "Josh James"
+  fangraphs$Name[fangraphs$Name == 'D.J. Stewart'] <- "DJ Stewart"
+
+  batters <- fangraphs %>%
+    filter(type="batter") %>%
+    select(-type)
+
+  pitchers <- fangraphs %>%
+    filter(type="pitcher") %>%
+    select(-type)
+
+  batters %>% saveRDS(fangraphs_batters)
+  pitchers %>% saveRDS(fangraphs_pitchers)
+}
+
+rm(c(fangraphs_pitchers, fangraphs_batters, pitchers_file, batters_file, fangraphs))
+```
+
+```{r importYahoo, include=FALSE}
+yahoo_file <- "data/players_position_eligibility.Rds"
+if (file.exists(yahoo_file)) {
+  yahoo_players <- readRDS(yahoo_file)
+} else {
+  get_players(2500) -> yahoo_players
+
+  position_columns <- yahoo_players %>%
+    select(starts_with("eligible_positions")) %>%
+    colnames()
+
+  yahoo_players %>%
+    mutate(positions = paste(!!! syms(position_columns), sep = "," )) %>%
+    mutate(positions = gsub('NA', '', positions)) %>%
+    mutate(positions = gsub("^,*|(?<=,),|,*$", "", positions, perl=T)) %>%
+    select(-(starts_with("eligible_positions"))) %>%
+  select(name.full, display_position, positions) %>%
+  mutate(name.full = chartr("áéóíñú", "aeoinu", name.full))  -> yahoo_players
+
+  yahoo_players$name.full[yahoo_players$name.full == 'Daniel Vogelbach'] <- "Dan Vogelbach"
+  yahoo_players$name.full[yahoo_players$name.full == 'Shohei Ohtani (Batter)'] <- "Shohei Ohtani"
+  yahoo_players$name.full[yahoo_players$name.full == 'Shin-soo Choo'] <- "Shin-Soo Choo"
+  yahoo_players$name.full[yahoo_players$name.full == 'Seunghwan Oh'] <- "Seung Hwan Oh"
+  yahoo_players$name.full[yahoo_players$name.full == 'JT Riddle'] <- "J.T. Riddle"
+  yahoo_players$name.full[yahoo_players$name.full == 'AJ Reed'] <- "A.J. Reed"
+
+  yahoo_players %>% 
+    saveRDS(yahoo_file)
+}
+rm(yahoo_file)
+```

### 2019-03-22 draftPrep.Rmd
Work in progress switching to latest projections

@@
 ##### Batters
-(@) Runs (R)
-(@) Hits (H)
-(@) Home runs (HR)
-(@) Runs Batted In (RBI)
-(@) Stolen Bases (SB)
-(@) Walks (BB)
-(@) Strikeouts (SO/K)
-(@) On-Base Percentage (OBP)
-(@) On-Base Plus Slugging (OPS)
-(@) \*Errors (E)
+- Runs (R)
+- Hits (H)
+- Home runs (HR)
+- Runs Batted In (RBI)
+- Stolen Bases (SB)
+- Walks (BB)
+- Strikeouts (SO/K)
+- On-Base Percentage (OBP)
+- On-Base Plus Slugging (OPS)
+- \*Errors (E)
 
 ##### Pitchers
-(@) Saves (SV)
-(@) Strikeouts (SO/K)
-(@) Holds (HLD)
-(@) Earned Run Average (ERA)
-(@) Walks+Hits per Inning (WHIP)
-(@) \*No Hitters (NH)
-(@) \*Quality Starts (QS)
-(@) \*Blown Saves (BS)
-(@) \*Complete Games (CG)
-(@) \*Shut outs (SHO)
+- Saves (SV)
+- Strikeouts (SO/K)
+- Holds (HLD)
+- Earned Run Average (ERA)
+- Walks+Hits per Inning (WHIP)
+- \*No Hitters (NH)
+- \*Quality Starts (QS)
+- \*Blown Saves (BS)
+- \*Complete Games (CG)
+- \*Shut outs (SHO)
 
-Categories marked with an asterisk (\*) are not inluded in projection data.
+*Categories marked with an asterisk (\*) are not inluded in projection data.*
 
@@
 
-(@) Batter projections tend to be more accurate than pitchers
-(@) I tend to ride the waiver wire for starting pitching to take advantage of two-start weeks in an effort to find quality starts
-(@) Since more batting categories are projected than pitching categories, I tend to put more emphasis on getting hitters early in drafts
+1. Batter projections tend to be more accurate than pitchers
+2. I tend to ride the waiver wire for starting pitching to take advantage of two-start weeks in an effort to find quality starts
+3. Since more batting categories are projected than pitching categories, I tend to put more emphasis on getting hitters early in drafts
 
@@
 fangraphs_batters <- "data/fangraphs_batters.Rds"
-pitchers_file <- "data/depthChartProjections_pitchers_20190308.csv"
-batters_file <- "data/depthChartProjections_batters_20190308.csv"
+pitchers_file <- "data/depthChartProjections_pitchers_20190321.csv"
+batters_file <- "data/depthChartProjections_batters_20190321.csv"
 
-if (file.exists(fangraphs_pitchers) && file.exists(fangraphs_batters)) {
-  pitchers <- readRDS(fangraphs_pitchers)
-  batters <- readRDS(fangraphs_batters)
-} else {
 if (!file.exists(pitchers_file) || !file.exists(batters_file)) {
@@
 
-  pitchers <- pitchers_file %>%
+pitchers <- 
+  pitchers_file %>%
   read_csv() %>%
   unique() %>% 
-    select(playerid, 
-           Name, 
-           Team,
-           ADP,
-           IP,
-           SV:ERA,
-           SO,
-           WHIP) %>%
   mutate(type = "pitcher")
@@
   unique() %>%
-    select(playerid,
-           Name,
-           Team,
-           ADP,
-           PA,
-           H,
-           HR:SO,
-           SB,
-           OBP,
-           OPS) %>%
   mutate(type = "batter")
@@
 batters <- fangraphs %>%
-    filter(type="batter") %>%
-    select(-type)
+  filter(type=="batter") %>%
+  select(playerid,
+         Name,
+         Team,
+         ADP,
+         PA,
+         H,
+         HR:SO,
+         SB,
+         OBP,
+         OPS)
 
 pitchers <- fangraphs %>%
-    filter(type="pitcher") %>%
-    select(-type)
+  filter(type=="pitcher") %>%
+  select(playerid,
+         Name,
+         Team,
+         ADP,
+         IP,
+         SV:ERA,
+         SO,
+         WHIP)
 
@@
 pitchers %>% saveRDS(fangraphs_pitchers)
-}
 
-rm(c(fangraphs_pitchers, fangraphs_batters, pitchers_file, batters_file, fangraphs))
+suppressWarnings(
+  rm(fangraphs_pitchers, fangraphs_batters, pitchers_file, batters_file) 
+)
 ```
@@
 ```
+
+```{r}
+players_master <- fangraphs %>%
+  full_join(yahoo_players, by = c("Name" = "name.full")) %>%
+  filter(!is.na(ADP))
+
+players_master %>% 
+  mutate(orphan = is.na(display_position) & is.na(positions)) %>%
+  filter(orphan) -> orphans
+
+if (!is.na(orphans) && nrow(orphans) > 0) {
+  stop(paste0("Join resulted in ",nrow(orphans)," orphaned players"))
+}
+
+orphans %>% select(Name)
+fangraphs %>% filter(grepl("Genesis",Name))
+yahoo_players %>% filter(grepl("Cabrera",name.full))
+```

### 2019-03-23 draftPrep.Rmd
Draft prep document in progress - up to position scarcity

@@
 source("R/yahoo_api.R")
+source("R/z_scores.R")
 options(tidyverse.quiet=TRUE)
+library(knitr)
+library(plotly)
 library(tidyverse)
@@
 fangraphs <- pitchers %>% 
-  bind_rows(batters)
+  bind_rows(batters) %>%
+  filter(ADP < 999)
 
@@
 fangraphs$Name[fangraphs$Name == 'D.J. Stewart'] <- "DJ Stewart"
+fangraphs$Name[fangraphs$Name == 'Daniel Poncedeleon'] <- "Daniel Ponce de Leon"
 
@@
 
-  yahoo_players$name.full[yahoo_players$name.full == 'Daniel Vogelbach'] <- "Dan Vogelbach"
   yahoo_players$name.full[yahoo_players$name.full == 'Shohei Ohtani (Batter)'] <- "Shohei Ohtani"
@@
   yahoo_players$name.full[yahoo_players$name.full == 'AJ Reed'] <- "A.J. Reed"
+  yahoo_players$name.full[yahoo_players$name.full == 'Dan Vogelbach'] <- "Daniel Vogelbach"
 
@@
 
-```{r}
+```{r include=FALSE}
 players_master <- fangraphs %>%
   full_join(yahoo_players, by = c("Name" = "name.full")) %>%
-  filter(!is.na(ADP))
+  filter(!is.na(ADP)) %>%
+  filter(ADP < 999)
 
@@
 }
+```
+Here's a look at a few rows from each starting data set.
 
-orphans %>% select(Name)
-fangraphs %>% filter(grepl("Genesis",Name))
-yahoo_players %>% filter(grepl("Cabrera",name.full))
+##### Batters
+```{r echo=FALSE}
+batters <- players_master %>%
+  filter(type == "batter") %>%
+  select(type, Name, Team, ADP, 
+         PA, R, H, HR, RBI, SB, BB, SO, OBP, OPS)
+
+batters %>%
+  select(-type) %>%
+  head()  %>%
+  kable()
 ```
+
+##### Pitchers
+```{r echo=FALSE}
+pitchers <- players_master %>%
+  filter(type == "pitcher") %>%
+  select(type, Name, Team, ADP,
+         IP, SV, SO, HLD, ERA, WHIP)
+
+pitchers %>%
+  select(-type) %>%
+  head()  %>%
+  kable()
+```
+
+# Generate Rankings
+I need to evaluate each player with a single metric that takes into account his relative rank in each scoring category.
+To do this, I'll generate z-scores for each scoring category via normalization, then sum the z-scores up per player to rank them.
+For rate statistics (i.e.
+OBP), the z_scores are controlled for batter's plate appearances (PA) and pitcher's innings pitched (IP).
+Here are the same batters with their z_scores computed:
+
+```{r echo=FALSE}
+batters %>%
+  z_score_count(R) %>%
+  z_score_count(H) %>%
+  z_score_count(HR) %>%
+  z_score_count(RBI) %>%
+  z_score_count(SB) %>%
+  z_score_count(BB) %>%
+  z_score_count(SO, TRUE) %>%
+  z_score_rate(OBP, PA) %>%
+  z_score_rate(OPS, PA) %>%
+  mutate(
+    z_sum = pmap_dbl(
+      select(., starts_with("z_")), 
+      sum
+    )
+  ) -> batters
+
+batters %>%
+  head() %>%
+  select(Name, Team, ADP, 
+         z_H:z_sum) %>%
+  kable()
+```
+
+I experimented with some additional adjustment for pitchers since there are four categories for which I don't have projections (note to self for the future, take some time to develop Quality Start projections).
+For now, no additional adjustment - here are the same pitchers with their z_scores.
+
+```{r echo=FALSE}
+pitchers %>%
+  z_score_count(SV) %>%
+  z_score_count(SO) %>%
+  z_score_count(HLD) %>%
+  z_score_rate(ERA, IP, TRUE) %>%
+  z_score_rate(WHIP, IP, TRUE) %>%
+  mutate(
+    z_sum = pmap_dbl(
+      select(., starts_with("z_")), 
+      sum
+    )
+  ) -> pitchers
+
+pitchers %>%
+  head() %>%
+  select(Name, Team, ADP, 
+         z_SV:z_sum) %>%
+  kable()
+```
+
+Let's compare the z_sum scores with average draft position (ADP).
+
+```{r echo=FALSE}
+z_sums <- pitchers %>%
+  select(Name, type, ADP, z_sum)
+
+batters %>%
+  select(Name, type, ADP, z_sum) %>%
+  bind_rows(z_sums) %>%
+  arrange(desc(z_sum)) %>%
+  mutate(z_rank = row_number()) -> z_sums
+
+z_sums %>%
+  ggplot(aes(x=ADP,y=z_rank,color=type)) +
+  geom_point(aes(text=Name)) +
+  geom_abline(slope=-1) +
+  scale_y_reverse() -> p
+
+ggplotly(p)
+```
+
+Some observations from this plot:
+- Batters are in general weighed higher than pitchers since there are more categories with which to add to the z_sum
+- Andrew Miller-like relievers are valued higher than ADP due to their high inning total and low ratio stats (ERA, WHIP)
+- Ace starting pitchers and traditional closers are valued less than ADP despite their relative scarcity. 
+  - Aces are the players most affected by not adjusting the z_score weighting for pitchers
+  - Even with adjustment, tradtional closers have a lesser inning count nor have significant input in other categories to adjust their z_score very much
+
+Thus far this is algining with my general strategy.
+These rankings value hitters highly, identify relievers to draft late, and leave it up to me to scrape for some starting pitchers to spring up over the course of the year.
+With this approach, I should be able to meaningfully attack most of the batting categories and a few of the pitching categories (i.e.
+ERA, WHIP, HLD), hopefully translating to a a weekly lead in categories.
+
+### Position Scarcity
+
+What is not yet covered is batting lineup slots and offensive position scarcity.
+For example, catcher is traditionally very light on talent, but even the best offensive catcher is unlikely to crack the top 20.
+Here's a catcher that I happen to know is projected to be (one of) the best this year:
+```{r echo=FALSE}
+z_sums %>%
+  select(Name, z_rank) %>%
+  filter(grepl("Realmuto", Name)) %>%
+  inner_join(batters, by = "Name") %>%
+  select(Name, ADP, z_rank, z_sum) %>%
+  kable()
+```
+
+J.T.
+Realmuto is going before the end of the third round yet by my ranking he shouldn't be going before the eleventh.
+However, I bet most catchers available to draft would have a negative z_sum, meaning they could be negating the benefit of taking higher z_sums from other positions with less bad options later in the draft.
+Let's confirm that.

### 2019-03-23 draftPrep.Rmd
Boxplots and keepers

@@
   filter(type == "batter") %>%
-  select(type, Name, Team, ADP, 
-         PA, R, H, HR, RBI, SB, BB, SO, OBP, OPS)
+  select(Name, Team, ADP, type, display_position, positions,
+         PA, R, H, HR, RBI, SB, BB, SO, OBP, OPS,)
 
 batters %>%
-  select(-type) %>%
+  select(-(type:positions)) %>%
   head()  %>%
@@
   filter(type == "pitcher") %>%
-  select(type, Name, Team, ADP,
+  select(Name, Team, ADP, type, display_position, positions,
          IP, SV, SO, HLD, ERA, WHIP)
@@
 pitchers %>%
-  select(-type) %>%
+  select(-(type:positions)) %>%
   head()  %>%
@@
 Let's confirm that.
+
+```{r include=FALSE}
+
+z_sums %>%
+  filter(type == "batter") %>%
+  select(Name, z_rank) %>%
+  full_join(batters, by = "Name") %>% 
+  mutate(C = grepl("C", display_position)) %>%
+  mutate(`1B` = grepl("1B", positions)) %>%
+  mutate(`2B` = grepl("2B", positions)) %>%
+  mutate(SS = grepl("SS", positions)) %>%
+  mutate(`3B` = grepl("3B", positions)) %>%
+  mutate(LF = grepl("LF", positions)) %>% 
+  mutate(CF = grepl("CF", positions)) %>% 
+  mutate(RF = grepl("RF", positions)) -> batters_ranked
+
+z_sums %>%
+  filter(type == "pitcher") %>%
+  select(Name, z_rank) %>%
+  full_join(pitchers, by = "Name") %>%
+  mutate(SP = grepl("SP", positions)) %>%
+  mutate(RP = grepl("RP", positions)) -> pitchers_ranked
+
+C <- batters_ranked %>%
+  filter(C) %>%
+  mutate(position = "C")
+
+`1B` <- batters_ranked %>%
+  filter(`1B`) %>%
+  mutate(position = "1B")
+
+`2B` <- batters_ranked %>%
+  filter(`2B`) %>%
+  mutate(position = "2B")
+
+`3B` <- batters_ranked %>%
+  filter(`3B`) %>%
+  mutate(position = "3B")
+
+SS <- batters_ranked %>%
+  filter(SS) %>%
+  mutate(position = "SS")
+
+LF <- batters_ranked %>%
+  filter(LF) %>%
+  mutate(position = "LF")
+
+CF <- batters_ranked %>%
+  filter(LF) %>%
+  mutate(position = "CF")
+
+RF <- batters_ranked %>%
+  filter(RF) %>%
+  mutate(position = "RF")
+
+SP <- pitchers_ranked %>% 
+  filter(SP) %>% 
+  mutate(position = "SP")
+
+RP <- pitchers_ranked %>% 
+  filter(RP) %>% 
+  mutate(position = "RP")
+
+pitcher_positions_ranked <- SP %>%
+  bind_rows(RP) %>%
+  select(Name, ADP, z_sum, position) %>%
+  unique()
+
+positions_ranked <- C %>%
+  bind_rows(`1B`) %>%
+	bind_rows(`2B`) %>%
+	bind_rows(`3B`) %>%
+	bind_rows(SS) %>%
+  bind_rows(LF) %>% 
+  bind_rows(CF) %>% 
+  bind_rows(RF) %>% 
+  select(Name, ADP, z_sum, position) %>% 
+  unique() %>%
+  bind_rows(pitcher_positions_ranked) %>%
+  arrange(z_sum %>% desc) %>%
+  mutate(round = ceiling(ADP/12),
+         z_rank = row_number(),
+         position = fct_relevel(position, "C","1B", "2B","3B","SS","LF","CF","RF","SP","RP"))
+
+positions_ranked %>%
+  filter(ADP <= 300,
+         !position %in% c("SP","RP")) %>%
+  ggplot(aes(x=position, y=z_sum)) +
+  geom_boxplot() +
+  geom_jitter(aes(text=Name, alpha=desc(round)), width = .2) +
+  geom_abline(slope=0, intercept = 0, linetype = "dotted") +
+  labs(x="Position",
+       y="Z_Points",
+       title="Batter value by position, top 300 drafted") -> pt
+
+ggplotly(pt)
+```
+
+This highlights how poor the catcher position is.
+The upper outliers at the position are roughly equivlanet to the median value of most other positions.
+If I don't get one of the top four catchers, I'll need to at least make up the 4 z_points somewhere else.
+That said, the projections indicate that I would do nearly as well with Yasmani Grandal or Buster Posey (rounds 13 and 10, respectively) as I would with the higher in demand J.T.
+Realmuto and Gary Sanchez (rounds 4 and 5 respectively).
+
+# Draft Prep
+Armed with this information, here's what I need before the draft:
+1. Exclude known keepers from this list - no sense planning on a player being available if they won't be
+2. Add pitchers to the above plot so that I can...
+3. ...put together a basic plan of attack for the draft
+4. Generate a cheat sheet document to use for the draft
+
+```{r echo=FALSE}
+
+keepers <- c(
+  "Justin turner",
+  "Miles Mikolas",
+  "Whit Merrifield",
+  "Archie Bradley",
+  "Patrick Corbin",
+  "Matt Carpenter",
+  "Blake Treinen",
+  "Ronald Acuna Jr.",
+  "Blake Snell",
+  "Lorenzo Cain",
+  "Trevor Story",
+  "Andrew Benintendi",
+  "Mike Clevinger"
+)
+
+positions_ranked %>%
+  mutate(keeper = (Name %in% keepers)) -> positions_ranked_with_keepers
+
+positions_ranked_with_keepers %>%
+  filter(ADP <= 300,
+         !keeper) %>%
+  ggplot(aes(x=position, y=z_sum)) +
+  geom_boxplot() +
+  geom_jitter(aes(text=Name, alpha=desc(round)), width = .2) +
+  geom_abline(slope=0, intercept = 0, linetype = "dotted") +
+  labs(x="Position",
+       y="Z_Points",
+       title="Player value by position, top 300 drafted") -> ptk
+
+ggplotly(ptk)
+```

### 2019-03-23 draftPrep.Rmd
Minor knitr adjustments

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
 knitr::opts_knit$set(stop_on_error = 2L)
@@
 Some observations from this plot:
+
 - Batters are in general weighed higher than pitchers since there are more categories with which to add to the z_sum
@@
 
-```{r include=FALSE}
+```{r echo=FALSE}
 
@@
 Armed with this information, here's what I need before the draft:
+
 1. Exclude known keepers from this list - no sense planning on a player being available if they won't be

### 2019-03-23 draftPrep.Rmd
Starting draft approach

@@
 output:
+  pdf_document: default
   html_document:
@@
 CF <- batters_ranked %>%
-  filter(LF) %>%
+  filter(CF) %>%
   mutate(position = "CF")
@@
 keepers <- c(
-  "Justin turner",
+  "Justin Turner",
   "Miles Mikolas",
@@
        y="Z_Points",
-       title="Player value by position, top 300 drafted") -> ptk
+       title="Player value by position, top 300 drafted, keepers excluded ") -> ptk
 
@@
 ```
+
+*Note, one of the excluded keepers is mine - SS Trevor Story, round 11*
+
+I'd like to put together a plan of attack where, for each round, I identify the kinds of players available at the highest projected scoring, perhaps in tiers of z_scores: >= 15, 10-15, 5-10, etc.
+Let's start with the upper tier:
+
+##### Elite Tier (z_score >= 15)
+
+```{r echo = FALSE}
+positions_ranked_with_keepers %>%
+  filter(z_sum >= 15) %>%
+  select(Name, z_sum, ADP, round) %>%
+  unique() %>%
+  arrange(ADP) %>%
+  kable()
+```
+
+We should assume Trout, Betts, and Ramirez will go 1,2,3, or at least not make it to me at 11.
+However, according to the projection data, Bryce Harper & Juan Soto could be available, potentially worth getting at the rounds 1 & 2 turn.

### 2019-03-23 draftPrep.Rmd
Still working on the tiers and approach

@@
 output:
-  pdf_document: default
   html_document:
     df_print: paged
+  pdf_document: default
 editor_options:
@@
 
+```{r echo=FALSE}
+positions_ranked_with_keepers %>%
+  filter(!keeper,
+         ADP <=300) %>%
+  arrange(round, position) %>%
+  mutate(round = as_factor(round)) %>%
+  mutate(round = fct_inseq(round, ordered = TRUE)) %>%
+  ggplot(aes(x=round,y=z_sum,alpha=desc(z_rank),size=z_sum,color=position)) +
+  geom_jitter(aes(text=Name)) +
+  facet_wrap(~ position) -> rv
+
+ggplotly(rv)
+```
 *Note, one of the excluded keepers is mine - SS Trevor Story, round 11*
@@
 positions_ranked_with_keepers %>%
-  filter(z_sum >= 15) %>%
+  filter(z_sum >= 15, !keeper) %>%
   select(Name, z_sum, ADP, round) %>%
@@
 However, according to the projection data, Bryce Harper & Juan Soto could be available, potentially worth getting at the rounds 1 & 2 turn.
+
+##### Damn Good Tier (z_score between 10 and 15)
+
+```{r echo = FALSE}
+positions_ranked_with_keepers %>%
+  filter(between(z_sum,10,15), !keeper) %>%
+  ggplot(aes(position,z_sum,size=round,color=Name)) +
+  geom_jitter(aes(text=Name), width = .2) -> dgt
+
+ggplotly(dgt)
+
+positions_ranked_with_keepers %>%
+  filter(between(z_sum,10,15), !keeper) %>%
+  count(position) %>%
+  arrange(desc(n)) %>%
+  kable()
+```
+
+At the top of this tier are two first basemen (Votto, Rizzo) and two outfielders (Yelich, Martinez).
+Votto has been going late enough (round 6) that I can afford to wait, giving me some fallback options in the OF if Harper and Soto are not available first.
+Although Bregman and Judge are next up, I'm thinking Jose Altuve might be a good pick since 2B is relatively scarce compared to OF and 3B.
+
+##### Pretty Good Tier
+
+```{r echo=FALSE}
+positions_ranked_with_keepers %>%
+  filter(between(z_sum,5,10), !keeper) %>%
+  ggplot(aes(position,z_sum,size=round,color=Name)) +
+  geom_jitter(aes(text=Name), width = .2) -> dgt
+
+ggplotly(dgt)
+
+positions_ranked_with_keepers %>%
+  filter(between(z_sum,5,10), !keeper) %>%
+  count(position) %>%
+  arrange(desc(n)) %>%
+  kable()
+```

### 2019-03-23 R/z_scores.R
Moved z_score functions to separate script

@@ -1,0 +1,46 @@
+z_score_count <- function(df, stat, invert=FALSE, multiplier=1) {
+  stat <- enquo(stat)
+  col_nm <- paste0("z_", quo_name(stat))
+  
+  df <- df %>% 
+    mutate(s_z = (!! stat - mean(!! stat)) / sd(!! stat)) 
+  
+  if (invert) {
+    df %>%
+      mutate(s_z = -s_z) -> df
+  }
+  
+  if (multiplier != 1) {
+    df %>%
+      mutate(s_z = multiplier * s_z) -> df
+  }
+  
+  df %>% 
+    mutate(s_z = round(s_z,2)) %>%
+    rename(!! col_nm := s_z)
+} 
+
+z_score_rate <- function(df, stat, quantity, invert=FALSE, multiplier = 1) {
+  stat <- enquo(stat)
+  quantity <- enquo(quantity)
+  col_nm <- paste0("z_",quo_name(stat))
+  
+  df %>%
+    mutate(s_q = (!! stat - mean(!! stat)) * !! quantity) %>%
+    mutate(s_z = (s_q - mean(s_q)) / sd(s_q)) -> df
+  
+  if (invert) {
+    df %>%
+      mutate(s_z = -s_z) -> df
+  }
+  
+  if (multiplier != 1) {
+    df %>%
+      mutate(s_z = multiplier * s_z) -> df
+  }
+  
+  df %>%
+    mutate(s_z = round(s_z, 2)) %>%
+    rename(!! col_nm := s_z) %>%
+    select(-s_q)
+}

### 2019-03-23 draftPrep.Rmd
Draft data set complete

--- 2019-03-23 draftPrep.Rmd
@@
 # Draft Prep
-Armed with this information, here's what I need before the draft:
-
-1. Exclude known keepers from this list - no sense planning on a player being available if they won't be
-2. Add pitchers to the above plot so that I can...
-3. ...put together a basic plan of attack for the draft
-4. Generate a cheat sheet document to use for the draft
+The above plot is reproduced below to exclude known keepers and include pitchers.
 
@@
 
+Below is a plot of z_score by round so I can identify in which rounds to target specific positions, particularly once we pass to below a z_score of 10. 
+```{r echo=FALSE}
+positions_ranked_with_keepers %>%
+  filter(!keeper,
+         ADP <=300) %>%
+  group_by(round, position) %>%
+  summarize(low = min(z_sum),
+            mid = median(z_sum),
+            high = max(z_sum),
+            n = n()) %>%
+  arrange(round) %>%
+  ggplot(aes(y=mid, x=round, color=n)) +
+  geom_pointrange(aes(ymax = high,ymin = low)) +
+  labs(x="Round (ADP)", 
+        y="Z_Score") +
+  facet_wrap(~ position) -> rv
+
+ggplotly(rv)
+```
 *Note, one of the excluded keepers is mine - SS Trevor Story, round 11*
 
-I'd like to put together a plan of attack where, for each round, I identify the kinds of players available at the highest projected scoring, perhaps in tiers of z_scores: >= 15, 10-15, 5-10, etc.
-Let's start with the upper tier:
+Here's the data set with which I'll print a little cheat sheet (or interactive app?) for the draft.
 
-##### Elite Tier (z_score >= 15)
+```{r echo=FALSE}
+batters_ranked %>%
+  select(Name, z_rank, z_sum, ADP, positions) -> batters_draft
 
-```{r echo = FALSE}
-positions_ranked_with_keepers %>%
-  filter(z_sum >= 15) %>%
-  select(Name, z_sum, ADP, round) %>%
-  unique() %>%
-  arrange(ADP) %>%
+batters_draft %>%
+  mutate(rn = row_number()) %>% 
+  filter(grepl("Robertson",Name)) %>%
+  select(rn) %>%
+  pull() -> robertson_drop
+
+batters_draft %>%
+  mutate(rn = row_number()) %>% 
+  filter(grepl("Jose Ramirez",Name)) %>%
+  select(rn) %>%
+  pull() -> jramirez_drop
+
+rows_drop <- c(robertson_drop[-1],jramirez_drop[-1])
+
+batters_draft %>%
+  slice(-rows_drop) -> batters_draft
+
+pitchers_ranked %>%
+  select(Name, z_rank, z_sum, ADP, positions) -> pitchers_draft
+
+pitchers_draft %>%
+  mutate(rn = row_number()) %>%
+  filter(grepl("Cody Reed",Name)) %>%
+  select(rn) %>%
+  pull() -> reed_drop
+
+pitchers_draft %>%
+  mutate(rn = row_number()) %>%
+  filter(grepl("Will Smith",Name)) %>%
+  select(rn) %>%
+  pull() -> smith_drop
+
+rows_drop <- c(smith_drop[-1], reed_drop[-2])
+
+pitchers_draft %>%
+  slice(-rows_drop) -> pitchers_draft
+
+rm(rows_drop, robertson_drop, jramirez_drop, reed_drop, smith_drop)
+
+pitchers_draft %>%
+  bind_rows(batters_draft) %>%
+  mutate(round = ceiling(ADP/12)) %>%
+  select(z_rank, Name, z_sum, round, ADP, positions) %>%
+  arrange(z_rank) -> draft_df
+
+draft_df %>% saveRDS("data/draft_dataset.Rds")
+
+draft_df %>%
+  head(25) %>%
   kable()
 ```
-
-We should assume Trout, Betts, and Ramirez will go 1,2,3, or at least not make it to me at 11.
-However, according to the projection data, Bryce Harper & Juan Soto could be available, potentially worth getting at the rounds 1 & 2 turn.

### 2019-03-23 draftPrep.Rmd
Hopefully the last core data changes before draft

@@
 fangraphs_batters <- "data/fangraphs_batters.Rds"
-pitchers_file <- "data/depthChartProjections_pitchers_20190321.csv"
-batters_file <- "data/depthChartProjections_batters_20190321.csv"
+pitchers_file <- "data/depthChartProjections_pitchers_20190323.csv"
+batters_file <- "data/depthChartProjections_batters_20190323.csv"
 
@@
   mutate(round = ceiling(ADP/12)) %>%
-  select(z_rank, Name, z_sum, round, ADP, positions) %>%
-  arrange(z_rank) -> draft_df
+  arrange(z_sum %>% desc) %>%
+  mutate(z_rank = row_number()) %>%
+  select(z_rank, Name, z_sum, round, ADP, positions) -> draft_df
 

### 2019-03-23 draftPrep.Rmd
Forgot to exclude keepers

@@
 positions_ranked_with_keepers %>%
+positions_ranked_with_keepers %>%
   filter(!keeper,
@@
   bind_rows(batters_draft) %>%
-  mutate(round = ceiling(ADP/12)) %>%
+  mutate(round = ceiling(ADP/12),
+         keeper = (Name %in% keepers)) %>%
+  filter(!keeper) %>%
   arrange(z_sum %>% desc) %>%
@@
 draft_df %>% saveRDS("data/draft_dataset.Rds")
-
-draft_df %>%
-  head(25) %>%
-  kable()
 ```

### 2019-03-23 draft_helper/app.R
Starting cheat sheet app

@@ -1,0 +1,56 @@
+library(shiny)
+library(plotly)
+library(tidyverse)
+
+main_df <- readRDS("../data/draft_dataset.Rds")
+positions_df <- readRDS("../data/positions_ranked_with_keepers.Rds")
+
+# Define UI for application that draws a histogram
+ui <- fluidPage(
+   
+   # Application title
+   titlePanel("Tom's Draft Cheat Sheet"),
+   
+   # Sidebar
+   sidebarLayout(
+      sidebarPanel(
+      ),
+      
+      # Main Panel
+      mainPanel(
+        tabsetPanel(
+          tabPanel("Table", dataTableOutput("table")),
+          tabPanel("Plot", plotlyOutput("plot"))
+        )
+      )
+   )
+)
+
+# Server
+server <- function(input, output) {
+   
+   output$plot <- renderPlotly({
+      positions_df %>%
+       group_by(round, position) %>%
+       summarize(low = min(z_sum),
+                 mid = median(z_sum) %>% round(2),
+                 high = max(z_sum),
+                 n = n()) %>%
+       arrange(round) %>%
+       ggplot(aes(y=mid, x=round, color=n)) +
+       geom_pointrange(aes(ymax = high,ymin = low)) +
+       labs(x="Round (ADP)", 
+            y="Z_Score") +
+       facet_wrap(~ position) -> rv
+     
+     ggplotly(rv)
+   })
+   
+   output$table <- renderDataTable({
+     main_df
+   })
+}
+
+# Run the application 
+shinyApp(ui = ui, server = server)
+

### 2019-03-23 draftPrep.Rmd
Functioning cheat sheet app, though working on a minor bug or two

--- 2019-03-23 draftPrep.Rmd
@@
 batters_ranked %>%
-  select(Name, z_rank, z_sum, ADP, positions) -> batters_draft
+  select(Name, z_rank, z_sum, ADP, positions, display_position) -> batters_draft
 
@@
 pitchers_ranked %>%
-  select(Name, z_rank, z_sum, ADP, positions) -> pitchers_draft
+  select(Name, z_rank, z_sum, ADP, positions, display_position) -> pitchers_draft
 
@@
   bind_rows(batters_draft) %>%
-  mutate(round = ceiling(ADP/12)) %>%
+  mutate(round = ceiling(ADP/12),
+         keeper = (Name %in% keepers)) %>%
+  filter(!keeper) %>%
   arrange(z_sum %>% desc) %>%
   mutate(z_rank = row_number()) %>%
-  select(z_rank, Name, z_sum, round, ADP, positions) -> draft_df
+  select(z_rank, Name, z_sum, round, ADP, positions, display_position) -> draft_df
 
@@
 draft_df %>%
+  select(-display_position) %>%
   head(25) %>%

### 2019-03-23 draft_helper/app.R

@@ -2,8 +2,72 @@ library(shiny)
 library(plotly)
 library(tidyverse)
 
+source("chooser.R")
+
 main_df <- readRDS("../data/draft_dataset.Rds")
-positions_df <- readRDS("../data/positions_ranked_with_keepers.Rds")
+positions_df <- main_df %>%
+  mutate(C = grepl("C", display_position)) %>%
+  mutate(`1B` = grepl("1B", positions)) %>%
+  mutate(`2B` = grepl("2B", positions)) %>%
+  mutate(SS = grepl("SS", positions)) %>%
+  mutate(`3B` = grepl("3B", positions)) %>%
+  mutate(LF = grepl("LF", positions)) %>% 
+  mutate(CF = grepl("CF", positions)) %>% 
+  mutate(RF = grepl("RF", positions)) %>%
+  mutate(SP = grepl("SP", positions)) %>%
+  mutate(RP = grepl("RP", positions)) 
+
+C <- positions_df %>%
+  filter(C) %>%
+  mutate(position = "C")
+
+`1B` <- positions_df %>%
+  filter(`1B`) %>%
+  mutate(position = "1B")
+
+`2B` <- positions_df %>%
+  filter(`2B`) %>%
+  mutate(position = "2B")
+
+`3B` <- positions_df %>%
+  filter(`3B`) %>%
+  mutate(position = "3B")
+
+SS <- positions_df %>%
+  filter(SS) %>%
+  mutate(position = "SS")
+
+LF <- positions_df %>%
+  filter(LF) %>%
+  mutate(position = "LF")
+
+CF <- positions_df %>%
+  filter(CF) %>%
+  mutate(position = "CF")
+
+RF <- positions_df %>%
+  filter(RF) %>%
+  mutate(position = "RF")
+
+SP <- positions_df %>% 
+  filter(SP) %>% 
+  mutate(position = "SP")
+
+RP <- positions_df %>% 
+  filter(RP) %>% 
+  mutate(position = "RP")
+
+positions_df_ex <- C %>%
+  bind_rows(`1B`) %>%
+  bind_rows(`2B`) %>%
+  bind_rows(`3B`) %>%
+  bind_rows(SS) %>%
+  bind_rows(LF) %>% 
+  bind_rows(CF) %>% 
+  bind_rows(RF) %>% 
+  bind_rows(SP) %>%
+  bind_rows(RP) %>%
+  unique()
 
[…]

### 2019-03-23 draft_helper/app.R
Minor bug fix with de-selecting

@@ -67,7 +67,8 @@ positions_df_ex <- C %>%
   bind_rows(RF) %>% 
   bind_rows(SP) %>%
   bind_rows(RP) %>%
-  unique()
+  unique() %>%
+  select(-(positions:RP))
 
 # Define UI for application that draws a histogram
 ui <- fluidPage(
@@ -78,6 +79,7 @@ ui <- fluidPage(
    # Sidebar
    sidebarLayout(
       sidebarPanel(
+        # many thanks to rstudio/shiny-examples/036-custom-input-control/
         chooserInput("chooser", "Available Players", "Drafted Players",
                      main_df$Name, c(), size = 25, multiple = TRUE)
       ),
@@ -95,20 +97,24 @@ ui <- fluidPage(
 # Server
 server <- function(input, output, session) {
   
+  output$selection <- renderPrint(
+    input$chooser
+  )
+  
   table_df <- reactive({
     main_df %>%
       select(-display_position) %>%
-      filter(!Name %in% input$chooser)
+      filter(!Name %in% input$chooser$right)
   })
   
   plot_df <- reactive({
     positions_df_ex %>%
-      filter(!Name %in% input$chooser)
+      filter(!Name %in% input$chooser$right)
   })
    
   output$plot <- renderPlotly({
       plot_df() %>%
-       group_by(round, position) %>%
+       group_by(position, round) %>%
        summarize(low = min(z_sum),
                  mid = median(z_sum) %>% round(2),
                  high = max(z_sum),

### 2019-03-24 draft_helper/app.R
Dark theme and rearranged player name selection list

@@ -1,10 +1,17 @@
 library(shiny)
+library(shinythemes)
 library(plotly)
 library(tidyverse)
 
 source("chooser.R")
 
 main_df <- readRDS("../data/draft_dataset.Rds")
+
+players <- main_df %>%
+  arrange(ADP) %>%
+  select(Name) %>%
+  pull()
+
 positions_df <- main_df %>%
   mutate(C = grepl("C", display_position)) %>%
   mutate(`1B` = grepl("1B", positions)) %>%
@@ -72,6 +79,8 @@ positions_df_ex <- C %>%
 
 # Define UI for application that draws a histogram
 ui <- fluidPage(
+  
+  theme = shinytheme("cyborg"),
    
    # Application title
    titlePanel("Tom's Draft Cheat Sheet"),
@@ -81,7 +90,7 @@ ui <- fluidPage(
       sidebarPanel(
         # many thanks to rstudio/shiny-examples/036-custom-input-control/
         chooserInput("chooser", "Available Players", "Drafted Players",
-                     main_df$Name, c(), size = 25, multiple = TRUE)
+                     players, c(), size = 25, multiple = TRUE)
       ),
       
       # Main Panel

### 2019-03-25 draftResults.Rmd
Draft results review, merge from draft day

---
title: "Draft Results"
author: "Tom Kain"
date: "March 24, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
knitr::opts_knit$set(stop_on_error = 2L)
source("R/yahoo_api.R")
source("R/z_scores.R")
options(tidyverse.quiet=TRUE)
library(knitr)
library(janitor)
library(tidyverse)
```

# Data Set
Put together the data set:
1. Player
2. Position
3. Team
4. Pick
5. isKeeper

```{r}
keepers <- c(
  "Justin Turner",
  "Miles Mikolas",
  "Whit Merrifield",
  "Archie Bradley",
  "Patrick Corbin",
  "Matt Carpenter",
  "Blake Treinen",
  "Ronald Acuna Jr.",
  "Blake Snell",
  "Lorenzo Cain",
  "Trevor Story",
  "Andrew Benintendi",
  "Mike Clevinger"
)

draft_results <- read_tsv("data/draftResults.tsv") %>%  
  clean_names() %>% 
  select(-mlb_team) %>%
  mutate(player = chartr("áéóíñú", "aeoinu", player)) %>% 
  mutate(keeper = (player %in% keepers))

```

# My team
How did I do?

# Team Scores
Compute z_scores based on my pre-draft rankings

# z_Rank vs ADP
See biggest stretches vs biggest value gets - what does that say about our league?

# Consider preseason trades

### 2019-03-25 draftPrep.Rmd
Additional prepping for draft review, plus first trade proposal

@@
          keeper = (Name %in% keepers)) %>% 
-  filter(!keeper) %>%
   arrange(z_sum %>% desc) %>%
   mutate(z_rank = row_number()) %>%
-  select(z_rank, Name, z_sum, round, ADP, positions, display_position) -> draft_df
+  select(z_rank, Name, z_sum, round, ADP, positions, display_position, keeper) -> draft_df
 
-draft_df %>% saveRDS("data/draft_dataset.Rds")
+draft_df %>% saveRDS("data/draft_dataset_with_keepers")
+
+draft_df %>% filter(!keeper) %>% saveRDS("data/draft_dataset.Rds")
 
 draft_df %>%
-  select(-display_position) %>%
+  select(-display_position, -keeper) %>%
   head(25) %>%

### 2019-03-25 draftResults.Rmd
Additional prepping for draft review, plus first trade proposal

@@
 
-draft_results <- read_tsv("data/draftResults.tsv") %>%  
+results <- read_tsv("data/draftResults.tsv") %>%  
   clean_names() %>% 
-  select(-mlb_team) %>%
-  mutate(player = chartr("áéóíñú", "aeoinu", player)) %>% 
-  mutate(keeper = (player %in% keepers))
+  mutate(name = chartr("áéóíñú", "aeoinu", player)) %>% 
+  select(-mlb_team, -player) %>% 
+  mutate(keeper = (name %in% keepers))
+
+ranks <- readRDS("data/draft_dataset_with_keepers") %>% 
+  clean_names() %>% 
+  select(name, adp, z_sum, z_rank)
+
+results <- results %>%
+  left_join(ranks, by = "name")
 
@@
 # Consider preseason trades
+```{r}
+results %>% 
+  filter(grepl("Plouffe|Hebrew",team)) %>% 
+  arrange(team, z_sum %>% desc) %>%
+  View()
+```

### 2019-03-26 draftPrep.Rmd
Draft Results Review

@@
 ```
+
+# Post-Draft Thoughts
+Overall I'm happy with the rankings and interactive cheat sheet - both helped me make decisions during the draft to execute on my strategy that will hopefully return a good team this year.
+That said, there are some things I should revist next year, noted below.
+Over the course of the year, I should capture weekly performance so I can get a sense of variability.
+I should also review the end of year z_scores to see how my draft strategy, z_score computation, and other facets worked.
+
+### Improvements
+
+##### Relative value between pitchers and batters
+Even though my strategy was to value pitchers less than batters, I was about halfway through the draft where the bottom of the barrel batters were clearly overvalued compared to remaining pitchers.
+As a result I probably picked too many batters rather than filtering batters out entirely.
+By end of year, I should have a good sense of what a "replacement" player value is, and reframe the z_scores relative to that.

### 2019-04-06 tradeReview.Rmd
Starting to get team roster from Yahoo Fantasy Sports Api

---
title: "Trade Reviews"
author: "Tom Kain"
date: "April 5, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
```

Various trade scenarios to review during the year.

## Early April
Targeting a 3B, considering Chris's team as a trade partner since he has multiple high value 3B and needs 1B, RP. I'll need to

1. Get the latest ROS projection data, calculate z_scores
2. Get the players for both teams with their eligible positions
3. Get draft results
4. Join roster, projection, and draft result data, rescale z_scores appropriately
5. Identify some equitable trade scenarios keeping as close to a net even z_score exchange

```{r}
source("R/yahoo_api.R")
league_string <- paste0("388.l.",Sys.getenv("LEAGUE_KEY"))
get_team_roster(league_string, 8) %>% 
  clean_names() %>% 
  mutate(owner = 'Tom') -> my_team
get_team_roster(league_string, 3) %>% 
  clean_names() %>% 
  mutate(owner = 'Chris') -> chris_team

my_team %>% 
  bind_rows(chris_team) %>% 
  select(owner, name_full, display_position) -> roster_players

```

### 2019-04-06 R/yahoo_api.R

@@ -43,6 +43,8 @@ get_json <- function(path) {
   
   url <- paste0(base, path, req_json)
   
+  print(url)
+  
   resp <- GET(url = url, config = config, ua)
   if (http_type(resp) != "application/json") {
     stop("API did not return json", call. = F)
@@ -107,10 +109,28 @@ get_players_page <- function(start) {
   count <- players_filtered$count
   
   lapply(players_filtered[1:count], function(x) x[[1]][[1]] %>% 
-           flatten() %>% 
+           rlang::flatten() %>% 
            as.data.frame(stringsAsFactors = F)) %>% 
     bind_rows() %>% 
     as_tibble() %>%
     select(-(14:16))
+}
+
+get_team_roster <- function(league_string, team_id) {
+  # TODO find, add team_name
+  path <- paste0("team/",league_string,".t.",team_id,"/roster/players")
+  
+  get_json(path) %>% 
+    content() -> players_resp
+  
+  players_resp$fantasy_content$team[[2]]$roster$`0`$players -> players_filtered
+  
+  count <- players_filtered$count
+  
+  lapply(players_filtered[1:count], function(x) x[[1]][[1]] %>% 
+           rlang::flatten() %>% 
+           as.data.frame(stringsAsFactors = F)) %>% 
+    bind_rows() %>% 
+    as_tibble() 
 }
 

### 2019-04-06 tradeReview.Rmd
Joined various data sources for first trade review

@@
 ## Early April
-Targeting a 3B, considering Chris's team as a trade partner since he has multiple high value 3B and needs 1B, RP. I'll need to
+Targeting a 3B, considering Chris's team as a trade partner since he has multiple high value 3B and needs 1B, RP. I'll need to...
 
@@
 
+#### Latest ROS Projection data, calculate z_scores
+```{r}
+source("R/z_scores.R")
+proj_batter_raw <- read_csv("data/depthChartProjections_ros_batters_20190405.csv") 
+proj_pitcher_raw <- read_csv("data/depthChartProjections_ros_pitchers_20190405.csv")
+
+proj_batter_raw %>%
+  z_score_count(R) %>%
+  z_score_count(H) %>%
+  z_score_count(HR) %>%
+  z_score_count(RBI) %>%
+  z_score_count(SB) %>%
+  z_score_count(BB) %>%
+  z_score_count(SO, TRUE) %>%
+  z_score_rate(OBP, PA) %>%
+  z_score_rate(OPS, PA) %>%
+  mutate(
+    z_sum = pmap_dbl(
+      select(., starts_with("z_")), 
+      sum
+    ),
+    type = "batter") %>% 
+  select(Name, type, z_sum) -> proj_batter
+
+proj_pitcher_raw %>%
+  z_score_count(SV) %>%
+  z_score_count(SO) %>%
+  z_score_count(HLD) %>%
+  z_score_rate(ERA, IP, TRUE) %>%
+  z_score_rate(WHIP, IP, TRUE) %>%
+  mutate(
+    z_sum = pmap_dbl(
+      select(., starts_with("z_")), 
+      sum
+    ),
+    type = "pitcher") %>% 
+  select(Name, type, z_sum) -> proj_pitcher
+
+```
+
+#### Fantasy team rosters
 ```{r}
@@
   clean_names() %>% 
-  mutate(owner = 'Tom') -> my_team
+  mutate(owner = 'Tom',
+         name_full = chartr("áéóíñú", "aeoinu", name_full)) -> my_team
 get_team_roster(league_string, 3) %>% 
   clean_names() %>% 
-  mutate(owner = 'Chris') -> chris_team
+  mutate(owner = 'Chris',
+         name_full = chartr("áéóíñú", "aeoinu", name_full)) -> chris_team
 
@@
 ```
+
+#### Draft results
+```{r}
+draft_results_raw <- read_tsv("data/draftResults.tsv") %>% 
+  clean_names()
+
+draft_results <- draft_results_raw %>% 
+  select(pick, player)
+```
+
+#### Join data
+```{r}
+projections <- proj_batter %>% 
+  bind_rows(proj_pitcher)
+
+roster_players %>% 
+  left_join(draft_results, by = c("name_full" = "player")) %>% 
+  left_join(projections, by = c("name_full" = "Name")) -> trade_df
+
+trade_df %>% saveRDS("data/tradeReview_20190405.Rds")
+```

### 2019-04-06 tradeReview.Rmd
Missed one data set for accent mark cleanup

@@
 draft_results <- draft_results_raw %>% 
+  mutate(player = chartr("áéóíñú", "aeoinu", player)) %>% 
   select(pick, player)
@@
 trade_df %>% saveRDS("data/tradeReview_20190405.Rds")
+
+trade_df %>% 
+  mutate(z_sum = round(z_sum)) %>% 
+  arrange(z_sum %>% desc, pick) %>% 
+  View()
 ```

### 2019-04-06 tradeReview.Rmd
Added get all team rosters method for yahoo api

@@
 league_string <- paste0("388.l.",Sys.getenv("LEAGUE_KEY"))
-get_team_roster(league_string, 8) %>% 
-  clean_names() %>% 
-  mutate(owner = 'Tom',
-         name_full = chartr("áéóíñú", "aeoinu", name_full)) -> my_team
-get_team_roster(league_string, 3) %>% 
-  clean_names() %>% 
-  mutate(owner = 'Chris',
-         name_full = chartr("áéóíñú", "aeoinu", name_full)) -> chris_team
+get_team_rosters(league_string) -> rosters
 
-my_team %>% 
-  bind_rows(chris_team) %>% 
-  select(owner, name_full, display_position) -> roster_players
+rosters %>% 
+  filter(grepl('Tom|Christopher',manager)) %>% 
+  select(manager, name_full, display_position) -> roster_players
 
@@
   arrange(z_sum %>% desc, pick) %>% 
-  View()
+  write_csv("data/tradeReview_20190405.csv")
 ```

### 2019-04-06 R/yahoo_api.R

@@ -3,6 +3,8 @@ library(httpuv)
 library(jsonlite)
 library(magrittr)
 library(glue)
+library(dplyr)
+library(purrr)
 
 app_keys <- function() {
   key <- Sys.getenv('YAHOO_KEY')
@@ -123,6 +125,10 @@ get_team_roster <- function(league_string, team_id) {
   get_json(path) %>% 
     content() -> players_resp
   
+  players_resp$fantasy_content$team[[1]][[3]]$name -> team_name
+  
+  players_resp$fantasy_content$team[[1]][[20]]$managers[[1]]$manager$nickname -> manager
+  
   players_resp$fantasy_content$team[[2]]$roster$`0`$players -> players_filtered
   
   count <- players_filtered$count
@@ -131,6 +137,16 @@ get_team_roster <- function(league_string, team_id) {
            rlang::flatten() %>% 
            as.data.frame(stringsAsFactors = F)) %>% 
     bind_rows() %>% 
-    as_tibble() 
+    as_tibble() %>% 
+    mutate(team = team_name,
+           manager = manager)
+}
+
+get_team_rosters <- function(league_string, teams=12) {
+  1:teams %>% 
+    map(get_team_roster, league_string = league_string) %>% 
+    bind_rows() %>% 
+    clean_names() %>% 
+    mutate(name_full = chartr("áéóíñú", "aeoinu", name_full))
 }
 

### 2019-04-07 tradeReview.Rmd
Adjusted z_scores, free agent options

@@
 library(janitor)
+library(glue)
+library(plotly)
 ```
@@
 
-rosters %>% 
-  filter(grepl('Tom|Christopher',manager)) %>% 
-  select(manager, name_full, display_position) -> roster_players
-
 ```
@@
 
-roster_players %>% 
+projections$Name[projections$Name == 'Enrique Hernandez'] <- "Kike Hernandez"
+projections$Name[projections$Name == 'Peter Alonso'] <- "Pete Alonso"
+projections$Name[projections$Name == 'Joshua James'] <- "Josh James"
+
+rosters %>% 
   left_join(draft_results, by = c("name_full" = "player")) %>% 
-  left_join(projections, by = c("name_full" = "Name")) -> trade_df
+  full_join(projections, by = c("name_full" = "Name")) %>% 
+  mutate(team = if_else(is.na(team),"Free Agent",team),
+         team = fct_reorder(team, z_sum)) -> rosters_with_projections
 
-trade_df %>% saveRDS("data/tradeReview_20190405.Rds")
+rosters_with_projections %>% 
+  saveRDS("data/rosters_with_projections_20190405.Rds")
+```
 
-trade_df %>% 
+#### Evaluate trade options
+```{r}
+rosters_with_projections %>% 
+  filter(grepl('Tom|Christopher',manager)) %>% 
+  select(manager, name_full, display_position, pick, z_sum) %>%  
   mutate(z_sum = round(z_sum)) %>% 
   arrange(z_sum %>% desc, pick) %>% 
-  write_csv("data/tradeReview_20190405.csv")
+  View()
 ```
+
+## Other research
+
+```{r}
+rosters_with_projections %>% 
+  mutate(z_sum = round(z_sum)) %>% 
+  ggplot(aes(x=team,y=z_sum,color=type)) +
+  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
+  coord_flip() -> p
+
+ggplotly(p)
+
+rosters_with_projections %>% 
+  filter(!type == 'NA', !team == 'Free Agent') %>%
+  ggplot(aes(x=type,y=z_sum)) +
+  geom_boxplot()
+
+rosters_with_projections %>% 
+  filter(!type == 'NA', !team == 'Free Agent') %>%
+  group_by(type) %>% 
+  summarize(adj = median(z_sum)) -> z_sum_adj
+
+rosters_with_adj_projections <- rosters_with_projections %>% 
+  filter(!type == 'NA') %>% 
+  mutate(zar = if_else(type=="batter",
+                       z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
+                       z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"]))
+
+rosters_with_adj_projections %>% 
+  ggplot(aes(x=type,y=zar)) +
+  geom_boxplot()
+
+rosters_with_adj_projections %>% 
+  mutate(zar = round(zar)) %>% 
+  ggplot(aes(x=team,y=zar,color=type)) +
+  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
+  coord_flip() -> z
+
+ggplotly(z)
+
+rosters_with_adj_projections %>% 
+  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
+  arrange(zar %>% desc) %>% 
+  select(name_full, display_position, type, zar) %>% 
+  View()
+```

### 2019-04-08 tradeReview.Rmd
Removed todo, check for league key environment variable

@@
 source("R/yahoo_api.R")
+league_key <- Sys.getenv("LEAGUE_KEY")
+
+if (identical("", league_key)) {
+  stop("LEAGUE_KEY isn't set as R Environment variable")
+} else {
   league_string <- paste0("388.l.",Sys.getenv("LEAGUE_KEY"))
   get_team_rosters(league_string) -> rosters  
-
+}
 ```

### 2019-04-09 rosterReview.Rmd
Laying ground work for roster review

---
title: "Roster Review"
author: "Tom Kain"
date: "April 5, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(glue)
library(plotly)
```

Various general roster reviews throughout the year.

Long and short term views for addressing roster gaps, potential trade targets, free agents, etc.

### 2019-04-09 rosterReview.Rmd
Moving often used code to R scripts, adding new projections

@@
 author: "Tom Kain"
-date: "April 5, 2019"
+date: "April 9, 2019"
 output: html_document
@@
 library(plotly)
+source("R/z_scores.R")
+source("R/yahoo_api.R")
 ```
@@
 Long and short term views for addressing roster gaps, potential trade targets, free agents, etc.
+
+```{r}
+if (!file.exists("data/rosters_with_projections_20190409.Rds")) {
+
+  get_team_rosters() -> rosters
+
+  proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190409.csv","batter") 
+  proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190409.csv", "pitcher")
+
+  draft_results <- read_tsv("data/draftResults.tsv") %>% 
+    clean_names() %>% 
+    mutate(player = chartr("áéóíñú", "aeoinu", player)) %>% 
+    select(pick, player)
+
+  projections <- proj_batter %>% 
+  bind_rows(proj_pitcher)
+
+  projections$Name[projections$Name == 'Enrique Hernandez'] <- "Kike Hernandez"
+  projections$Name[projections$Name == 'Peter Alonso'] <- "Pete Alonso"
+  projections$Name[projections$Name == 'Joshua James'] <- "Josh James"
+
+  rosters %>% 
+    left_join(draft_results, by = c("name_full" = "player")) %>% 
+    full_join(projections, by = c("name_full" = "Name")) %>% 
+    mutate(team = if_else(is.na(team),"Free Agent",team),
+           team = fct_reorder(team, z_sum)) -> rosters_with_projections
+
+  rosters_with_projections %>% 
+    saveRDS("data/rosters_with_projections_20190409.Rds")
+} else {
+  rosters_with_projections <- readRDS("data/rosters_with_projections_20190409.Rds")
+}
+
+```
+
+```{r}
+rosters_with_projections %>% 
+  mutate(z_sum = round(z_sum)) %>% 
+  ggplot(aes(x=team,y=z_sum,color=type)) +
+  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
+  coord_flip() -> p
+
+ggplotly(p)
+
+rosters_with_projections %>% 
+  filter(!type == 'NA', !team == 'Free Agent') %>%
+  ggplot(aes(x=type,y=z_sum)) +
+  geom_boxplot()
+
+rosters_with_projections %>% 
+  filter(!type == 'NA', !team == 'Free Agent') %>%
+  group_by(type) %>% 
+  summarize(adj = median(z_sum)) -> z_sum_adj
+
+rosters_with_adj_projections <- rosters_with_projections %>% 
+  filter(!type == 'NA') %>% 
+  mutate(zar = if_else(type=="batter",
+                       z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
+                       z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"]))
+
+rosters_with_adj_projections %>% 
+  ggplot(aes(x=type,y=zar)) +
+  geom_boxplot()
+
+rosters_with_adj_projections %>% 
+  mutate(zar = round(zar)) %>% 
+  ggplot(aes(x=team,y=zar,color=type)) +
+  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
+  coord_flip() -> z
+
+ggplotly(z)
+
+rosters_with_adj_projections %>% 
+  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
+  arrange(zar %>% desc) %>% 
+  select(name_full, display_position, type, zar) %>% 
+  View()
+```
+
+```{r}
+rosters_with_adj_projections %>% 
+  filter(grepl('2B',display_position)) %>% 
+  ggplot(aes(x=team,y=zar,color=team)) +
+  geom_point(aes(text=name_full)) +
+  coord_flip() -> sb
+
+ggplotly(sb)
+
+rosters_with_adj_projections %>% 
+  filter(grepl('3B',display_position)) %>% 
+  ggplot(aes(x=team,y=zar,color=team)) +
+  geom_point(aes(text=name_full)) +
+  coord_flip() -> tb
+
+ggplotly(tb)
+
+rosters_with_adj_projections %>% 
+  mutate(third_base = grepl('3B',display_position),
+         second_base = grepl('2B',display_position),
+         position_plot_display = case_when(
+           third_base & second_base ~ 'Both',
+           third_base ~ '3B',
+           second_base ~ '2B',
+           TRUE ~ "Other")) %>% 
+  filter(!position_plot_display == 'Other') %>% 
+  mutate(team = fct_relevel(team, "Plouffe There It Is!")) %>% 
+  ggplot(aes(x=team,y=zar,color=position_plot_display)) +
+  geom_point(aes(text=name_full)) +
+  coord_flip() -> both
+
+ggplotly(both)
+
+# free agents?
+
+```

### 2019-04-09 tradeReview.Rmd
Moving often used code to R scripts, adding new projections

--- 2019-04-07 tradeReview.Rmd
@@
 source("R/yahoo_api.R")
-league_string <- paste0("388.l.",Sys.getenv("LEAGUE_KEY"))
-get_team_rosters(league_string) -> rosters
-
+get_team_rosters() -> rosters
 ```
@@
 ```
-
-## Other research
-
-```{r}
-rosters_with_projections %>% 
-  mutate(z_sum = round(z_sum)) %>% 
-  ggplot(aes(x=team,y=z_sum,color=type)) +
-  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
-  coord_flip() -> p
-
-ggplotly(p)
-
-rosters_with_projections %>% 
-  filter(!type == 'NA', !team == 'Free Agent') %>%
-  ggplot(aes(x=type,y=z_sum)) +
-  geom_boxplot()
-
-rosters_with_projections %>% 
-  filter(!type == 'NA', !team == 'Free Agent') %>%
-  group_by(type) %>% 
-  summarize(adj = median(z_sum)) -> z_sum_adj
-
-rosters_with_adj_projections <- rosters_with_projections %>% 
-  filter(!type == 'NA') %>% 
-  mutate(zar = if_else(type=="batter",
-                       z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
-                       z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"]))
-
-rosters_with_adj_projections %>% 
-  ggplot(aes(x=type,y=zar)) +
-  geom_boxplot()
-
-rosters_with_adj_projections %>% 
-  mutate(zar = round(zar)) %>% 
-  ggplot(aes(x=team,y=zar,color=type)) +
-  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
-  coord_flip() -> z
-
-ggplotly(z)
-
-rosters_with_adj_projections %>% 
-  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
-  arrange(zar %>% desc) %>% 
-  select(name_full, display_position, type, zar) %>% 
-  View()
-```

### 2019-04-09 R/yahoo_api.R

@@ -118,8 +118,17 @@ get_players_page <- function(start) {
     select(-(14:16))
 }
 
-get_team_roster <- function(league_string, team_id) {
-  path <- paste0("team/",league_string,".t.",team_id,"/roster/players")
+league_string <- function(game_key=388) {
+  league_key <- Sys.getenv("LEAGUE_KEY")
+  if (identical("", league_key)) {
+    stop("LEAGUE_KEY isn't set as R Environment variable")
+  } else {
+    paste0(game_key,".l.",Sys.getenv("LEAGUE_KEY"))
+  }
+}
+
+get_team_roster <- function(team_id) {
+  path <- paste0("team/",league_string(),".t.",team_id,"/roster/players")
   
   get_json(path) %>% 
     content() -> players_resp
@@ -141,9 +150,9 @@ get_team_roster <- function(league_string, team_id) {
            manager = manager)
 }
 
-get_team_rosters <- function(league_string, teams=12) {
+get_team_rosters <- function(teams=12) {
   1:teams %>% 
-    map(get_team_roster, league_string = league_string) %>% 
+    map(get_team_roster) %>% 
     bind_rows() %>% 
     clean_names() %>% 
     mutate(name_full = chartr("áéóíñú", "aeoinu", name_full))

### 2019-04-09 R/z_scores.R

@@ -1,3 +1,7 @@
+library(magrittr)
+library(dplyr)
+library(readr)
+
 z_score_count <- function(df, stat, invert=FALSE, multiplier=1) {
   stat <- enquo(stat)
   col_nm <- paste0("z_", quo_name(stat))
@@ -43,4 +47,50 @@ z_score_rate <- function(df, stat, quantity, invert=FALSE, multiplier = 1) {
     mutate(s_z = round(s_z, 2)) %>%
     rename(!! col_nm := s_z) %>%
     select(-s_q)
+}
+
+add_z_scores_to_projections <- function(file, mode) {
+  if (!mode %in% c("batter","pitcher")) {
+    stop("mode must be either batter or pitcher")
+  }
+  
+  raw <- read_csv(file)
+  #TODO enforce expected columns by mode
+  
+  if (mode == "batter") {
+    raw %>% 
+      z_score_count(R) %>%
+      z_score_count(H) %>%
+      z_score_count(HR) %>%
+      z_score_count(RBI) %>%
+      z_score_count(SB) %>%
+      z_score_count(BB) %>%
+      z_score_count(SO, TRUE) %>%
+      z_score_rate(OBP, PA) %>%
+      z_score_rate(OPS, PA) %>%
+      mutate(
+        z_sum = pmap_dbl(
+          select(., starts_with("z_")), 
+          sum
+        ),
+        type = "batter") %>% 
+      select(Name, type, z_sum)
+  }
+  
+  else {
+    raw %>% 
+      z_score_count(SV) %>%
+      z_score_count(SO) %>%
+      z_score_count(HLD) %>%
+      z_score_rate(ERA, IP, TRUE) %>%
+      z_score_rate(WHIP, IP, TRUE) %>%
+      mutate(
+        z_sum = pmap_dbl(
+          select(., starts_with("z_")), 
+          sum
+        ),
+        type = "pitcher") %>% 
+      select(Name, type, z_sum)
+  }
+  
 }

### 2019-04-11 rosterReview.Rmd
Some 2B/3B replacement research

@@
 rosters_with_adj_projections %>%
+  filter(type == 'batter') %>% 
   mutate(third_base = grepl('3B',display_position),
          second_base = grepl('2B',display_position),
-         position_plot_display = case_when(
+         position = case_when(
            third_base & second_base ~ 'Both',
@@
            TRUE ~ "Other")) %>% 
-  filter(!position_plot_display == 'Other') %>% 
   mutate(team = fct_relevel(team, "Plouffe There It Is!")) %>% 
-  ggplot(aes(x=team,y=zar,color=position_plot_display)) +
+  ggplot(aes(x=team,y=zar,color=position)) +
   geom_point(aes(text=name_full)) +
@@
 
-# free agents?
+rosters_with_adj_projections %>% 
+  filter(team == 'Free Agent', 
+         grepl('2B|3B',display_position)) %>% 
+  arrange(zar %>% desc) %>% 
+  head(30) %>% 
+  View()
+
+#free agents missing display position - not getting free agents from Yahoo
 
 ```
+
+```{r}
+proj_batter %>% 
+  mutate(zar = if_else(type=="batter",
+                       z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
+                       z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"])) %>% 
+  filter(grepl("Frazier|Voit|Bell|Bradley|Flores",Name)) %>% 
+  arrange(zar %>% desc) %>% 
+  select(Name, Team, zar, G:z_sum) %>% 
+  View()
+```

### 2019-04-11 R/z_scores.R

@@ -73,8 +73,7 @@ add_z_scores_to_projections <- function(file, mode) {
           select(., starts_with("z_")), 
           sum
         ),
-        type = "batter") %>% 
-      select(Name, type, z_sum)
+        type = "batter")
   }
   
   else {
@@ -89,8 +88,7 @@ add_z_scores_to_projections <- function(file, mode) {
           select(., starts_with("z_")), 
           sum
         ),
-        type = "pitcher") %>% 
-      select(Name, type, z_sum)
+        type = "pitcher") 
   }
   
 }

### 2019-04-12 rosterReview_01.Rmd
Cross-platform solution for cleaning accents, import fixes

--- 2019-04-11 rosterReview.Rmd
@@
 library(plotly)
+library(stringi)
 source("R/z_scores.R")
@@
     clean_names() %>% 
-    mutate(player = chartr("áéóíñú", "aeoinu", player)) %>% 
+    mutate(player = stri_trans_general(player, "latin-ascii")) %>% 
     select(pick, player)
@@
 
-#free agents missing display position - not getting free agents from Yahoo
-
 ```
@@
 ```
+
+```{r}
+players <- get_players() %>% 
+  clean_names() %>% 
+  mutate(name_full = stri_trans_general(name_full, "latin-ascii"))
+
+View(players)
+```

### 2019-04-12 tradeReview.Rmd
Cross-platform solution for cleaning accents, import fixes

@@
 library(plotly)
+library(stringi)
 ```
@@
 
-#### Fantasy team rosters
-```{r}
-source("R/yahoo_api.R")
-get_team_rosters() -> rosters
-```
-
 #### Draft results
@@
 draft_results <- draft_results_raw %>% 
-  mutate(player = chartr("áéóíñú", "aeoinu", player)) %>% 
+  mutate(player = stri_trans_general(player, "latin-ascii")) %>% 
   select(pick, player)
@@
 
-#### Join data
+#### Join with roster data
 ```{r}
+if (!file.exists("data/rosters_with_projections_20190405.Rds")) {
+  source("R/yahoo_api.R")
+  get_team_rosters() -> rosters
+
   projections <- proj_batter %>% 
@@
     saveRDS("data/rosters_with_projections_20190405.Rds")
+} else {
+  rosters_with_projections <- readRDS("data/rosters_with_projections_20190405.Rds")
+}
+
 ```

### 2019-04-12 R/yahoo_api.R

@@ -5,6 +5,8 @@ library(magrittr)
 library(glue)
 library(dplyr)
 library(purrr)
+library(janitor)
+library(stringi)
 
 app_keys <- function() {
   key <- Sys.getenv('YAHOO_KEY')
@@ -114,8 +116,7 @@ get_players_page <- function(start) {
            rlang::flatten() %>% 
            as.data.frame(stringsAsFactors = F)) %>% 
     bind_rows() %>% 
-    as_tibble() %>%
-    select(-(14:16))
+    as_tibble()
 }
 
 league_string <- function(game_key=388) {
@@ -155,6 +156,6 @@ get_team_rosters <- function(teams=12) {
     map(get_team_roster) %>% 
     bind_rows() %>% 
     clean_names() %>% 
-    mutate(name_full = chartr("бйунсъ", "aeoinu", name_full))
+    mutate(name_full = stri_trans_general(name_full, "latin-ascii"))
 }
 

### 2019-04-22 rosterReview_02.Rmd
Reviewing available free agents

--- 2019-04-12 rosterReview_01.Rmd
@@
 ---
-title: "Roster Review"
+title: "Roster Review 2"
 author: "Tom Kain"
-date: "April 9, 2019"
+date: "April 22, 2019"
 output: html_document
@@
 
-Various general roster reviews throughout the year.
-
-Long and short term views for addressing roster gaps, potential trade targets, free agents, etc.
-
 ```{r}
-if (!file.exists("data/rosters_with_projections_20190409.Rds")) {
-
-  get_team_rosters() -> rosters
-
-  proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190409.csv","batter") 
-  proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190409.csv", "pitcher")
-
 draft_results <- read_tsv("data/draftResults.tsv") %>% 
@@
     select(pick, player)
+
+if (!file.exists("data/rosters_with_projections_20190422.Rds")) {
+
+  if (!file.exists("data/rosters_20190422.Rds")) {
+    get_team_rosters() -> rosters
+    rosters %>% 
+      saveRDS("data/rosters_20190422.Rds")
+  } else {
+    rosters <- readRDS("data/rosters_20190422.Rds")
+  }
+
+  if (!file.exists("data/yahoo_players_20190422.Rds")) {
+    yahoo_players <- get_players(2500)
+    yahoo_players %>% 
+      saveRDS("data/yahoo_players_20190422.Rds")
+  } else {
+    yahoo_players <- readRDS("data/yahoo_players_20190422.Rds")
+  }
+
+  all_players <- rosters %>% 
+    select(player_id, team, manager) %>% 
+    full_join(yahoo_players) %>% 
+    clean_names() %>% 
+    mutate(name_full = stri_trans_general(name_full, "latin-ascii"))
+
+  proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190422.csv","batter") 
+  proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190422.csv", "pitcher")
 
@@
 
-  rosters %>% 
-    left_join(draft_results, by = c("name_full" = "player")) %>% 
+  all_players %>% 
+    #left_join(draft_results, by = c("name_full" = "player")) %>% 
     full_join(projections, by = c("name_full" = "Name")) %>% 
@@
   rosters_with_projections %>% 
-    saveRDS("data/rosters_with_projections_20190409.Rds")
+    saveRDS("data/rosters_with_projections_20190422.Rds")
+
 } else {
@@
 ```{r}
-rosters_with_projections %>% 
-  mutate(z_sum = round(z_sum)) %>% 
-  ggplot(aes(x=team,y=z_sum,color=type)) +
-  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
-  coord_flip() -> p
-
-ggplotly(p)
-
-rosters_with_projections %>% 
-  filter(!type == 'NA', !team == 'Free Agent') %>%
-  ggplot(aes(x=type,y=z_sum)) +
-  geom_boxplot()
-
 rosters_with_projections %>% 
@@
                        z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"]))
+```
 
-rosters_with_adj_projections %>% 
-  ggplot(aes(x=type,y=zar)) +
-  geom_boxplot()
-
+```{r}
 rosters_with_adj_projections %>% 
   mutate(zar = round(zar)) %>% 
+  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +
   geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
-  coord_flip() -> z
+  coord_flip() -> pa
 
-ggplotly(z)
+ggplotly(pa)
 
@@
 ```
+---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
+
+## R Markdown
+
+This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+
+When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
+You can embed an R code chunk like this:
+
+```{r cars}
+summary(cars)
+```
+
+## Including Plots
+
+You can also embed plots, for example:
+
+```{r pressure, echo=FALSE}
+plot(pressure)
+```
+
+Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-04-22 R/yahoo_api.R
Reviewing available free agents

@@ -102,7 +102,7 @@ get_players <- function(rownum=25, start=0) {
   results
 }
 
-get_players_page <- function(start) {
+get_players_page <- function(start=0) {
   path <- paste0("users;use_login=1/games;game_keys=mlb/players;start=",start,";count=25")
   
   get_json(path) %>% 
@@ -116,7 +116,8 @@ get_players_page <- function(start) {
            rlang::flatten() %>% 
            as.data.frame(stringsAsFactors = F)) %>% 
     bind_rows() %>% 
-    as_tibble()
+    as_tibble() %>% 
+    mutate(name.full = stri_trans_general(name.full, "latin-ascii"))
 }
 
 league_string <- function(game_key=388) {

### 2019-04-24 rosterReview_02.Rmd
Some trade scenarios and fixes to pulled data

@@
 rosters_with_adj_projections %>% 
-  filter(grepl('2B',display_position)) %>% 
-  ggplot(aes(x=team,y=zar,color=team)) +
-  geom_point(aes(text=name_full)) +
-  coord_flip() -> sb
-
-ggplotly(sb)
+  filter(grepl("Plouffe|Painting",team)) %>% 
+  select(team, manager, name_full, display_position, zar) %>% 
+  arrange(zar %>% desc) %>% 
+  View()
+  # mutate(zar = janitor::round_half_up(zar)) %>% 
+  # write_csv("data/tradeReview_20190423.csv")
 
 rosters_with_adj_projections %>% 
-  filter(grepl('3B',display_position)) %>% 
-  ggplot(aes(x=team,y=zar,color=team)) +
-  geom_point(aes(text=name_full)) +
-  coord_flip() -> tb
+  filter(grepl("Plouffe|Painting",team)) %>% 
+  ggplot(aes(x=team,y=zar,color=type)) +
+  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
+  coord_flip() -> tv
 
-ggplotly(tb)
+ggplotly(tv)
 
 rosters_with_adj_projections %>% 
-  filter(type == 'batter') %>% 
-  mutate(third_base = grepl('3B',display_position),
-         second_base = grepl('2B',display_position),
-         position = case_when(
-           third_base & second_base ~ 'Both',
-           third_base ~ '3B',
-           second_base ~ '2B',
-           TRUE ~ "Other")) %>% 
-  mutate(team = fct_relevel(team, "Plouffe There It Is!")) %>% 
-  ggplot(aes(x=team,y=zar,color=position)) +
-  geom_point(aes(text=name_full)) +
-  coord_flip() -> both
-
-ggplotly(both)
+  filter(grepl("Plouffe|Dorn",team)) %>% 
+  select(team, manager, name_full, display_position, zar) %>% 
+  filter(grepl("Devers|Swarzak|deGrom|Rendon|Alex Colom|David Price",name_full)) %>% 
+  group_by(team) %>% 
+  summarize(zar = sum(zar))
 
 rosters_with_adj_projections %>% 
-  filter(team == 'Free Agent', 
-         grepl('2B|3B',display_position)) %>% 
-  arrange(zar %>% desc) %>% 
-  head(30) %>% 
-  View()
-
+  filter(grepl("Plouffe|Painting",team)) %>% 
+  select(team, manager, name_full, display_position, zar) %>% 
+  filter(grepl("Santana|Robertson|deGrom|Devers",name_full)) %>% 
+  group_by(team) %>% 
+  summarize(zar = sum(zar))
 ```
-
-```{r}
-proj_batter %>% 
-  mutate(zar = if_else(type=="batter",
-                       z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
-                       z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"])) %>% 
-  filter(grepl("Frazier|Voit|Bell|Bradley|Flores",Name)) %>% 
-  arrange(zar %>% desc) %>% 
-  select(Name, Team, zar, G:z_sum) %>% 
-  View()
-```
-
-```{r}
-players <- get_players() %>% 
-  clean_names() %>% 
-  mutate(name_full = stri_trans_general(name_full, "latin-ascii"))
-
-View(players)
-```
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
-```
-
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-04-25 rosterReview_generic.Rmd
Starting to abstracting roster review functions

---
title: "Roster Review (Generic)"
author: "Tom Kain"
date: "April 25, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(glue)
library(plotly)
library(stringi)
source("R/z_scores.R")
source("R/yahoo_api.R")
```

```{r}
filename <- function(name) {
  paste0("data/",name,"_",gsub("-","",Sys.Date()),".Rds")
}

draft_results <- read_tsv("data/draftResults.tsv") %>% 
    clean_names() %>% 
    mutate(player = stri_trans_general(player, "latin-ascii")) %>% 
    select(pick, player)

get_team_rosters() -> rosters
rosters %>% 
  saveRDS(filename("rosters"))

yahoo_players <- get_players(2500)
yahoo_players %>% 
  saveRDS(filename("yahoo_players"))

all_players <- rosters %>% 
  select(player_id, team, manager) %>% 
  full_join(yahoo_players) %>% 
  clean_names() %>% 
  mutate(name_full = stri_trans_general(name_full, "latin-ascii"))

#TODO abstract projection filename

proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190422.csv","batter") 
proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190422.csv", "pitcher")

projections <- proj_batter %>% 
  bind_rows(proj_pitcher)

#TODO save these to some file
projections$Name[projections$Name == 'Enrique Hernandez'] <- "Kike Hernandez"
projections$Name[projections$Name == 'Peter Alonso'] <- "Pete Alonso"
projections$Name[projections$Name == 'Joshua James'] <- "Josh James"

#TODO test, include draft team
all_players %>% 
  full_join(draft_results, by = c("name_full" = "player")) %>% 
  full_join(projections, by = c("name_full" = "Name")) %>% 
  mutate(team = if_else(is.na(team),"Free Agent",team),
         team = fct_reorder(team, z_sum)) -> rosters_with_projections

rosters_with_projections %>% 
  saveRDS(filename("rosters_with_projections"))

```

```{r}
#TODO move to script (sets z_score above replacement, based on median z_score of rostered players, grouped by type [batter/pitcher])
rosters_with_projections %>% 
  filter(!type == 'NA', !team == 'Free Agent') %>%
  group_by(type) %>% 
  summarize(adj = median(z_sum)) -> z_sum_adj

rosters_with_adj_projections <- rosters_with_projections %>% 
  filter(!type == 'NA') %>% 
  mutate(zar = if_else(type=="batter",
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"]))
```

```{r}
#TODO abstract some of these views
rosters_with_adj_projections %>% 
  mutate(zar = round(zar)) %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
  coord_flip() -> pa

ggplotly(pa)

rosters_with_adj_projections %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
  arrange(zar %>% desc) %>% 
  select(name_full, display_position, type, zar) %>% 
  View()
```

```{r}
rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Bat Lives",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Bat Lives",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Bryant|deGrom|Bumgarner|Devers",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Painting",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

ggplotly(tv)

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Poofer",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Bregman|Walker|deGrom|Lindor",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Painting",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Santana|Robertson|deGrom|Devers",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))
```
```{r}
rosters_with_adj_projections %>% 
  filter(grepl("Free Agent|Plouffe",team),
         grepl("RP",display_position)) %>% 
  ggplot(aes(x=team,y=zar)) +
  geom_jitter(aes(text=name_full), width = .2) +
  coord_flip() -> tb

ggplotly(tb)
```

### 2019-04-26 rosterReview_generic.Rmd
A touch of refactoring/organizing

@@
 ```{r}
+# check if file exists, maybe move all in this chunk to a script
 filename <- function(name) {
@@
   clean_names() %>% 
-    mutate(player = stri_trans_general(player, "latin-ascii")) %>% 
-    select(pick, player)
+  mutate(player = stri_trans_general(player, "latin-ascii"),
+           round = ceiling(pick/12)) %>%  
+  select(player, pick, round) %>% 
+  rename(draft_pick = pick,
+         draft_round = round)
 
@@
 ```{r}
+# TODO find way to wrap these three views into one
 rosters_with_adj_projections %>% 
-  filter(grepl("Plouffe|Bat Lives",team)) %>% 
+  filter(grepl("Plouffe|Poofer",team)) %>% 
   select(team, manager, name_full, display_position, zar) %>% 
@@
 rosters_with_adj_projections %>% 
-  filter(grepl("Plouffe|Bat Lives",team)) %>% 
-  select(team, manager, name_full, display_position, zar) %>% 
-  filter(grepl("Bryant|deGrom|Bumgarner|Devers",name_full)) %>% 
-  group_by(team) %>% 
-  summarize(zar = sum(zar))
-
-rosters_with_adj_projections %>% 
-  filter(grepl("Plouffe|Painting",team)) %>% 
+  filter(grepl("Plouffe|Poofers",team)) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +
@@
   select(team, manager, name_full, display_position, zar) %>% 
-  filter(grepl("Bregman|Walker|deGrom|Lindor",name_full)) %>% 
-  group_by(team) %>% 
-  summarize(zar = sum(zar))
-
-rosters_with_adj_projections %>% 
-  filter(grepl("Plouffe|Painting",team)) %>% 
-  select(team, manager, name_full, display_position, zar) %>% 
-  filter(grepl("Santana|Robertson|deGrom|Devers",name_full)) %>% 
+  filter(grepl("Bregman|deGrom|Lindor",name_full)) %>% 
   group_by(team) %>% 
@@
 ```
+
 ```{r}
 rosters_with_adj_projections %>% 
-  filter(grepl("Free Agent|Plouffe",team),
-         grepl("RP",display_position)) %>% 
-  ggplot(aes(x=team,y=zar)) +
+  filter(!grepl("Free Agent",team),
+         grepl("SP|3B",display_position)) %>% 
+  ggplot(aes(x=team,y=zar,color=type)) +
   geom_jitter(aes(text=name_full), width = .2) +
@@
 ```
+
+```{r}
+#TODO measuring projected value of draft picks, move to separate research
+rosters_with_adj_projections %>% 
+  filter(!is.na(draft_pick)) %>% 
+  group_by(draft_round) %>% 
+  summarize(zar_median = median(zar) %>% janitor::round_half_up(),
+            zar_mean = mean(zar) %>% janitor::round_half_up()) %>%
+  ggplot(aes(x=draft_round,y=zar_mean)) +
+  geom_col() +
+  geom_line(aes(y=zar))
+
+rosters_with_adj_projections %>% 
+  filter(!is.na(draft_pick)) %>% 
+  group_by(draft_round) %>% 
+  arrange(draft_round) %>% 
+  ggplot(aes(x=draft_round,y=zar,group=draft_round)) +
+  geom_boxplot()
+```

### 2019-05-04 rosterReview_generic.Rmd
Minor notes and visual options

@@
 
-proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190422.csv","batter") 
-proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190422.csv", "pitcher")
+proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190429.csv","batter") 
+proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190429.csv", "pitcher")
 
@@
 projections$Name[projections$Name == 'Joshua James'] <- "Josh James"
+projections$Name[projections$Name == 'Shin-Soo Choo'] <- "Shin-soo Choo"
 
@@
 #TODO abstract some of these views
+#FIXME some join issues here
 rosters_with_adj_projections %>% 
@@
 rosters_with_adj_projections %>% 
-  filter(grepl("Plouffe|Poofer",team)) %>% 
+  filter(grepl("Plouffe|Hebrew",team)) %>% 
   select(team, manager, name_full, display_position, zar) %>% 
@@
 rosters_with_adj_projections %>% 
-  filter(grepl("Plouffe|Poofers",team)) %>% 
+  filter(grepl("Plouffe|Hebrew",team)) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +
@@
 rosters_with_adj_projections %>% 
-  filter(grepl("Plouffe|Poofer",team)) %>% 
+  filter(grepl("Plouffe|Hebrew",team)) %>% 
   select(team, manager, name_full, display_position, zar) %>% 
-  filter(grepl("Bregman|deGrom|Lindor",name_full)) %>% 
+  filter(grepl("deGrom|Rizzo",name_full)) %>% 
   group_by(team) %>% 
@@
   filter(!grepl("Free Agent",team),
-         grepl("SP|3B",display_position)) %>% 
+         # grepl("SP|3B",display_position)
+         ) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +
-  geom_jitter(aes(text=name_full), width = .2) +
+  geom_boxplot() +
+  # geom_jitter(aes(text=name_full), width = .2) +
   coord_flip() -> tb
@@
   geom_col() +
-  geom_line(aes(y=zar))
+  geom_line(aes(y=zar_median))
 

### 2019-05-06 rosterReview_generic.Rmd
More projections, updated data

@@
 
-proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190429.csv","batter") 
-proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190429.csv", "pitcher")
+proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190506.csv","batter") 
+proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190506.csv", "pitcher")
 
@@
 rosters_with_adj_projections %>% 
-  filter(!grepl("Free Agent",team),
+  #filter(!grepl("Free Agent",team),
          # grepl("SP|3B",display_position)
-         ) %>% 
+   #      ) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +

### 2019-05-15 rosterReview_generic.Rmd
Added position aggregation

--- 2019-05-04 rosterReview_generic.Rmd
@@
 
-proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190429.csv","batter") 
-proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190429.csv", "pitcher")
+proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190513.csv","batter") 
+proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190513.csv", "pitcher")
 
@@
                        z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"]))
+
+position_columns <- rosters_with_adj_projections %>%
+    select(starts_with("eligible_positions")) %>%
+    colnames()
+
+rosters_with_adj_projections %>%
+  mutate(positions = paste(!!! syms(position_columns), sep = "," )) %>%
+  mutate(positions = gsub('NA', '', positions)) %>%
+  mutate(positions = gsub("^,*|(?<=,),|,*$", "", positions, perl=T)) %>%
+  select(-(starts_with("eligible_positions"))) -> rosters_with_adj_projections
 ```
@@
 rosters_with_adj_projections %>% 
-  filter(grepl("Plouffe|Hebrew",team)) %>% 
+  filter(grepl("Plouffe|Utleys",team)) %>% 
   select(team, manager, name_full, display_position, zar) %>% 
@@
 rosters_with_adj_projections %>% 
-  filter(grepl("Plouffe|Hebrew",team)) %>% 
+  filter(grepl("Plouffe|Utleys",team)) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +
@@
 rosters_with_adj_projections %>% 
-  filter(grepl("Plouffe|Hebrew",team)) %>% 
+  filter(grepl("Plouffe|theriverbrew",team)) %>% 
   select(team, manager, name_full, display_position, zar) %>% 
-  filter(grepl("deGrom|Rizzo",name_full)) %>% 
+  filter(grepl("deGrom|Lucchesi",name_full)) %>% 
   group_by(team) %>% 
@@
   filter(!grepl("Free Agent",team),
-         # grepl("SP|3B",display_position)
+  grepl("CF",positions)
        ) %>%
   ggplot(aes(x=team,y=zar,color=type)) +
-  geom_boxplot() +
-  # geom_jitter(aes(text=name_full), width = .2) +
+  #geom_boxplot() +
+  geom_jitter(aes(text=name_full), width = .2) +
   coord_flip() -> tb
@@
   geom_col() +
-  geom_line(aes(y=zar_median))
+  geom_line(aes(y=zar_median)) -> draft_plot
+
+ggplotly(draft_plot)
 

### 2019-05-29 R/helper.R
Laying some ground work and testing of comparing performance to projection data

@@ -5,10 +5,10 @@ source("R/z_scores.R")
 source("R/yahoo_api.R")
 
 #TODO review/resolve all player name joins (orphaned results, incorrect assignments)
-#TODO keep player ids from each source
 #TODO ingest performance data from fangraphs
+#TODO add z_score_adj (zar), position column compact options for load player data
 
-filename <- function(name) {
+filename_today <- function(name) {
   paste0("data/", name, "_", gsub("-", "", Sys.Date()), ".Rds")
 }
 
@@ -24,7 +24,7 @@ load_draft_results <- function() {
 }
 
 load_rosters <- function(force = FALSE) {
-  file <- filename("rosters")
+  file <- filename_today("rosters")
   
   if (force || !file %>% file.exists()) {
     get_team_rosters() %>%
@@ -34,7 +34,7 @@ load_rosters <- function(force = FALSE) {
 }
 
 load_players <- function(force = FALSE) {
-  file <- filename("yahoo_players")
+  file <- filename_today("yahoo_players")
   
   if (force || !file %>% file.exists()) {
     get_players(2500) %>%
@@ -74,13 +74,18 @@ load_projections <-
       }
     }
     
-    proj_batter <- add_z_scores_to_projections(batter_destination, "batter")
-    proj_pitcher <- add_z_scores_to_projections(pitcher_destination, "pitcher")
+    compile_z_scores(batter_destination, pitcher_destination)
     
-    bind_rows(proj_batter, proj_pitcher) %>%
-      clean_names() %>%
-      adjust_names_for_join()
   }
+
+compile_z_scores <- function(batter_file, pitcher_file) {
+  proj_batter <- add_z_scores(batter_file, "batter")
+  proj_pitcher <- add_z_scores(pitcher_file, "pitcher")
+  
+  bind_rows(proj_batter, proj_pitcher) %>%
+    clean_names() %>%
+    adjust_names_for_join()
+}
 
 adjust_names_for_join <- function(df) {
   names_key_df <- read_csv("data/nameJoins.csv") %>%
@@ -98,7 +103,7 @@ load_players_with_projections <-
   function(force = FALSE,
            batter_file = NULL,
            pitcher_file = NULL) {
-    file <- filename("rosters_with_projections")
+    file <- filename_today("rosters_with_projections")
     
     if (force || !file %>% file.exists()) {
       load_rosters(force) %>%

### 2019-05-29 R/z_scores.R

@@ -50,7 +50,11 @@ z_score_rate <- function(df, stat, quantity, invert=FALSE, multiplier = 1) {
 }
 
 add_z_scores_to_projections <- function(file, mode) {
-  if (!mode %in% c("batter","pitcher")) {
+  add_z_scores(file, mode)
+}
+
+add_z_scores <- function(file, mode) {
+  if (is.null(mode) | !mode %in% c("batter","pitcher")) {
     stop("mode must be either batter or pitcher")
   }
   

### 2019-05-31 R/helper.R
Some fixes for helper script

@@ -74,7 +74,8 @@ load_projections <-
       }
     }
     
-    compile_z_scores(batter_destination, pitcher_destination)
+    compile_z_scores(batter_destination, pitcher_destination) %>% 
+      rename(mlb_team = team)
     
   }
 
@@ -113,7 +114,7 @@ load_players_with_projections <-
         mutate(name_full = stri_trans_general(name_full, "latin-ascii")) %>%
         full_join(load_draft_results(), by = c("name_full" = "player")) %>%
         full_join(load_projections(force, batter_file, pitcher_file),
-                  by = c("name_full" = "Name")) %>%
+                  by = c("name_full" = "name")) %>%
         mutate(team = if_else(is.na(team), "Free Agent", team),
                team = fct_reorder(team, z_sum)) %>%
         saveRDS(file)

### 2019-05-31 rosterReview_generic.Rmd
Cleanup, join fix by position type, remove duplicated code from generic roster review, a few more TODOs

--- 2019-05-04 rosterReview_generic.Rmd
@@
 library(tidyverse)
-library(janitor)
 library(glue)
 library(plotly)
-library(stringi)
-source("R/z_scores.R")
-source("R/yahoo_api.R")
+
+source("R/helper.R")
 ```
@@
 ```{r}
-# check if file exists, maybe move all in this chunk to a script
-filename <- function(name) {
-  paste0("data/",name,"_",gsub("-","",Sys.Date()),".Rds")
-}
+force <- FALSE
+batter_file <- NULL
+pitcher_file <- NULL
 
-draft_results <- read_tsv("data/draftResults.tsv") %>% 
-  clean_names() %>% 
-  mutate(player = stri_trans_general(player, "latin-ascii"),
-           round = ceiling(pick/12)) %>%  
-  select(player, pick, round) %>% 
-  rename(draft_pick = pick,
-         draft_round = round)
-
-get_team_rosters() -> rosters
-rosters %>% 
-  saveRDS(filename("rosters"))
-
-yahoo_players <- get_players(2500)
-yahoo_players %>% 
-  saveRDS(filename("yahoo_players"))
-
-all_players <- rosters %>% 
-  select(player_id, team, manager) %>% 
-  full_join(yahoo_players) %>% 
-  clean_names() %>% 
-  mutate(name_full = stri_trans_general(name_full, "latin-ascii"))
-
-#TODO abstract projection filename
-
-proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190429.csv","batter") 
-proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190429.csv", "pitcher")
-
-projections <- proj_batter %>% 
-  bind_rows(proj_pitcher)
-
-#TODO save these to some file
-projections$Name[projections$Name == 'Enrique Hernandez'] <- "Kike Hernandez"
-projections$Name[projections$Name == 'Peter Alonso'] <- "Pete Alonso"
-projections$Name[projections$Name == 'Joshua James'] <- "Josh James"
-projections$Name[projections$Name == 'Shin-Soo Choo'] <- "Shin-soo Choo"
-
-#TODO test, include draft team
-all_players %>% 
-  full_join(draft_results, by = c("name_full" = "player")) %>% 
-  full_join(projections, by = c("name_full" = "Name")) %>% 
-  mutate(team = if_else(is.na(team),"Free Agent",team),
-         team = fct_reorder(team, z_sum)) -> rosters_with_projections
-
-rosters_with_projections %>% 
-  saveRDS(filename("rosters_with_projections"))
-
+rosters <- load_players_with_projections(force, batter_file, pitcher_file)
 ```
@@
 ```{r}
-#TODO move to script (sets z_score above replacement, based on median z_score of rostered players, grouped by type [batter/pitcher])
-rosters_with_projections %>% 
+#TODO move to helper
+rosters %>% 
   filter(!type == 'NA', !team == 'Free Agent') %>%
@@
 
-rosters_with_adj_projections <- rosters_with_projections %>% 
+rosters <- rosters %>% 
   filter(!type == 'NA') %>% 
@@
                        z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"]))
+
+position_columns <- rosters %>%
+    select(starts_with("eligible_positions")) %>%
+    colnames()
+
+rosters %>%
+  mutate(positions = paste(!!! syms(position_columns), sep = "," )) %>%
+  mutate(positions = gsub('NA', '', positions)) %>%
+  mutate(positions = gsub("^,*|(?<=,),|,*$", "", positions, perl=T)) %>%
+  select(-(starts_with("eligible_positions"))) -> rosters
 ```
@@
 #FIXME some join issues here
-rosters_with_adj_projections %>% 
+rosters %>% 
   mutate(zar = round(zar)) %>% 
@@
 
-rosters_with_adj_projections %>% 
+rosters %>% 
   filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
@@
 # TODO find way to wrap these three views into one
-rosters_with_adj_projections %>% 
-  filter(grepl("Plouffe|Hebrew",team)) %>% 
+rosters %>% 
+  filter(grepl("Plouffe|Utleys",team)) %>% 
   select(team, manager, name_full, display_position, zar) %>% 
@@
 
-rosters_with_adj_projections %>% 
-  filter(grepl("Plouffe|Hebrew",team)) %>% 
+rosters %>% 
+  filter(grepl("Plouffe|Utleys",team)) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +
@@
 
-rosters_with_adj_projections %>% 
-  filter(grepl("Plouffe|Hebrew",team)) %>% 
+rosters %>% 
+  filter(grepl("Plouffe|theriverbrew",team)) %>% 
   select(team, manager, name_full, display_position, zar) %>% 
-  filter(grepl("deGrom|Rizzo",name_full)) %>% 
+  filter(grepl("deGrom|Lucchesi",name_full)) %>% 
   group_by(team) %>% 
@@
 ```{r}
-rosters_with_adj_projections %>% 
+rosters %>% 
   filter(!grepl("Free Agent",team),
-         # grepl("SP|3B",display_position)
+  grepl("CF",positions)
        ) %>%
   ggplot(aes(x=team,y=zar,color=type)) +
-  geom_boxplot() +
-  # geom_jitter(aes(text=name_full), width = .2) +
+  #geom_boxplot() +
+  geom_jitter(aes(text=name_full), width = .2) +
   coord_flip() -> tb
@@
 #TODO measuring projected value of draft picks, move to separate research
-rosters_with_adj_projections %>% 
+rosters %>% 
   filter(!is.na(draft_pick)) %>%
@@
   geom_col() +
-  geom_line(aes(y=zar_median))
+  geom_line(aes(y=zar_median)) -> draft_plot
 
-rosters_with_adj_projections %>% 
+ggplotly(draft_plot)
+
+rosters %>% 
   filter(!is.na(draft_pick)) %>% 

### 2019-05-31 R/helper.R

@@ -6,7 +6,9 @@ source("R/yahoo_api.R")
 
 #TODO review/resolve all player name joins (orphaned results, incorrect assignments)
 #TODO ingest performance data from fangraphs
-#TODO add z_score_adj (zar), position column compact options for load player data
+#TODO add position column compact options for load player data
+#TODO add z_adj -> zar (sets z_score above replacement, based on median z_score of rostered players, grouped by type [batter/pitcher])
+#TODO create a "get latest compiled roster" method
 
 filename_today <- function(name) {
   paste0("data/", name, "_", gsub("-", "", Sys.Date()), ".Rds")
@@ -38,6 +40,13 @@ load_players <- function(force = FALSE) {
   
   if (force || !file %>% file.exists()) {
     get_players(2500) %>%
+      clean_names() %>%
+      mutate(type = case_when(
+        position_type == "B" ~ "batter",
+        position_type == "P" ~ "pitcher",
+        TRUE ~ "other"
+      )) %>% 
+      select(-position_type) %>% 
       saveRDS(file)
   }
   readRDS(file)
@@ -102,19 +111,18 @@ adjust_names_for_join <- function(df) {
 
 load_players_with_projections <-
   function(force = FALSE,
+           force_all = FALSE,
            batter_file = NULL,
            pitcher_file = NULL) {
     file <- filename_today("rosters_with_projections")
     
-    if (force || !file %>% file.exists()) {
-      load_rosters(force) %>%
+    if (force || force_all || !file %>% file.exists()) {
+      load_rosters(force_all) %>%
         select(player_id, team, manager) %>%
-        full_join(load_players(force)) %>%
-        clean_names() %>%
-        mutate(name_full = stri_trans_general(name_full, "latin-ascii")) %>%
+        full_join(load_players(force_all)) %>%
         full_join(load_draft_results(), by = c("name_full" = "player")) %>%
-        full_join(load_projections(force, batter_file, pitcher_file),
-                  by = c("name_full" = "name")) %>%
+        left_join(load_projections(force_all, batter_file, pitcher_file),
+                  by = c("name_full" = "name", "type" = "type")) %>%
         mutate(team = if_else(is.na(team), "Free Agent", team),
                team = fct_reorder(team, z_sum)) %>%
         saveRDS(file)

### 2019-05-31 rosterReview_generic.Rmd
Overwrite and inner join fix

@@
 force <- FALSE
+force_all <- FALSE
 batter_file <- NULL
@@
 
-rosters <- load_players_with_projections(force, batter_file, pitcher_file)
+rosters <- load_players_with_projections(force, force_all, batter_file, pitcher_file)
 ```
@@
 rosters %>% 
-  filter(!type == 'NA', !team == 'Free Agent') %>%
+  filter(type != 'NA', team != 'Free Agent') %>%
   group_by(type) %>% 

### 2019-05-31 R/helper.R

@@ -63,23 +63,23 @@ load_projections <-
     pitcher_destination <-
       paste0(file_start, "pitchers_", date_string, ".csv")
     
-    if (force || !batter_destination %>% file.exists()) {
-      if (batter_file %>% is_null() || !batter_file %>% file.exists()) {
+    if (force | !batter_destination %>% file.exists()) {
+      if (batter_file %>% is_null() | !batter_file %>% file.exists()) {
         stop(
           "Could not find today's batter projections in expected folder, or replacement not specified"
         )
       } else {
-        file.copy(batter_file, batter_destination)
+        file.copy(batter_file, batter_destination, overwrite=TRUE)
       }
     }
     
-    if (force || !pitcher_destination %>% file.exists()) {
-      if (pitcher_file %>% is_null() || !pitcher_file %>% file.exists()) {
+    if (force | !pitcher_destination %>% file.exists()) {
+      if (pitcher_file %>% is_null() | !pitcher_file %>% file.exists()) {
         stop(
           "Could not find today's pitcher projections in expected folder, or replacement not specified"
         )
       } else {
-        file.copy(pitcher_file, pitcher_destination)
+        file.copy(pitcher_file, pitcher_destination, overwrite=TRUE)
       }
     }
     
@@ -121,7 +121,7 @@ load_players_with_projections <-
         select(player_id, team, manager) %>%
         full_join(load_players(force_all)) %>%
         full_join(load_draft_results(), by = c("name_full" = "player")) %>%
-        left_join(load_projections(force_all, batter_file, pitcher_file),
+        inner_join(load_projections(force_all, batter_file, pitcher_file),
                   by = c("name_full" = "name", "type" = "type")) %>%
         mutate(team = if_else(is.na(team), "Free Agent", team),
                team = fct_reorder(team, z_sum)) %>%

### 2019-06-01 rosterReview_generic.Rmd
Moved more munging code to helper, finished a few to-dos

@@
 ```{r}
-force <- FALSE
+force <- TRUE
 force_all <- FALSE
@@
 ```{r}
-#TODO move to helper
-rosters %>% 
-  filter(type != 'NA', team != 'Free Agent') %>%
-  group_by(type) %>% 
-  summarize(adj = median(z_sum)) -> z_sum_adj
-
-rosters <- rosters %>% 
-  filter(!type == 'NA') %>% 
-  mutate(zar = if_else(type=="batter",
-                       z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
-                       z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"]))
-
-position_columns <- rosters %>%
-    select(starts_with("eligible_positions")) %>%
-    colnames()
-
-rosters %>%
-  mutate(positions = paste(!!! syms(position_columns), sep = "," )) %>%
-  mutate(positions = gsub('NA', '', positions)) %>%
-  mutate(positions = gsub("^,*|(?<=,),|,*$", "", positions, perl=T)) %>%
-  select(-(starts_with("eligible_positions"))) -> rosters
-```
-
-```{r}
 #TODO abstract some of these views
-#FIXME some join issues here
 rosters %>% 
@@
   arrange(zar %>% desc) %>% 
-  select(name_full, display_position, type, zar) %>% 
+  select(name_full, positions, type, zar) %>% 
   View()
@@
 rosters %>% 
-  filter(grepl("Plouffe|theriverbrew",team)) %>% 
+  filter(grepl("process|Dorn",team)) %>% 
   select(team, manager, name_full, display_position, zar) %>% 
-  filter(grepl("deGrom|Lucchesi",name_full)) %>% 
+  filter(grepl("Cain|Price|Romo|Trout|Whitley|Claudio",name_full)) %>% 
   group_by(team) %>% 
@@
 rosters %>% 
-  filter(!grepl("Free Agent",team),
-  grepl("CF",positions)
+  filter(!grepl("Free Agent",team)
+  #        ,
+  # grepl("CF",positions)
        ) %>%
   ggplot(aes(x=team,y=zar,color=type)) +
-  #geom_boxplot() +
-  geom_jitter(aes(text=name_full), width = .2) +
+  geom_boxplot() +
+  # geom_jitter(aes(text=name_full), width = .2) +
   coord_flip() -> tb
@@
 ```
+
+```{r}
+#TODO move to separate research
+#FIXME where is Robinson Chirinos?
+
+rosters_by_position <- row_per_position(rosters)
+
+rosters_by_position %>% 
+  filter(team != "Free Agent") %>% 
+  ggplot(aes(position, zar, color = position, alpha = zar)) +
+  geom_point(aes(text=name_full)) +
+  facet_wrap(~ team) -> team_pos
+
+ggplotly(team_pos)
+```

### 2019-06-01 R/helper.R

@@ -4,11 +4,9 @@ library(stringi)
 source("R/z_scores.R")
 source("R/yahoo_api.R")
 
-#TODO review/resolve all player name joins (orphaned results, incorrect assignments)
 #TODO ingest performance data from fangraphs
-#TODO add position column compact options for load player data
-#TODO add z_adj -> zar (sets z_score above replacement, based on median z_score of rostered players, grouped by type [batter/pitcher])
 #TODO create a "get latest compiled roster" method
+#TODO add overall/by type rankings
 
 filename_today <- function(name) {
   paste0("data/", name, "_", gsub("-", "", Sys.Date()), ".Rds")
@@ -125,8 +123,105 @@ load_players_with_projections <-
                   by = c("name_full" = "name", "type" = "type")) %>%
         mutate(team = if_else(is.na(team), "Free Agent", team),
                team = fct_reorder(team, z_sum)) %>%
+        compact_positions() %>% 
+        rescale_z_sum() %>% 
         saveRDS(file)
     }
     
     readRDS(file)
   }
+
+rescale_z_sum <- function(df) {
+  df %>% 
+    filter(type != 'NA', team != 'Free Agent') %>%
+    group_by(type) %>% 
+    summarize(adj = median(z_sum)) -> z_sum_adj
+  
+  df %>% 
+    filter(!type == 'NA') %>% 
+    mutate(zar = if_else(type=="batter",
+                         z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
+                         z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"]))
+}
+
+compact_positions <- function(df) {
+  position_columns <- df %>%
+    select(starts_with("eligible_positions")) %>%
+    colnames()
+  
+  df %>%
+    mutate(positions = paste(!!! syms(position_columns), sep = "," )) %>%
+    mutate(positions = gsub('NA', '', positions)) %>%
+    mutate(positions = gsub("^,*|(?<=,),|,*$", "", positions, perl=T)) %>%
+    select(-(starts_with("eligible_positions"))) %>% 
+    mutate(positions = if_else(positions == "",position,positions))
+}
+
+row_per_position <- function(df) {
[…]

### 2019-06-04 rosterReview_generic.Rmd
Latest projections, further fleshing out per-position view

@@
 ggplotly(team_pos)
+
+rosters_by_position %>% 
+  filter(!is.na(manager)) %>% 
+  group_by(position) %>% 
+  count() %>% 
+  ungroup() -> count_by_pos
+
+rosters_by_position %>% 
+  group_by(position) %>% 
+  arrange(zar %>% desc()) %>% 
+  mutate(num = row_number()) %>% 
+  ungroup %>% 
+  full_join(count_by_pos, "position") %>% 
+  filter(num <= 1.5 * n) %>% 
+  select(team, manager, name_full, position, zar) %>% View()
 ```

### 2019-06-04 R/helper.R

@@ -7,6 +7,7 @@ source("R/yahoo_api.R")
 #TODO ingest performance data from fangraphs
 #TODO create a "get latest compiled roster" method
 #TODO add overall/by type rankings
+#TODO rank/zar by position
 
 filename_today <- function(name) {
   paste0("data/", name, "_", gsub("-", "", Sys.Date()), ".Rds")
@@ -61,8 +62,8 @@ load_projections <-
     pitcher_destination <-
       paste0(file_start, "pitchers_", date_string, ".csv")
     
-    if (force | !batter_destination %>% file.exists()) {
-      if (batter_file %>% is_null() | !batter_file %>% file.exists()) {
+    if (force || !batter_destination %>% file.exists()) {
+      if (batter_file %>% is_null() || !batter_file %>% file.exists()) {
         stop(
           "Could not find today's batter projections in expected folder, or replacement not specified"
         )
@@ -71,8 +72,8 @@ load_projections <-
       }
     }
     
-    if (force | !pitcher_destination %>% file.exists()) {
-      if (pitcher_file %>% is_null() | !pitcher_file %>% file.exists()) {
+    if (force || !pitcher_destination %>% file.exists()) {
+      if (pitcher_file %>% is_null() || !pitcher_file %>% file.exists()) {
         stop(
           "Could not find today's pitcher projections in expected folder, or replacement not specified"
         )

### 2019-06-04 rosterReview_generic.Rmd
Standardize import of new projections

@@
 force_all <- FALSE
-batter_file <- NULL
-pitcher_file <- NULL
+batter_file <- "temp/FanGraphs Leaderboard.csv"
+pitcher_file <- "temp/FanGraphs Leaderboard (1).csv"
 
-rosters <- load_players_with_projections(force, force_all, batter_file, pitcher_file)
+if (force_all && (batter_file %>% is.null() || pitcher_file %>% is.null())) {
+  stop("Need projection files to force a recalc")
+} else {
+  rosters <- load_players_with_projections(force, 
+                                           force_all, 
+                                           batter_file, 
+                                           pitcher_file)
+}
+
 ```
@@
 rosters %>% 
-  filter(grepl("Plouffe|Utleys",team)) %>% 
+  filter(grepl("Plouffe|Deez",team)) %>% 
   select(team, manager, name_full, display_position, zar) %>% 
@@
 rosters %>% 
-  filter(grepl("Plouffe|Utleys",team)) %>% 
+  filter(grepl("Plouffe|Deez",team)) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +
@@
 rosters %>% 
-  filter(grepl("process|Dorn",team)) %>% 
+  filter(grepl("Dorn|Plouffe",team)) %>% 
   select(team, manager, name_full, display_position, zar) %>% 
-  filter(grepl("Cain|Price|Romo|Trout|Whitley|Claudio",name_full)) %>% 
+  filter(grepl("Puig|Yonny Chir",name_full)) %>% 
   group_by(team) %>% 

### 2019-06-04 rosterReview_generic.Rmd
Per position zar sketches

@@
   count() %>% 
-  ungroup() -> count_by_pos
+  ungroup() -> rostered_count_by_pos
 
@@
   mutate(num = row_number()) %>% 
-  ungroup %>% 
-  full_join(count_by_pos, "position") %>% 
-  filter(num <= 1.5 * n) %>% 
-  select(team, manager, name_full, position, zar) %>% View()
+  full_join(rostered_count_by_pos, "position") %>% 
+  filter(num <= n) %>% 
+  summarize(median_zar = median(zar)) -> pos_median_zar
+
+rosters_by_position %>% 
+  full_join(pos_median_zar) %>% 
+  mutate(pos_zar = zar + median_zar) -> rosters_by_position
+
+rosters_by_position %>% 
+  select(team, manager, name_full, position, zar, pos_zar) %>% 
+  View()
+
+rosters_by_position %>% 
+  filter(team != "Free Agent") %>% 
+  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
+  geom_point(aes(text=name_full)) +
+  facet_wrap(~ team) -> team_pos_adj
+
+ggplotly(team_pos_adj)
+
 ```

### 2019-06-04 rosterReview_generic.Rmd
Some WAR draft views

@@
 rosters %>% 
-  filter(grepl("Plouffe|Deez",team)) %>% 
+  filter(grepl("Plouffe|Dorn",team)) %>% 
   select(team, manager, name_full, display_position, zar) %>% 
@@
 rosters %>% 
-  filter(grepl("Plouffe|Deez",team)) %>% 
+  filter(grepl("Plouffe|Dorn",team)) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +
@@
 rosters %>% 
-  filter(grepl("Dorn|Plouffe",team)) %>% 
+  filter(grepl("Dorn|process",team)) %>% 
   select(team, manager, name_full, display_position, zar) %>% 
-  filter(grepl("Puig|Yonny Chir",name_full)) %>% 
+  filter(grepl("Trout|Whitley|Cain|Price",name_full)) %>% 
   group_by(team) %>% 
   summarize(zar = sum(zar))
+
+rosters %>% 
+  filter(grepl("Dorn|process",team)) %>% 
+  select(team, manager, name_full, display_position, war) %>% 
+  filter(grepl("Trout|Whitley|Cain|Price",name_full))
 ```
@@
 #TODO measuring projected value of draft picks, move to separate research
+#TODO get beginning of year zar/war values
 rosters %>% 
@@
   ggplot(aes(x=draft_round,y=zar,group=draft_round)) +
+  geom_boxplot()
+
+rosters %>% 
+  filter(!is.na(draft_pick)) %>%
+  group_by(draft_round) %>% 
+  summarize(war_median = median(war) %>% janitor::round_half_up(),
+            war_mean = mean(war) %>% janitor::round_half_up()) %>%
+  ggplot(aes(x=draft_round,y=war_mean)) +
+  geom_col() +
+  geom_line(aes(y=war_median)) -> draft_plot_war
+
+ggplotly(draft_plot_war)
+
+rosters %>% 
+  filter(!is.na(draft_pick)) %>% 
+  group_by(draft_round) %>% 
+  arrange(draft_round) %>% 
+  ggplot(aes(x=draft_round,y=war,group=draft_round)) +
   geom_boxplot()

### 2019-06-05 rosterReview_generic.Rmd
Minor pos_zar bug fix

@@
 rosters %>% 
-  filter(grepl("Plouffe|Dorn",team)) %>% 
-  select(team, manager, name_full, display_position, zar) %>% 
+  filter(grepl("Plouffe|Matter",team)) %>% 
+  select(team, manager, name_full, display_position, zar, positions) %>% 
   arrange(zar %>% desc) %>% 
@@
 rosters %>% 
-  filter(grepl("Plouffe|Dorn",team)) %>% 
+  filter(grepl("Plouffe|Matter",team)) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +
@@
 rosters %>% 
-  filter(grepl("Dorn|process",team)) %>% 
+  filter(grepl("Plouffe|Matter",team)) %>% 
   select(team, manager, name_full, display_position, zar) %>% 
-  filter(grepl("Trout|Whitley|Cain|Price",name_full)) %>% 
-  group_by(team) %>% 
-  summarize(zar = sum(zar))
-
-rosters %>% 
-  filter(grepl("Dorn|process",team)) %>% 
-  select(team, manager, name_full, display_position, war) %>% 
-  filter(grepl("Trout|Whitley|Cain|Price",name_full))
+  filter(grepl("Hicks|Muncy",name_full)) 
+# %>%
+#   group_by(team) %>%
+#   summarize(zar = sum(zar))
 ```
@@
 #TODO move to separate research
-#FIXME where is Robinson Chirinos?
 
@@
   full_join(pos_median_zar) %>% 
-  mutate(pos_zar = zar + median_zar) -> rosters_by_position
+  mutate(pos_zar = zar - median_zar) -> rosters_by_position
 

### 2019-06-06 rosterReview_generic.Rmd
New projections, found some duplicates, trying some per-team average views

@@
 
+#TODO review duplicates
 ```
@@
   full_join(pos_median_zar) %>% 
+  #FIXME two decimal places for pos_zar
   mutate(pos_zar = zar - median_zar) -> rosters_by_position
@@
 
+# Averaging pos_zar by position, overall
+# Does this actually indicate good/bad teams?
+rosters_by_position %>% 
+  filter(team != "Free Agent") %>% 
+  group_by(team, position) %>% 
+  summarize(avg_pos_zar = mean(pos_zar)) -> team_pos_avg_zar
+
+team_pos_avg_zar %>%  
+  ggplot(aes(position, avg_pos_zar, color = position)) +
+  geom_point() +
+  facet_wrap(~ team) -> team_avg_pos
+
+ggplotly(team_avg_pos)
+
+team_pos_avg_zar %>% 
+  ungroup() %>% 
+  group_by(team) %>% 
+  summarize(avg_pos_zar = mean(avg_pos_zar)) %>% 
+  arrange(avg_pos_zar %>% desc)
 ```

### 2019-06-07 rosterReview_generic.Rmd
Reordering research in generic rmd

@@
 force <- TRUE
-force_all <- FALSE
+force_all <- TRUE
 batter_file <- "temp/FanGraphs Leaderboard.csv"
@@
   View()
-```
-
-```{r}
-# TODO find way to wrap these three views into one
-rosters %>% 
-  filter(grepl("Plouffe|Matter",team)) %>% 
-  select(team, manager, name_full, display_position, zar, positions) %>% 
-  arrange(zar %>% desc) %>% 
-  View()
-  # mutate(zar = janitor::round_half_up(zar)) %>% 
-  # write_csv("data/tradeReview_20190423.csv")
-
-rosters %>% 
-  filter(grepl("Plouffe|Matter",team)) %>% 
-  ggplot(aes(x=team,y=zar,color=type)) +
-  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
-  coord_flip() -> tv
-
-ggplotly(tv)
-
-rosters %>% 
-  filter(grepl("Plouffe|Matter",team)) %>% 
-  select(team, manager, name_full, display_position, zar) %>% 
-  filter(grepl("Hicks|Muncy",name_full)) 
-# %>%
-#   group_by(team) %>%
-#   summarize(zar = sum(zar))
-```
-
-```{r}
-rosters %>% 
-  filter(!grepl("Free Agent",team)
-  #        ,
-  # grepl("CF",positions)
-       ) %>%
-  ggplot(aes(x=team,y=zar,color=type)) +
-  geom_boxplot() +
-  # geom_jitter(aes(text=name_full), width = .2) +
-  coord_flip() -> tb
-
-ggplotly(tb)
-```
-
-```{r}
-#TODO measuring projected value of draft picks, move to separate research
-#TODO get beginning of year zar/war values
-rosters %>% 
-  filter(!is.na(draft_pick)) %>%
-  group_by(draft_round) %>% 
-  summarize(zar_median = median(zar) %>% janitor::round_half_up(),
-            zar_mean = mean(zar) %>% janitor::round_half_up()) %>%
-  ggplot(aes(x=draft_round,y=zar_mean)) +
-  geom_col() +
-  geom_line(aes(y=zar_median)) -> draft_plot
-
-ggplotly(draft_plot)
-
-rosters %>% 
-  filter(!is.na(draft_pick)) %>% 
-  group_by(draft_round) %>% 
-  arrange(draft_round) %>% 
-  ggplot(aes(x=draft_round,y=zar,group=draft_round)) +
-  geom_boxplot()
-
-rosters %>% 
-  filter(!is.na(draft_pick)) %>%
-  group_by(draft_round) %>% 
-  summarize(war_median = median(war) %>% janitor::round_half_up(),
-            war_mean = mean(war) %>% janitor::round_half_up()) %>%
-  ggplot(aes(x=draft_round,y=war_mean)) +
-  geom_col() +
-  geom_line(aes(y=war_median)) -> draft_plot_war
-
-ggplotly(draft_plot_war)
-
-rosters %>% 
-  filter(!is.na(draft_pick)) %>% 
-  group_by(draft_round) %>% 
-  arrange(draft_round) %>% 
-  ggplot(aes(x=draft_round,y=war,group=draft_round)) +
-  geom_boxplot()
 ```
@@
   group_by(team) %>% 
-  summarize(avg_pos_zar = mean(avg_pos_zar)) %>% 
-  arrange(avg_pos_zar %>% desc)
+  summarize(ovrl_avg_pos_zar = mean(avg_pos_zar),
+            var_pos_zar = sd(avg_pos_zar)) %>% 
+  arrange(ovrl_avg_pos_zar %>% desc)
+
+rosters_by_position %>% 
+  filter(team != "Free Agent") %>% 
+  ggplot(aes(pos_zar)) + 
+  geom_freqpoly(binwidth=.25) + 
+  facet_wrap(~ position)
 ```
+
+```{r}
+# TODO find way to wrap these three views into one
+rosters %>% 
+  filter(grepl("Plouffe|Nuts",team)) %>% 
+  select(team, manager, name_full, display_position, zar, positions) %>% 
+  arrange(zar %>% desc) %>% 
+  View()
+  # mutate(zar = janitor::round_half_up(zar)) %>% 
+  # write_csv("data/tradeReview_20190423.csv")
+
+rosters %>% 
+  filter(grepl("Plouffe|Nuts",team)) %>% 
+  ggplot(aes(x=team,y=zar,color=type)) +
+  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
+  coord_flip() -> tv
+
+ggplotly(tv)
+
+rosters %>% 
+  #filter(grepl("Plouffe|Oakmont|Nuts",team)) %>% 
+  select(team, manager, name_full, display_position, zar) %>% 
+  filter(grepl("Benintendi|Martin Perez",name_full)) 
+# %>%
+#   group_by(team) %>%
+#   summarize(zar = sum(zar))
+```
+
+```{r}
+rosters %>% 
+  filter(!grepl("Free Agent",team)
+  #        ,
+  # grepl("CF",positions)
+       ) %>%
+  ggplot(aes(x=team,y=zar,color=type)) +
+  geom_boxplot() +
+  # geom_jitter(aes(text=name_full), width = .2) +
+  coord_flip() -> tb
+
+ggplotly(tb)
+```
+
+```{r}
+#TODO measuring projected value of draft picks, move to separate research
+#TODO get beginning of year zar/war values
+rosters %>% 
+  filter(!is.na(draft_pick)) %>%
+  group_by(draft_round) %>% 
+  summarize(zar_median = median(zar) %>% janitor::round_half_up(),
+            zar_mean = mean(zar) %>% janitor::round_half_up()) %>%
+  ggplot(aes(x=draft_round,y=zar_mean)) +
+  geom_col() +
+  geom_line(aes(y=zar_median)) -> draft_plot
+
+ggplotly(draft_plot)
+
+rosters %>% 
+  filter(!is.na(draft_pick)) %>% 
+  group_by(draft_round) %>% 
+  arrange(draft_round) %>% 
+  ggplot(aes(x=draft_round,y=zar,group=draft_round)) +
+  geom_boxplot()
+
+rosters %>% 
+  filter(!is.na(draft_pick)) %>%
+  group_by(draft_round) %>% 
+  summarize(war_median = median(war) %>% janitor::round_half_up(),
+            war_mean = mean(war) %>% janitor::round_half_up()) %>%
+  ggplot(aes(x=draft_round,y=war_mean)) +
+  geom_col() +
+  geom_line(aes(y=war_median)) -> draft_plot_war
+
+ggplotly(draft_plot_war)
+
+rosters %>% 
+  filter(!is.na(draft_pick)) %>% 
+  group_by(draft_round) %>% 
+  arrange(draft_round) %>% 
+  ggplot(aes(x=draft_round,y=war,group=draft_round)) +
+  geom_boxplot()
+```

### 2019-06-09 rosterReview_generic.Rmd
Latest projections and rosters

@@
   mutate(zar = round(zar)) %>% 
-  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
+  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +
@@
 rosters %>% 
-  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
+  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
   arrange(zar %>% desc) %>% 

### 2019-06-11 rosterReview_generic.Rmd
Latest rosters, many big trades lately

@@
 
+#TODO 3 OFs, players with multiple positions, avoid bench players
 team_pos_avg_zar %>% 
@@
   group_by(team) %>% 
-  summarize(ovrl_avg_pos_zar = mean(avg_pos_zar),
+  summarize(sum_pos_zar = sum(avg_pos_zar),
+            mean_pos_zar = mean(avg_pos_zar),
             var_pos_zar = sd(avg_pos_zar)) %>% 
-  arrange(ovrl_avg_pos_zar %>% desc)
+  arrange(mean_pos_zar %>% desc)
 

### 2019-06-14 rosterReview_generic.Rmd
Latest rosters, ohtani missing

@@
   arrange(zar %>% desc) %>% 
-  select(name_full, positions, type, zar) %>% 
+  select(team, name_full, positions, type, zar) %>% 
   View()
@@
   select(team, manager, name_full, position, zar, pos_zar) %>% 
+  # filter(position %in% c('SP','RP')) %>% 
   View()

### 2019-06-14 R/helper.R
Fix for yahoo two-way player naming

@@ -40,11 +40,14 @@ load_players <- function(force = FALSE) {
   if (force || !file %>% file.exists()) {
     get_players(2500) %>%
       clean_names() %>%
-      mutate(type = case_when(
-        position_type == "B" ~ "batter",
-        position_type == "P" ~ "pitcher",
-        TRUE ~ "other"
-      )) %>% 
+      mutate(
+        type = case_when(
+          position_type == "B" ~ "batter",
+          position_type == "P" ~ "pitcher",
+          TRUE ~ "other"),
+        # Shoehei Ohtani treated as two separate players, breaking join
+        name_full = gsub(" (Pitcher)", "", name_full, fixed=TRUE),
+        name_full = gsub(" (Batter)", "", name_full, fixed=TRUE)) %>% 
       select(-position_type) %>% 
       saveRDS(file)
   }

### 2019-06-15 rosterReview_generic.Rmd
WIP adding latest data retrieval methods

@@
   # filter(position %in% c('SP','RP')) %>% 
+  filter(grepl("Plouffe",team)) %>% 
+  arrange(pos_zar %>% desc) %>% 
   View()

### 2019-06-15 R/helper.R

@@ -13,6 +13,14 @@ filename_today <- function(name) {
   paste0("data/", name, "_", gsub("-", "", Sys.Date()), ".Rds")
 }
 
+read_latest_data_file <- function(name) {
+  list.files("./data",
+             pattern ="yahoo_players",
+             full.names = TRUE) %>% 
+    tail(1) %>% 
+    readRDS()
+}
+
 load_draft_results <- function() {
   read_tsv("data/draftResults.tsv") %>%
     clean_names() %>%
@@ -25,19 +33,19 @@ load_draft_results <- function() {
 }
 
 load_rosters <- function(force = FALSE) {
-  file <- filename_today("rosters")
+  file <- "rosters"
   
-  if (force || !file %>% file.exists()) {
+  if (force) {
     get_team_rosters() %>%
-      saveRDS(file)
+      saveRDS(filename_today(file))
   }
-  readRDS(file)
+  read_latest_data_file(file)
 }
 
 load_players <- function(force = FALSE) {
-  file <- filename_today("yahoo_players")
+  file <- "yahoo_players"
   
-  if (force || !file %>% file.exists()) {
+  if (force) {
     get_players(2500) %>%
       clean_names() %>%
       mutate(
@@ -45,15 +53,16 @@ load_players <- function(force = FALSE) {
           position_type == "B" ~ "batter",
           position_type == "P" ~ "pitcher",
           TRUE ~ "other"),
-        # Shoehei Ohtani treated as two separate players, breaking join
+        # two-way players treated as two separate players, breaking join
         name_full = gsub(" (Pitcher)", "", name_full, fixed=TRUE),
         name_full = gsub(" (Batter)", "", name_full, fixed=TRUE)) %>% 
       select(-position_type) %>% 
-      saveRDS(file)
+      saveRDS(filename_today(file))
   }
-  readRDS(file)
+  read_latest_data_file(file)
 }
 
+#TODO
 load_projections <-
   function(force = FALSE,
            batter_file = NULL,
@@ -116,7 +125,7 @@ load_players_with_projections <-
            force_all = FALSE,
            batter_file = NULL,
            pitcher_file = NULL) {
-    file <- filename_today("rosters_with_projections")
+    file <- "rosters_with_projections"
     
     if (force || force_all || !file %>% file.exists()) {
       load_rosters(force_all) %>%
@@ -129,10 +138,10 @@ load_players_with_projections <-
[…]

### 2019-06-15 R/helper.R
Finished a latest compiled data method, now need to use it. Renamed roster files to team_rosters to avoid name conflict on regex search

@@ -5,20 +5,43 @@ source("R/z_scores.R")
 source("R/yahoo_api.R")
 
 #TODO ingest performance data from fangraphs
-#TODO create a "get latest compiled roster" method
 #TODO add overall/by type rankings
 #TODO rank/zar by position
+#TODO move all read_csv references to read_latest_file_csv
 
-filename_today <- function(name) {
-  paste0("data/", name, "_", gsub("-", "", Sys.Date()), ".Rds")
+filename_today <- function(name, extension) {
+  paste0("data/", name, "_", gsub("-", "", Sys.Date()), extension)
 }
 
-read_latest_data_file <- function(name) {
-  list.files("./data",
-             pattern ="yahoo_players",
+filename_today_rds <- function(name) {
+  filename_today(name, ".Rds")
+}
+
+filename_today_csv <- function(name) {
+  filename_today(name, ".csv")
+}
+
+find_latest_data_file <- function(name) {
+  #FIXME search by extension
+  rslt <- list.files("./data",
+             pattern = name,
              full.names = TRUE) %>% 
-    tail(1) %>% 
+    tail(1)
+  
+  paste0("Found file = ", rslt) %>% print()
+  
+  rslt
+}
+
+read_latest_file_rds <- function(name) {
+   find_latest_data_file(name) %>% 
     readRDS()
+}
+
+read_latest_file_csv <- function(name) {
+  find_latest_data_file(name) %>% 
+    read_csv() %>% 
+    clean_names()
 }
 
 load_draft_results <- function() {
@@ -33,13 +56,13 @@ load_draft_results <- function() {
 }
 
 load_rosters <- function(force = FALSE) {
-  file <- "rosters"
+  file <- "team_rosters"
   
   if (force) {
     get_team_rosters() %>%
-      saveRDS(filename_today(file))
+      saveRDS(filename_today_rds(file))
   }
-  read_latest_data_file(file)
+  read_latest_file_rds(file)
 }
 
 load_players <- function(force = FALSE) {
@@ -57,47 +80,39 @@ load_players <- function(force = FALSE) {
         name_full = gsub(" (Pitcher)", "", name_full, fixed=TRUE),
         name_full = gsub(" (Batter)", "", name_full, fixed=TRUE)) %>% 
       select(-position_type) %>% 
-      saveRDS(filename_today(file))
+      saveRDS(filename_today_rds(file))
   }
-  read_latest_data_file(file)
[…]

### 2019-06-20 rosterReview_generic.Rmd
A few days of lineup retrieval, a few bug fixes. Prepping reaction to rival team trade

--- 2019-06-11 rosterReview_generic.Rmd
@@
 ```{r}
-force <- TRUE
-force_all <- TRUE
+force_fetch <- TRUE
+force_join <- TRUE
 batter_file <- "temp/FanGraphs Leaderboard.csv"
@@
 
-if (force_all && (batter_file %>% is.null() || pitcher_file %>% is.null())) {
+if (force_fetch && (batter_file %>% is.null() || pitcher_file %>% is.null())) {
   stop("Need projection files to force a recalc")
 } else {
-  rosters <- load_players_with_projections(force, 
-                                           force_all, 
+  rosters <- load_players_with_projections(force_fetch, 
+                                           force_join, 
                                            batter_file, 
@@
   arrange(zar %>% desc) %>% 
-  select(name_full, positions, type, zar) %>% 
-  View()
+  mutate(zar = zar %>% round(digits=1)) %>% 
+  select(team, name_full, positions, type, zar) %>% 
+  View("Available Free Agents")
 ```
@@
   select(team, manager, name_full, position, zar, pos_zar) %>% 
-  View()
+  # filter(position %in% c('SP','RP')) %>% 
+  filter(grepl("Plouffe",team)) %>% 
+  arrange(pos_zar %>% desc) %>%
+  mutate(pos_zar = pos_zar %>% round(1),
+         zar = zar %>% round(1)) %>% 
+  View("ZAR by Position")
 
@@
 rosters %>% 
-  filter(grepl("Plouffe|Nuts",team)) %>% 
+  filter(grepl("Plouffe|Bump",team)) %>% 
   select(team, manager, name_full, display_position, zar, positions) %>% 
   arrange(zar %>% desc) %>% 
-  View()
+  mutate(zar = zar %>% round(1)) %>% 
+  View("Trade Partner")
   # mutate(zar = janitor::round_half_up(zar)) %>% 
@@
 rosters %>% 
-  filter(grepl("Plouffe|Nuts",team)) %>% 
+  filter(grepl("Plouffe|Bump",team)) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +

### 2019-06-20 R/helper.R

@@ -95,9 +95,9 @@ load_projections <- function(force = FALSE,
   
   if (force) {
     if (batter_projection_file %>% is_null() || 
-        batter_projection_file %>% !file.exists() ||
+        !batter_projection_file %>% file.exists() ||
         pitcher_projection_file %>% is_null() ||
-        pitcher_projection_file %>% !file.exists()) {
+        !pitcher_projection_file %>% file.exists()) {
       stop(
         "Could not find today's batter or pitcher projections in expected folder, or replacement not specified"
       )

### 2019-07-04 midyear_perfVsProj.Rmd
Starting comparison of projections vs this year's performance

---
title: "Midyear Performance vs Projection"
author: "Tom Kain"
date: "7/3/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(glue)
library(plotly)

source("R/helper.R")
```

```{r}
#Latest rosters with projections
pitchers <- load_players_with_projections() %>% 
  filter(type == 'pitcher')

#Manually loading latest performance from fangraphs
pitcher_perf <- "temp/FanGraphs Leaderboard.csv" %>% 
  add_z_scores("pitcher") %>% 
  clean_names() %>% 
  select(type, playerid, name:so,era:war, z_sv:z_sum) %>% 
  mutate(playerid = as.character(playerid))

rosters_perf <- pitcher_perf %>% 
  rename(z_perf = z_sum) %>% 
  select(playerid, z_perf) %>% 
  right_join(pitchers)

rosters_perf %>% 
  filter(team != 'Free Agent') %>% 
  summarize(perf_adj = median(z_perf, na.rm = TRUE),
            proj_adj = median(z_sum, na.rm = TRUE)) %>% 
  summarize(adj = proj_adj - perf_adj) %>% 
  pull() -> adj

rosters_perf %>% 
  mutate(z_perf = z_perf + adj) -> rosters_perf
```

```{r}
rosters_perf %>% 
  filter(grepl("SP",positions)) %>% 
  ggplot(aes(z_sum,z_perf,color=team)) +
  geom_point(aes(text=name_full)) +
  geom_abline(slope = 1)-> p

ggplotly(p)
```

### 2019-07-06 optimalLineup.Rmd
Starting optimal lineup logic

--- 2019-06-14 rosterReview_generic.Rmd
@@
 ---
-title: "Roster Review (Generic)"
+title: "Optimal Lineup"
 author: "Tom Kain"
-date: "April 25, 2019"
+date: "July 6, 2019"
 output: html_document
-editor_options: 
-  chunk_output_type: console
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
-library(tidyverse)
-library(glue)
-library(plotly)
-
-source("R/helper.R")
 ```
@@
 ```{r}
-force <- TRUE
-force_all <- TRUE
-batter_file <- "temp/FanGraphs Leaderboard.csv"
-pitcher_file <- "temp/FanGraphs Leaderboard (1).csv"
-
-if (force_all && (batter_file %>% is.null() || pitcher_file %>% is.null())) {
-  stop("Need projection files to force a recalc")
-} else {
-  rosters <- load_players_with_projections(force, 
-                                           force_all, 
-                                           batter_file, 
-                                           pitcher_file)
-}
-
-#TODO review duplicates
-```
-
-```{r}
-#TODO abstract some of these views
-rosters %>% 
-  mutate(zar = round(zar)) %>% 
-  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
-  ggplot(aes(x=team,y=zar,color=type)) +
-  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
-  coord_flip() -> pa
-
-ggplotly(pa)
-
-rosters %>% 
-  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
-  arrange(zar %>% desc) %>% 
-  select(team, name_full, positions, type, zar) %>% 
-  View()
-```
-
-```{r}
-#TODO move to separate research
-
 rosters_by_position <- row_per_position(rosters)
-
-rosters_by_position %>% 
-  filter(team != "Free Agent") %>% 
-  ggplot(aes(position, zar, color = position, alpha = zar)) +
-  geom_point(aes(text=name_full)) +
-  facet_wrap(~ team) -> team_pos
-
-ggplotly(team_pos)
 
@@
 
-rosters_by_position %>% 
-  select(team, manager, name_full, position, zar, pos_zar) %>% 
-  # filter(position %in% c('SP','RP')) %>% 
-  View()
+team <- rosters_by_position %>% 
+  filter(team == "Plouffe There It Is!")
 
-rosters_by_position %>% 
-  filter(team != "Free Agent") %>% 
-  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
-  geom_point(aes(text=name_full)) +
-  facet_wrap(~ team) -> team_pos_adj
+positions <- c("C","1B","2B","3B","SS","LF","CF","RF","Util")
 
-ggplotly(team_pos_adj)
+result <- tibble(
+  position = positions,
+  player_id = NA
+)
 
-# Averaging pos_zar by position, overall
-# Does this actually indicate good/bad teams?
-rosters_by_position %>% 
-  filter(team != "Free Agent") %>% 
-  group_by(team, position) %>% 
-  summarize(avg_pos_zar = mean(pos_zar)) -> team_pos_avg_zar
+batters <- team %>%
+  filter(type == "batter") %>% 
+  arrange(pos_zar %>% desc(), zar %>% desc() ) %>% 
+  select(player_id, name_full, position, pos_zar, zar)
 
-team_pos_avg_zar %>%  
-  ggplot(aes(position, avg_pos_zar, color = position)) +
-  geom_point() +
-  facet_wrap(~ team) -> team_avg_pos
+batter_ids <- batters$player_id %>% 
+  as_factor() %>%
+  levels()
 
-ggplotly(team_avg_pos)
-
-#TODO 3 OFs, players with multiple positions, avoid bench players
-team_pos_avg_zar %>% 
-  ungroup() %>% 
-  group_by(team) %>% 
-  summarize(sum_pos_zar = sum(avg_pos_zar),
-            mean_pos_zar = mean(avg_pos_zar),
-            var_pos_zar = sd(avg_pos_zar)) %>% 
-  arrange(mean_pos_zar %>% desc)
-
-rosters_by_position %>% 
-  filter(team != "Free Agent") %>% 
-  ggplot(aes(pos_zar)) + 
-  geom_freqpoly(binwidth=.25) + 
-  facet_wrap(~ position)
+for (i in 0:length(batter_ids)) {
+  print(i+1)
+}
 ```
-
-```{r}
-# TODO find way to wrap these three views into one
-rosters %>% 
-  filter(grepl("Plouffe|Nuts",team)) %>% 
-  select(team, manager, name_full, display_position, zar, positions) %>% 
-  arrange(zar %>% desc) %>% 
-  View()
-  # mutate(zar = janitor::round_half_up(zar)) %>% 
-  # write_csv("data/tradeReview_20190423.csv")
-
-rosters %>% 
-  filter(grepl("Plouffe|Nuts",team)) %>% 
-  ggplot(aes(x=team,y=zar,color=type)) +
-  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
-  coord_flip() -> tv
-
-ggplotly(tv)
-
-rosters %>% 
-  #filter(grepl("Plouffe|Oakmont|Nuts",team)) %>% 
-  select(team, manager, name_full, display_position, zar) %>% 
-  filter(grepl("Benintendi|Martin Perez",name_full)) 
-# %>%
-#   group_by(team) %>%
-#   summarize(zar = sum(zar))
-```
-
-```{r}
-rosters %>% 
-  filter(!grepl("Free Agent",team)
-  #        ,
-  # grepl("CF",positions)
-       ) %>%
-  ggplot(aes(x=team,y=zar,color=type)) +
-  geom_boxplot() +
-  # geom_jitter(aes(text=name_full), width = .2) +
-  coord_flip() -> tb
-
-ggplotly(tb)
-```
-
-```{r}
-#TODO measuring projected value of draft picks, move to separate research
-#TODO get beginning of year zar/war values
-rosters %>% 
-  filter(!is.na(draft_pick)) %>%
-  group_by(draft_round) %>% 
-  summarize(zar_median = median(zar) %>% janitor::round_half_up(),
-            zar_mean = mean(zar) %>% janitor::round_half_up()) %>%
-  ggplot(aes(x=draft_round,y=zar_mean)) +
-  geom_col() +
-  geom_line(aes(y=zar_median)) -> draft_plot
-
-ggplotly(draft_plot)
-
-rosters %>% 
-  filter(!is.na(draft_pick)) %>% 
-  group_by(draft_round) %>% 
-  arrange(draft_round) %>% 
-  ggplot(aes(x=draft_round,y=zar,group=draft_round)) +
-  geom_boxplot()
-
-rosters %>% 
-  filter(!is.na(draft_pick)) %>%
-  group_by(draft_round) %>% 
-  summarize(war_median = median(war) %>% janitor::round_half_up(),
-            war_mean = mean(war) %>% janitor::round_half_up()) %>%
-  ggplot(aes(x=draft_round,y=war_mean)) +
-  geom_col() +
-  geom_line(aes(y=war_median)) -> draft_plot_war
-
-ggplotly(draft_plot_war)
-
-rosters %>% 
-  filter(!is.na(draft_pick)) %>% 
-  group_by(draft_round) %>% 
-  arrange(draft_round) %>% 
-  ggplot(aes(x=draft_round,y=war,group=draft_round)) +
-  geom_boxplot()
-```

### 2019-07-06 rosterReview_generic.Rmd
Starting optimal lineup logic

@@
 ```{r}
-force_fetch <- TRUE
-force_join <- TRUE
+force_fetch <- FALSE
+force_join <- FALSE
 batter_file <- "temp/FanGraphs Leaderboard.csv"
@@
 #TODO move to separate research
-
 rosters_by_position <- row_per_position(rosters)
-
-rosters_by_position %>% 
-  filter(team != "Free Agent") %>% 
-  ggplot(aes(position, zar, color = position, alpha = zar)) +
-  geom_point(aes(text=name_full)) +
-  facet_wrap(~ team) -> team_pos
-
-ggplotly(team_pos)
 
@@
   mutate(pos_zar = zar - median_zar) -> rosters_by_position
+
+```
+```{r}
+rosters_by_position %>% 
+  filter(team != "Free Agent") %>% 
+  ggplot(aes(position, zar, color = position, alpha = zar)) +
+  geom_point(aes(text=name_full)) +
+  facet_wrap(~ team) -> team_pos
+
+ggplotly(team_pos)
 
@@
 rosters %>% 
-  filter(grepl("Plouffe|Bump",team)) %>% 
+  filter(grepl("Plouffe|Mata",team)) %>% 
   select(team, manager, name_full, display_position, zar, positions) %>% 
@@
 rosters %>% 
-  filter(grepl("Plouffe|Bump",team)) %>% 
+  filter(grepl("Plouffe|Mata",team)) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +

### 2019-07-06 R/helper.R

@@ -206,8 +206,7 @@ row_per_position <- function(df) {
     mutate(CF = grepl("CF", positions)) %>% 
     mutate(RF = grepl("RF", positions)) %>% 
     mutate(SP = grepl("SP", positions)) %>% 
-    mutate(RP = grepl("RP", positions)) %>% 
-    mutate(DH = grepl("DH", positions))
+    mutate(RP = grepl("RP", positions)) 
   
   C <- df %>%
     filter(C) %>%
@@ -249,10 +248,6 @@ row_per_position <- function(df) {
     filter(RP) %>% 
     mutate(position = "RP")
   
-  DH <- df %>% 
-    filter(DH) %>% 
-    mutate(position = "DH")
-  
   C %>%
     bind_rows(`1B`) %>%
     bind_rows(`2B`) %>%
@@ -263,9 +258,32 @@ row_per_position <- function(df) {
     bind_rows(RF) %>% 
     bind_rows(SP) %>% 
     bind_rows(RP) %>% 
-    bind_rows(DH) %>% 
     unique() %>%
     arrange(z_sum %>% desc) %>%
     mutate(z_rank = row_number(),
-           position = fct_relevel(position, "C","1B", "2B","3B","SS","LF","CF","RF","DH","SP","RP"))
+           position = fct_relevel(position, "C","1B","2B","3B","SS","LF","CF","RF","SP","RP"))
 }
+
+#TODO WIP
+optimal_lineup <- function(df) {
+  positions <- c("C","1B","2B","3B","SS","LF","CF","RF","Util")
+  
+  result <- NULL
+  
+  for (team in df$team %>% levels()) {
+    team_result <- tibble(
+      position = positions,
+      player_id = NA
+    )
+    
+    batters <- df %>%
+      filter(type == "batter", 
+             team == team) %>% 
+      arrange(pos_zar %>% desc(), zar %>% desc() ) %>% 
+      select(player_id, name_full, position, pos_zar, zar)
+    
+    batter_ids <- batters$player_id %>% 
+      as_factor() %>%
+      levels()
+  }
+} 

### 2019-07-06 R/helper.R
Added approach notes for optimal lineup

@@ -265,6 +265,20 @@ row_per_position <- function(df) {
 }
 
 #TODO WIP
+# Assign by pos_zar (for each player, check if there are other rows beneath)
+# LF - Soto
+# RF - Bellinger
+# SS - Lindor
+# CF - Gallo (zar < LF && zar < RF)
+# Util - Story
+# 1B - Bell
+# C - Contreras
+# Bench - Puig (zar < RF && zar < Util)
+# Bench - Posey (zar < C && zar < Util zar < 1B)
+# 2B - Carpenter
+# 3B - Devers
+# Bench - Murphy (zar < 2B && zar < 1B && zar < Util)
+
 optimal_lineup <- function(df) {
   positions <- c("C","1B","2B","3B","SS","LF","CF","RF","Util")
   

### 2019-07-06 midyear_perfVsProj.Rmd
Latest rosters

@@
 #Manually loading latest performance from fangraphs
-pitcher_perf <- "temp/FanGraphs Leaderboard.csv" %>% 
+pitcher_perf <- "temp/FanGraphs Leaderboard - perf.csv" %>% 
   add_z_scores("pitcher") %>% 

### 2019-07-06 optimalLineup.Rmd
WIP optimal lineup

@@
 knitr::opts_chunk$set(echo = TRUE)
+library(tidyverse)
+library(glue)
+library(plotly)
+
+source("R/helper.R")
 ```
@@
 ```{r}
+rosters <- load_players_with_projections()
+
 rosters_by_position <- row_per_position(rosters)
@@
 
-result <- tibble(
-  position = positions,
-  player_id = NA
-)
-
+```
+```{r}
 batters <- team %>%
   filter(type == "batter") %>% 
-  arrange(pos_zar %>% desc(), zar %>% desc() ) %>% 
-  select(player_id, name_full, position, pos_zar, zar)
+  select(player_id, name_full, position, pos_zar, zar) %>% 
+  arrange(zar %>% desc(), pos_zar %>% desc)
 
@@
 
-for (i in 0:length(batter_ids)) {
-  print(i+1)
+team_result <- tibble(
+  position = positions,
+  player_id = NA
+)
+
+i <- 1
+
+```
+```{r}
+
+batter_id <- batter_ids[i]
+
+batter <- batters %>% 
+  filter(player_id == batter_id)
+
+batters <- batters %>% 
+  add_row(
+    player_id = batter$player_id[1],
+    name_full = batter$name_full[1],
+    position = "Util",
+    pos_zar = 0,
+    zar = batter$zar[1]
+  ) %>% 
+  arrange(zar %>% desc(), pos_zar %>% desc)
+
+for (j in 1:length(batter$position)) {
+  assign <- FALSE
+  if (team_result$player_id[team_result$position == batter$position[j]] %>% is.na()) {
+    team_result$player_id[team_result$position == batter$position[j]] <- batter_id
+    assign <- TRUE
+    break;
   }
+  #FIXME is getting called despite prior assignment
+  if (!assign && team_result$player_id[team_result$position == "Util"] %>% is.na()) {
+    team_result$player_id[team_result$position == "Util"] <- batter_id
+  }
+}
+
+i <- i+1
+
+batters
+
+#FIXME need Util in batters data set
+team_result %>% 
+  left_join(batters, c("player_id","position"))
 ```

### 2019-07-06 R/helper.R

@@ -274,8 +274,8 @@ row_per_position <- function(df) {
 # 1B - Bell
 # C - Contreras
 # Bench - Puig (zar < RF && zar < Util)
-# Bench - Posey (zar < C && zar < Util zar < 1B)
 # 2B - Carpenter
+# Bench - Posey (zar < C && zar < Util zar < 1B)
 # 3B - Devers
 # Bench - Murphy (zar < 2B && zar < 1B && zar < Util)
 
@@ -299,5 +299,26 @@ optimal_lineup <- function(df) {
     batter_ids <- batters$player_id %>% 
       as_factor() %>%
       levels()
+    
+    for (i in 1:length(batter_ids)) {
+      batter <- batters %>% 
+        filter(player_id == batter_ids[i]) %>% 
+        filter(row_number() == 1)
+      
+      if (team_result$player_id[team_result$position == batter$position] %>% is.na()) {
+        team_result$player_id[team_result$position == batter$position] <- batter$player_id
+      } else if (team_result$player_id[team_result$position == "Util"] %>% is.na()) {
+        team_result$player_id[team_result$position == "Util"] <- batter$player_id
+      }
+    }
+    
+    #TODO setup final df with join
+    
+    if (result %>% is.null()) {
+      result <- team_result()
+    } else {
+      result %>% 
+        bind_rows(team_result)
+    }
   }
 } 

### 2019-07-07 optimalLineup.Rmd
Optimal lineup working prototype

--- 2019-07-06 optimalLineup.Rmd
@@
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-result <- tibble(
-  position = positions,
-  player_id = NA
-)
+```
 
+```{r}
 batters <- team %>%
   filter(type == "batter") %>% 
-  arrange(pos_zar %>% desc(), zar %>% desc() ) %>% 
-  select(player_id, name_full, position, pos_zar, zar)
+  select(player_id, name_full, position, pos_zar, zar) %>% 
+  arrange(zar %>% desc(), pos_zar %>% desc)
 
@@
 
-for (i in 0:length(batter_ids)) {
-  print(i+1)
+team_result <- tibble(
+  position = positions,
+  player_id = NA
+)
+
+i <- 1
+
+```
+```{r}
+
+batter_id <- batter_ids[i]
+
+batter <- batters %>% 
+  filter(player_id == batter_id)
+
+batters <- batters %>% 
+  add_row(
+    player_id = batter$player_id[1],
+    name_full = batter$name_full[1],
+    position = "Util",
+    pos_zar = -100,
+    zar = batter$zar[1]
+  ) %>% 
+  arrange(zar %>% desc(), pos_zar %>% desc)
+
+for (j in 1:length(batter$position)) {
+  if (team_result$player_id[team_result$position == batter$position[j]] %>% is.na()) {
+    team_result$player_id[team_result$position == batter$position[j]] <- batter_id
+    print(paste0("Assigned ",batter_id," to ",batter$position[j]))
+    break
   }
+}
+
+if (!batter_id %in% (team_result$player_id %>% as_factor() %>% levels())) {
+  if (team_result$player_id[team_result$position == "Util"] %>% is.na()) {
+    team_result$player_id[team_result$position == "Util"] <- batter_id
+  }
+  else {
+    print(paste0("sending batter_id ", batter_id, " to bench"))
+  }
+}
+
+i <- i+1
+
+team_result %>% 
+  left_join(batters, c("player_id","position"))
 ```

### 2019-07-07 optimalLineup.Rmd
Working optional lineup (offense) function

--- 2019-07-06 optimalLineup.Rmd
@@
 ```{r}
+rosters <- load_players_with_projections()
+
 rosters_by_position <- row_per_position(rosters)
+```
 
-rosters_by_position %>% 
-  filter(!is.na(manager)) %>% 
-  group_by(position) %>% 
-  count() %>% 
-  ungroup() -> rostered_count_by_pos
-
-rosters_by_position %>% 
-  group_by(position) %>% 
-  arrange(zar %>% desc()) %>% 
-  mutate(num = row_number()) %>% 
-  full_join(rostered_count_by_pos, "position") %>% 
-  filter(num <= n) %>% 
-  summarize(median_zar = median(zar)) -> pos_median_zar
-
-rosters_by_position %>% 
-  full_join(pos_median_zar) %>% 
-  #FIXME two decimal places for pos_zar
-  mutate(pos_zar = zar - median_zar) -> rosters_by_position
+```{r}
 
 team <- rosters_by_position %>% 
-  filter(team == "Plouffe There It Is!")
+  filter(team == "Deez Nuts")
 
@@
 
-result <- tibble(
-  position = positions,
-  player_id = NA
-)
+```
 
+```{r}
 batters <- team %>%
   filter(type == "batter") %>% 
-  arrange(pos_zar %>% desc(), zar %>% desc() ) %>% 
-  select(player_id, name_full, position, pos_zar, zar)
+  select(team, player_id, name_full, position, pos_zar, zar) %>% 
+  arrange(zar %>% desc(), pos_zar %>% desc)
 
@@
 
-for (i in 0:length(batter_ids)) {
-  print(i+1)
+team_result <- tibble(
+  position = positions,
+  player_id = NA
+)
+
+i <- 1
+
+```
+```{r}
+
+batter_id <- batter_ids[i]
+
+batter <- batters %>% 
+  filter(player_id == batter_id)
+
+batters <- batters %>% 
+  add_row(
+    team = team$team[1],
+    player_id = batter$player_id[1],
+    name_full = batter$name_full[1],
+    position = "Util",
+    pos_zar = -100,
+    zar = batter$zar[1]
+  ) %>% 
+  arrange(zar %>% desc(), pos_zar %>% desc)
+
+for (j in 1:length(batter$position)) {
+  if (team_result$player_id[team_result$position == batter$position[j]] %>% is.na()) {
+    batter_id -> team_result$player_id[team_result$position == batter$position[j]]
+    print(paste0("Assigned ",batter$name_full," to ",batter$position[j]))
+
+    break
   }
+}
+
+if (!batter_id %in% (team_result$player_id %>% as_factor() %>% levels())) {
+  if (team_result$player_id[team_result$position == "Util"] %>% is.na()) {
+    batter_id -> team_result$player_id[team_result$position == "Util"]
+  }
+  else {
+    print(paste0("sending batter_id ", batter_id, " to bench"))
+  }
+}
+
+i <- i+1
+
+result <- batters %>% 
+  mutate(position = as.character(position)) %>% 
+  inner_join(team_result, c("player_id","position"))
+
+result
 ```
+
+```{r}
+result %>% 
+  mutate(pos_zar = if_else(
+    position == "Util",
+    zar,
+    pos_zar
+  ))
+```

### 2019-07-07 rosterReview_generic.Rmd
Working optional lineup (offense) function

@@
 ```{r}
+rosters_by_position <- row_per_position(rosters)
+
+optimal_lineups_offense <- rosters_by_position %>% 
+  optimal_lineup()
+
+```
+
+```{r}
 #TODO abstract some of these views
@@
 
-```{r}
-#TODO move to separate research
-rosters_by_position <- row_per_position(rosters)
-
-rosters_by_position %>% 
-  filter(!is.na(manager)) %>% 
-  group_by(position) %>% 
-  count() %>% 
-  ungroup() -> rostered_count_by_pos
-
-rosters_by_position %>% 
-  group_by(position) %>% 
-  arrange(zar %>% desc()) %>% 
-  mutate(num = row_number()) %>% 
-  full_join(rostered_count_by_pos, "position") %>% 
-  filter(num <= n) %>% 
-  summarize(median_zar = median(zar)) -> pos_median_zar
-
-rosters_by_position %>% 
-  full_join(pos_median_zar) %>% 
-  #FIXME two decimal places for pos_zar
-  mutate(pos_zar = zar - median_zar) -> rosters_by_position
-
-```
 ```{r}
@@
 
-# Averaging pos_zar by position, overall
-# Does this actually indicate good/bad teams?
+# FIXME join optimal offense lineup with all pitching
 rosters_by_position %>% 
@@
 
-#TODO 3 OFs, players with multiple positions, avoid bench players
 team_pos_avg_zar %>% 

### 2019-07-07 R/helper.R

@@ -6,7 +6,6 @@ source("R/yahoo_api.R")
 
 #TODO ingest performance data from fangraphs
 #TODO add overall/by type rankings
-#TODO rank/zar by position
 #TODO move all read_csv references to read_latest_file_csv
 
 filename_today <- function(name, extension) {
@@ -194,7 +193,6 @@ compact_positions <- function(df) {
     mutate(positions = if_else(positions == "",position,positions))
 }
 
-#TODO replace DH with util
 row_per_position <- function(df) {
   df <- df %>%
     mutate(C = grepl("C", display_position)) %>%
@@ -248,7 +246,7 @@ row_per_position <- function(df) {
     filter(RP) %>% 
     mutate(position = "RP")
   
-  C %>%
+  rosters_by_position <- C %>%
     bind_rows(`1B`) %>%
     bind_rows(`2B`) %>%
     bind_rows(`3B`) %>%
@@ -262,63 +260,97 @@ row_per_position <- function(df) {
     arrange(z_sum %>% desc) %>%
     mutate(z_rank = row_number(),
            position = fct_relevel(position, "C","1B","2B","3B","SS","LF","CF","RF","SP","RP"))
+  
+  rosters_by_position %>% 
+    filter(!is.na(manager)) %>% 
+    group_by(position) %>% 
+    count() %>% 
+    ungroup() -> rostered_count_by_pos
+  
+  rosters_by_position %>% 
+    group_by(position) %>% 
+    arrange(zar %>% desc()) %>% 
+    mutate(num = row_number()) %>% 
+    full_join(rostered_count_by_pos, "position") %>% 
+    filter(num <= n) %>% 
+    summarize(median_zar = median(zar)) -> pos_median_zar
+  
+  rosters_by_position %>% 
+    full_join(pos_median_zar) %>% 
+    mutate(pos_zar = zar - median_zar)
 }
-
-#TODO WIP
-# Assign by pos_zar (for each player, check if there are other rows beneath)
-# LF - Soto
-# RF - Bellinger
-# SS - Lindor
-# CF - Gallo (zar < LF && zar < RF)
-# Util - Story
-# 1B - Bell
-# C - Contreras
-# Bench - Puig (zar < RF && zar < Util)
-# 2B - Carpenter
-# Bench - Posey (zar < C && zar < Util zar < 1B)
-# 3B - Devers
-# Bench - Murphy (zar < 2B && zar < 1B && zar < Util)
 
[…]

### 2019-07-09 rosterReview_generic.Rmd
WIP implementing optimal lineup

@@
 
-optimal_lineups_offense <- rosters_by_position %>% 
+team_batters_starters <- rosters_by_position %>% 
   optimal_lineup()
+
+# TODO get position factor ordering back, summarize pitching to single point/range, add bench single point/range, consider DL?
+rosters_by_position %>% 
+  filter(team != "Free Agent",
+         type == "pitcher") %>% 
+  mutate(position = as.character(position)) %>% 
+  droplevels() -> team_pitchers_all
+
+team_pitchers_SP <- team_pitchers_all %>% 
+  filter(position == 'SP')
+
+team_pitchers_RP <- team_pitchers_all %>% 
+  filter(position == 'RP') %>% 
+  anti_join(team_pitchers_SP, "player_id") %>% 
+  group_by(team) %>% 
+  arrange(zar %>% desc) %>% 
+  mutate(rnk = row_number()) %>% 
+  filter(rnk <= 6) %>% 
+  select(position, player_id, name_full, team, manager, zar, pos_zar)
+
+team_pitchers_SP %>% 
+  bind_rows(team_pitchers_RP) %>% 
+  group_by(team, position) %>% 
+  summarize(zar = mean(zar),
+            pos_zar = mean(pos_zar)) -> team_pitchers_starters
+
+rosters_by_position %>% 
+  filter(team != "Free Agent",
+         type == "batter") %>% 
+  mutate(position = as.character(position)) %>% 
+  droplevels() -> team_batters_all
+
+team_batters_all %>% 
+  anti_join(team_batters_starters, "player_id") %>% 
+  group_by(player_id, name_full) %>% 
+  arrange(player_id, pos_zar %>% desc) %>% 
+  mutate(rnk = row_number(),
+         position = "BN") %>% 
+  filter(rnk == 1) %>% 
+  ungroup() %>% 
+  select(position, player_id, name_full, team, manager, zar, pos_zar) -> team_batters_bench
+
+team_batters_starters %>% 
+  bind_rows(team_batters_bench) %>% 
+  bind_rows(team_pitchers_starters)
+
+#FIXME team_batters_starters needs MANAGER column
 
@@
 rosters_by_position %>% 
-  filter(team != "Free Agent") %>% 
-  ggplot(aes(position, zar, color = position, alpha = zar)) +
-  geom_point(aes(text=name_full)) +
-  facet_wrap(~ team) -> team_pos
-
-ggplotly(team_pos)
-
-rosters_by_position %>% 
   select(team, manager, name_full, position, zar, pos_zar) %>% 
@@
 
-# FIXME join optimal offense lineup with all pitching
-rosters_by_position %>% 
-  filter(team != "Free Agent") %>% 
-  group_by(team, position) %>% 
-  summarize(avg_pos_zar = mean(pos_zar)) -> team_pos_avg_zar
+team_pitchers %>% 
+  bind_rows(team_batters_starters) %>% 
+  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
+  geom_point() +
+  facet_wrap(~ team) -> team_pos_optimal
 
-team_pos_avg_zar %>%  
-  ggplot(aes(position, avg_pos_zar, color = position)) +
-  geom_point() +
-  facet_wrap(~ team) -> team_avg_pos
-
-ggplotly(team_avg_pos)
+ggplotly(team_pos_optimal)
 
@@
   arrange(mean_pos_zar %>% desc)
-
-rosters_by_position %>% 
-  filter(team != "Free Agent") %>% 
-  ggplot(aes(pos_zar)) + 
-  geom_freqpoly(binwidth=.25) + 
-  facet_wrap(~ position)
 ```
@@
   geom_boxplot()
+
+# frequency graph by pos_zar for each position
+rosters_by_position %>% 
+  filter(team != "Free Agent") %>% 
+  ggplot(aes(pos_zar)) + 
+  geom_freqpoly(binwidth=.25) + 
+  facet_wrap(~ position)
 ```

### 2019-07-09 R/helper.R

@@ -290,8 +290,6 @@ optimal_lineup <- function(df) {
     droplevels()
   
   for (each in df$team %>% levels()) {
-    print(paste0("Working on team = ", each))
-    
     team_result <- tibble(
       position = positions,
       player_id = NA

### 2019-07-09 rosterReview_generic.Rmd
optimal lineup complete, experimenting with various ros projected team rankings and views

@@
 
-```{r}
+```{r get_data}
 force_fetch <- FALSE
@@
 
-```{r}
+```{r df_prep}
 rosters_by_position <- row_per_position(rosters)
@@
 
-# TODO get position factor ordering back, summarize pitching to single point/range, add bench single point/range, consider DL?
+# TODO get position factor ordering back, consider DL?
 rosters_by_position %>% 
@@
   mutate(rnk = row_number()) %>% 
-  filter(rnk <= 6) %>% 
-  select(position, player_id, name_full, team, manager, zar, pos_zar)
+  filter(rnk <= 6)
 
@@
   bind_rows(team_pitchers_RP) %>% 
-  group_by(team, position) %>% 
-  summarize(zar = mean(zar),
-            pos_zar = mean(pos_zar)) -> team_pitchers_starters
+  select(position, player_id, name_full, team, manager, zar, pos_zar) -> team_pitchers_starters
 
@@
 
-team_batters_starters %>% 
+team_lineups <- team_batters_starters %>% 
   bind_rows(team_batters_bench) %>% 
-  bind_rows(team_pitchers_starters)
+  bind_rows(team_pitchers_starters) %>% 
+  mutate(position = fct_relevel(position, "C","1B","2B","3B","SS","LF","CF","RF", "Util","SP","RP","BN"))
 
-#FIXME team_batters_starters needs MANAGER column
+standings_projected <- team_lineups %>% 
+  filter(position != 'BN') %>% 
+  group_by(team) %>% 
+  summarize(sum_pos_zar = sum(pos_zar),
+            mean_pos_zar = mean(pos_zar),
+            median_pos_zar = median(pos_zar),
+            var_pos_zar = sd(pos_zar)) %>% 
+  arrange(sum_pos_zar %>% desc)
 
@@
 
-```{r}
+```{r ros_team_rankings}
+rosters_by_position %>% 
+  filter(team != "Free Agent") %>% 
+  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
+  geom_point(aes(text=name_full)) +
+  facet_wrap(~ team) -> team_pos_adj
+
+ggplotly(team_pos_adj)
+
+team_lineups %>% 
+  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
+  geom_point(aes(text=name_full)) +
+  facet_wrap(~ team) -> team_pos_optimal
+
+ggplotly(team_pos_optimal)
+
+standings_projected %>% 
+  mutate(sum_pos_zar = sum_pos_zar - median(sum_pos_zar)) %>% 
+  mutate(team = fct_reorder(team, sum_pos_zar)) %>% 
+  ggplot(aes(team, sum_pos_zar)) +
+  geom_col() +
+  coord_flip()
+
+#TODO try other graph views, including error bars representing variance
+```
+
+```{r free_agents}
 #TODO abstract some of these views
@@
 
-```{r}
-rosters_by_position %>% 
-  select(team, manager, name_full, position, zar, pos_zar) %>% 
-  # filter(position %in% c('SP','RP')) %>% 
-  filter(grepl("Plouffe",team)) %>% 
-  arrange(pos_zar %>% desc) %>%
-  mutate(pos_zar = pos_zar %>% round(1),
-         zar = zar %>% round(1)) %>% 
-  View("ZAR by Position")
-
-rosters_by_position %>% 
-  filter(team != "Free Agent") %>% 
-  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
-  geom_point(aes(text=name_full)) +
-  facet_wrap(~ team) -> team_pos_adj
-
-ggplotly(team_pos_adj)
-
-team_pitchers %>% 
-  bind_rows(team_batters_starters) %>% 
-  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
-  geom_point() +
-  facet_wrap(~ team) -> team_pos_optimal
-
-ggplotly(team_pos_optimal)
-
-team_pos_avg_zar %>% 
-  ungroup() %>% 
-  group_by(team) %>% 
-  summarize(sum_pos_zar = sum(avg_pos_zar),
-            mean_pos_zar = mean(avg_pos_zar),
-            var_pos_zar = sd(avg_pos_zar)) %>% 
-  arrange(mean_pos_zar %>% desc)
-```
-
-```{r}
+```{r trade_eval}
 # TODO find way to wrap these three views into one
@@
 
-```{r}
-rosters %>% 
-  filter(!grepl("Free Agent",team)
-  #        ,
-  # grepl("CF",positions)
-       ) %>%
-  ggplot(aes(x=team,y=zar,color=type)) +
-  geom_boxplot() +
-  # geom_jitter(aes(text=name_full), width = .2) +
-  coord_flip() -> tb
-
-ggplotly(tb)
-```
-
-```{r}
+```{r draft_analysis}
 #TODO measuring projected value of draft picks, move to separate research

### 2019-07-09 R/helper.R

@@ -349,6 +349,9 @@ optimal_lineup <- function(df) {
     }
   }
   
-  result %>%
-    mutate(pos_zar = if_else(position=="Util",zar,pos_zar))
+  df %>% 
+    select(team, manager) %>% 
+    distinct() %>% 
+    right_join(result, "team") %>%
+    mutate(pos_zar = if_else(position=="Util",zar,pos_zar)) 
 } 

### 2019-07-09 rosterReview_generic.Rmd
All-Star break lineups, some refactoring of views

@@
 ```{r get_data}
-force_fetch <- FALSE
-force_join <- FALSE
+force_fetch <- TRUE
+force_join <- TRUE
 batter_file <- "temp/FanGraphs Leaderboard.csv"
@@
 }
-
-#TODO review duplicates
 ```
@@
 
-# TODO get position factor ordering back, consider DL?
+# TODO consider DL?
+# FIXME a few empty position slots for a one or two teams
 rosters_by_position %>% 
@@
             var_pos_zar = sd(pos_zar)) %>% 
+  mutate(adj_sum_pos_zar = sum_pos_zar - median(sum_pos_zar)) %>% 
   arrange(sum_pos_zar %>% desc)
@@
   filter(team != "Free Agent") %>% 
+  mutate(zar = round(zar,2)) %>% 
   ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
@@
 team_lineups %>%
+  mutate(zar = round(zar,2)) %>% 
   ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
@@
 standings_projected %>% 
-  mutate(sum_pos_zar = sum_pos_zar - median(sum_pos_zar)) %>% 
-  mutate(team = fct_reorder(team, sum_pos_zar)) %>% 
-  ggplot(aes(team, sum_pos_zar)) +
+  mutate(team = fct_reorder(team, adj_sum_pos_zar)) %>% 
+  ggplot(aes(team, adj_sum_pos_zar)) +
   geom_col() +
+  geom_errorbar(aes(ymin=adj_sum_pos_zar-var_pos_zar, ymax=adj_sum_pos_zar+var_pos_zar), width = .5) +
   coord_flip()
-
-#TODO try other graph views, including error bars representing variance
 ```
@@
   mutate(zar = round(zar)) %>% 
-  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
+  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 3)) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +
-  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
+  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.3) +
   coord_flip() -> pa
@@
 rosters %>% 
-  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
+  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 3)) %>% 
   arrange(zar %>% desc) %>% 
@@
 ```
+
+```{r dups}
+#FIXME dups 
+rosters %>% count(player_id) %>% filter(n > 1) %>% left_join(rosters) -> dups
+
+dups %>% count(team)
+
+dups %>% select(team, manager, name_full, positions)
+
+```

### 2019-07-11 R/scrape_fg.R
Starting fangraphs scraping of performance and projection data via RSelenium

@@ -1,0 +1,58 @@
+library(RSelenium)
+library(here)
+
+fprof <- makeFirefoxProfile(
+  list(
+    browser.download.dir = here("temp"), 
+    browser.download.folderList = 2L, 
+    browser.download.manager.showWhenStarting = FALSE, 
+    browser.helperApps.neverAsk.saveToDisk = "text/csv"
+    )
+  )
+
+url_projection_batter <- "https://www.fangraphs.com/projections.aspx?pos=all&stats=bat&type=rfangraphsdc&team=0&lg=all&players=0"
+url_projection_pitcher <- "https://www.fangraphs.com/projections.aspx?pos=all&stats=pit&type=rfangraphsdc&team=0&lg=all&players=0"
+
+url_perf_batter <- "https://www.fangraphs.com/leaders.aspx?pos=all&stats=bat&lg=all&qual=0&type=c,4,6,5,7,11,12,13,21,14,16,-1,34,35,40,41,-1,23,37,38,39,50,61,-1,111,-1,203,199,58&season=2019&month=0&season1=2019&ind=0&team=&rost=&age=&filter=&players="
+url_perf_pitcher <- "https://www.fangraphs.com/leaders.aspx?pos=all&stats=pit&lg=all&qual=0&type=c,4,5,11,114,7,8,13,24,-1,36,37,40,43,44,48,51,-1,6,42,45,62,-1,59&season=2019&month=0&season1=2019&ind=0&team=0&rost=0&age=0&filter=&players=0"
+
+start_local_server <- function() {
+  rsDriver(
+    port = 2525L, 
+    browser = "firefox", 
+    extraCapabilities = fprof,
+    verbose = FALSE
+  )
+}
+
+download_fg_csv <- function(url, rd) {
+  csv_xpath <- NULL
+  
+  if (grepl("/leaders", url)) {
+    csv_xpath <- '//*[@id="LeaderBoard1_cmdCSV"]'
+  } else if (grepl("/projections", url)) {
+    csv_xpath <- '//*[@id="ProjectionBoard1_cmdCSV"]'
+  }
+  
+  if (!is.null(csv_button)) {
+    client <- rd$client
+    client$navigate(url)
+    
+    # TODO avoid membership popup
+    
+    csv_button <- client$findElement(using = "xpath", value = csv_xpath)
+    csv_button$clickElement
+    client$close()
+    
+    # TODO rename downloaded file
+    
+  } else {
[…]

### 2019-07-22 rosterReview_generic.Rmd
Latest rosters, some adjustments to the fg_scrape methods

@@
 
+# FIXME pretty sure this error bar ain't right
 standings_projected %>% 

### 2019-07-22 R/scrape_fg.R

@@ -3,8 +3,11 @@ library(here)
 
 fprof <- makeFirefoxProfile(
   list(
-    browser.download.dir = here("temp"), 
     browser.download.folderList = 2L, 
+    browser.download.defaultFolder = here("temp"),
+    browser.download.dir = here("temp"),
+    browser.download.downloadDir = here("temp"),
+    browser.download.lastDir = here("temp"),
     browser.download.manager.showWhenStarting = FALSE, 
     browser.helperApps.neverAsk.saveToDisk = "text/csv"
     )
@@ -38,10 +41,12 @@ download_fg_csv <- function(url, rd) {
     client <- rd$client
     client$navigate(url)
     
-    # TODO avoid membership popup
-    
+    membership_popup_nothanks <- client$findElement(using = "xpath",
+                                                    value = '/html/body/div[5]/div[1]/div[3]/a[2]')
     csv_button <- client$findElement(using = "xpath", value = csv_xpath)
-    csv_button$clickElement
+    
+    membership_popup_nothanks$clickElement() # appears to do nothing if not there
+    csv_button$clickElement()
     client$close()
     
     # TODO rename downloaded file
@@ -52,7 +57,8 @@ download_fg_csv <- function(url, rd) {
 }
 
 # implementation
-rd <- start_local_server()
-download_fg_csv(url_projection_batter, rd)
+# rd <- start_local_server()
+# download_fg_csv(url_perf_batter, rd)
+# rd$server$stop()
 
 

### 2019-07-25 rosterReview_generic.Rmd
minor adjustments to generic roster review and latest lineups

@@
 
+```{r myteam}
+rosters %>% 
+  filter(grepl("Plouffe",team)) %>% 
+  select(name_full, positions, zar) %>% 
+  arrange(zar %>% desc) %>% 
+  View("My Team")
+```
+
 ```{r ros_team_rankings}
@@
 # TODO find way to wrap these three views into one
-rosters %>% 
-  filter(grepl("Plouffe|Mata",team)) %>% 
-  select(team, manager, name_full, display_position, zar, positions) %>% 
+rosters_by_position %>% 
+  filter(grepl("Plouffe|Bumpin",team)) %>% 
+  select(team, manager, name_full, display_position, zar, pos_zar, positions, draft_round) %>% 
   arrange(zar %>% desc) %>% 
@@
 rosters %>% 
-  filter(grepl("Plouffe|Mata",team)) %>% 
+  filter(grepl("Plouffe|Bumpin",team)) %>% 
   ggplot(aes(x=team,y=zar,color=type)) +

### 2019-08-09 rosterReview_generic.Rmd
Latest rosters

@@
 ```{r ros_team_rankings}
+# TODO adjust for DL
 rosters_by_position %>% 

### 2019-08-19 rosterReview_generic.Rmd
Latest rosters, expanded free agent look

@@
 
+free_agent_compare <- 
   rosters %>% 
@@
   arrange(zar %>% desc) %>% 
-  mutate(zar = zar %>% round(digits=1)) %>% 
+  mutate(zar = zar %>% round(digits=1))
+
+free_agent_compare %>% 
+  # select(team, name_full, positions, type, zar) %>% 
+  select(team, name_full, positions, type, zar, g:war, z_r:z_whip)
+  View("Available Free Agents Expanded")
+
+free_agent_compare %>% 
   select(team, name_full, positions, type, zar) %>%

### 2019-09-02 rosterReview_generic.Rmd
Latest rosters to start the playoffs

@@
   # select(team, name_full, positions, type, zar) %>% 
-  select(team, name_full, positions, type, zar, g:war, z_r:z_whip)
+  select(team, name_full, positions, type, zar, g:war, z_r:z_whip) %>% 
   View("Available Free Agents Expanded")

### 2021-03-03 R/yahoo_api.R
Minor adjustment to yahoo_api

@@ -40,16 +40,18 @@ authenticate <- function() {
 }
 
 get_json <- function(path) {
-  
-  config <- authenticate()
-  ua <- user_agent("http://github.com/TK2575/ff_data")
-  
   base <- "https://fantasysports.yahooapis.com/fantasy/v2/"
   req_json <- "/?response=json"
   
   url <- paste0(base, path, req_json)
-  
+  get_json_url(url)
+}
+
+get_json_url <- function(url) {
   print(url)
+  
+  config <- authenticate()
+  ua <- user_agent("http://github.com/TK2575/ff_data")
   
   resp <- GET(url = url, config = config, ua)
   if (http_type(resp) != "application/json") {
@@ -128,6 +130,8 @@ get_players_page <- function(start=0) {
     tibble()
   }
 }
+
+httr::oauth_endpoint()
 
 league_string <- function(game_key=388) {
   league_key <- Sys.getenv("LEAGUE_KEY")

### 2021-03-03 draft_helper/app.R
Clear out for 2021

@@ -1,148 +1,0 @@
-library(shiny)
-library(shinythemes)
-library(plotly)
-library(tidyverse)
-
-source("chooser.R")
-
-main_df <- readRDS("../data/draft_dataset.Rds")
-
-players <- main_df %>%
-  arrange(ADP) %>%
-  select(Name) %>%
-  pull()
-
-positions_df <- main_df %>%
-  mutate(C = grepl("C", display_position)) %>%
-  mutate(`1B` = grepl("1B", positions)) %>%
-  mutate(`2B` = grepl("2B", positions)) %>%
-  mutate(SS = grepl("SS", positions)) %>%
-  mutate(`3B` = grepl("3B", positions)) %>%
-  mutate(LF = grepl("LF", positions)) %>% 
-  mutate(CF = grepl("CF", positions)) %>% 
-  mutate(RF = grepl("RF", positions)) %>%
-  mutate(SP = grepl("SP", positions)) %>%
-  mutate(RP = grepl("RP", positions)) 
-
-C <- positions_df %>%
-  filter(C) %>%
-  mutate(position = "C")
-
-`1B` <- positions_df %>%
-  filter(`1B`) %>%
-  mutate(position = "1B")
-
-`2B` <- positions_df %>%
-  filter(`2B`) %>%
-  mutate(position = "2B")
-
-`3B` <- positions_df %>%
-  filter(`3B`) %>%
-  mutate(position = "3B")
-
-SS <- positions_df %>%
-  filter(SS) %>%
-  mutate(position = "SS")
-
-LF <- positions_df %>%
-  filter(LF) %>%
-  mutate(position = "LF")
-
-CF <- positions_df %>%
-  filter(CF) %>%
-  mutate(position = "CF")
-
-RF <- positions_df %>%
-  filter(RF) %>%
-  mutate(position = "RF")
-
-SP <- positions_df %>% 
-  filter(SP) %>% 
-  mutate(position = "SP")
-
-RP <- positions_df %>% 
-  filter(RP) %>% 
-  mutate(position = "RP")
-
-positions_df_ex <- C %>%
-  bind_rows(`1B`) %>%
-  bind_rows(`2B`) %>%
-  bind_rows(`3B`) %>%
-  bind_rows(SS) %>%
-  bind_rows(LF) %>% 
-  bind_rows(CF) %>% 
-  bind_rows(RF) %>% 
-  bind_rows(SP) %>%
-  bind_rows(RP) %>%
-  unique() %>%
[…]

### 2021-03-03 Rmd/league_scoring_settings.Rmd
Evaluate league scoring settings by scraping 2020 performance data from baseball reference, plotting the distribution of points scored per player and position

---
title: "League Scoring Settings"
author: "Tom Kain"
date: "3/2/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(here)
source(here::here("R", "scrape_bref.R"))
```

```{r import}

year <- 2020
batting_raw <- player_standard_batting(year)
pitching_raw <- player_standard_pitching(year)
starting_pitching_raw <- player_starting_pitching(year)
relief_pitching_raw <- player_relief_pitching(year)
```

```{r clean}

clean <- function(df) {
  df %>% 
    filter(name != 'Name') %>% 
    mutate(rk = as.numeric(rk)) %>% 
    group_by(name) %>% 
    arrange(name, rk) %>% 
    mutate(rnk = row_number()) %>% 
    filter(rnk == 1) %>% 
    ungroup()
}

batting <- 
  batting_raw %>% 
  clean() %>% 
  select(-rk, -rnk, -name, -age, -tm, -lg) %>% 
  sapply(as.numeric) %>% 
  as_tibble() %>% 
  filter(g >= 10)

starting_pitching <- 
  starting_pitching_raw %>% 
  clean() %>% 
  select(name, qs)

relief_pitching <-
  relief_pitching_raw %>% 
  clean() %>% 
  select(name, b_sv) %>% 
  rename(bsv = b_sv)

pitching <-
  pitching_raw %>% 
  clean() %>% 
  left_join(starting_pitching, by = "name") %>% 
  left_join(relief_pitching, by = "name") %>% 
  select(-name, -rk, -rnk, -age, -tm, -lg) %>% 
  sapply(as.numeric) %>% 
  as_tibble() %>% 
  filter(g >= 10) %>% 
  mutate(qs = if_else(is.na(qs), 0, qs),
         bsv = if_else(is.na(bsv), 0, bsv))

```

```{r scoring rules}

batting <- 
  batting %>% 
  mutate(x1b = h - x2b - x3b - hr,
         tb = x1b + (2 * x2b) + (3 * x3b) + (4 * hr),
         points = r + x1b + (2 * x2b) + (3 * x3b) + (4 * hr) + tb + (2 * rbi) + bb + (-3 * so) + (2 * sb) + (-2 * cs))

pitching <-
  pitching %>% 
  mutate(ip_whole = round(ip),
         points = (ip_whole * 3) + (-1 * h) + (-2 * er) + (-1 * bb) +  so + (5 * qs) + (10 * sho) + (10 * w) + (-5 * l) + (7 * sv) + (-3 * bsv))

```

```{r point results}

points <-
  batting %>% 
  group_by(points) %>% 
  summarize(batting = n()) %>% 
  ungroup() %>% 
  pivot_longer(!points, names_to = "position", values_to = "count")

points <- 
  pitching %>% 
  group_by(points) %>% 
  summarize(pitching = n()) %>% 
  ungroup() %>% 
  pivot_longer(!points, names_to = "position", values_to = "count") %>% 
  bind_rows(points)

points %>% 
  ggplot(aes(x = points, group=position, color=position)) +
  geom_freqpoly()

```

### 2021-03-03 R/scrape_bref.R

@@ -1,0 +1,119 @@
+library(rvest)
+library(xml2)
+library(janitor)
+library(dplyr)
+library(magrittr)
+library(purrr)
+
+#TODO enforce numeric columns (chr defaults)
+
+scrape_table <- function(url) {
+  url %>% 
+    read_html() %>% 
+    html_nodes("table") %>% 
+    html_table() %>% 
+    .[[1]] %>% 
+    as_tibble() %>% 
+    clean_names()
+}
+
+player_standard_batting <- function(year) {
+  url <- paste0(
+    "https://widgets.sports-reference.com/wg.fcgi?css=1&site=br&url=%2Fleagues%2FMLB%2F",
+    year,
+    "-standard-batting.shtml&div=div_players_standard_batting"
+  )
+  
+  scrape_single_year_table(url, year)
+}
+
+player_standard_pitching <- function(year) {
+  url <- paste0(
+    "https://widgets.sports-reference.com/wg.fcgi?css=1&site=br&url=%2Fleagues%2FMLB%2F",
+    year,
+    "-standard-pitching.shtml&div=div_players_standard_pitching"
+  )
+  
+  scrape_single_year_table(url, year)
+}
+
+player_starting_pitching <- function(year) {
+  url <- paste0(
+    "https://widgets.sports-reference.com/wg.fcgi?css=1&site=br&url=%2Fleagues%2FMLB%2F",
+    year,
+    "-starter-pitching.shtml&div=div_players_starter_pitching"
+  )
+  
+  scrape_single_year_table(url, year)
+}
+
+player_relief_pitching <- function(year) {
+  url <- paste0(
+    "https://widgets.sports-reference.com/wg.fcgi?css=1&site=br&url=%2Fleagues%2FMLB%2F",
+    year,
+    "-reliever-pitching.shtml&div=div_players_reliever_pitching"
+  )
+  
+  scrape_single_year_table(url, year)
+}
+
+standings_expanded <- function(year) {
+  url <- paste0(
+    "https://widgets.sports-reference.com/wg.fcgi?css=1&site=br&url=%2Fleagues%2FMLB%2F", 
+    year,
+    "-standings.shtml%3Fsr%26utm_source%3Ddirect%26utm_medium%3DShare%26utm_campaign%3DShareTool&div=div_expanded_standings_overall")
+  
+  scrape_single_year_table(url, year)
+}
+
+scrape_single_year_table <- function(url, year) {
+  if (!is.numeric(year) || nchar(year) != 4) {
[…]

### 2021-03-27 Rmd/roto_draft_prep.Rmd
Roto draft prep

---
title: "Roto Draft Prep"
author: "Tom Kain"
date: "3/26/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(here)
```

Data from [Fangraphs](https://www.fangraphs.com/fantasy-tools/auction-calculator?teams=12&lg=MLB&dollars=1000&mb=1&mp=20&msp=5&mrp=5&type=bat&players=&proj=fangraphsdc&split=&rep=0&drp=0&pp=C,SS,2B,3B,OF,1B&pos=1,1,1,1,3,1,0,0,0,1,5,3,0,8,0&sort=&view=0&points=c|1,2,3,4,5,6|1,2,3,4)
```{r}

batting <-
  here::here("in", "fangraphs-auction-calculator-batting.csv") %>% 
  read_csv() %>% 
  janitor::clean_names() %>% 
  select(name, team, pos, adp, pts, a_pos, dollars, player_id)

pitching <-
  here::here("in", "fangraphs-auction-calculator-pitching.csv") %>% 
  read_csv() %>% 
  janitor::clean_names() %>% 
  select(name, team, pos, adp, pts, a_pos, dollars, player_id)

rankings <- 
  batting %>% 
  bind_rows(pitching) %>% 
  arrange(dollars %>% desc) %>% 
  head(400) %>% 
  mutate(pos_primary = str_extract(pos, '^[^/]+'))

```

```{r}

rankings %>% 
  filter(adp < 999) %>% 
  ggplot(aes(x=adp,y=dollars,color=pos_primary)) +
  geom_point() +
  geom_smooth(aes(group=1), method = "lm")

rankings %>% 
  filter(adp < 999) %>% 
  ggplot(aes(x=adp,y=dollars)) +
  geom_point() +
  geom_smooth(aes(group=1), method = "lm") + 
  facet_wrap(~pos_primary)

```
